\documentclass[11pt]{article}
\usepackage{orcidlink}
\usepackage[margin=0.82in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs,tabularx,array}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{authblk}
\usepackage{needspace}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{authblk}


\newcommand{\email}[1]{\texttt{#1}}
\definecolor{PRnavy}{HTML}{17365D}
\definecolor{PRblue}{HTML}{2F5597}
\definecolor{PRgray}{HTML}{5B6573}
\hypersetup{
  colorlinks=true,
  linkcolor=PRblue,
  citecolor=PRblue,
  urlcolor=PRblue,
  pdftitle={Projection Relativity IV: The Global Singleton Theorem},
  pdfauthor={Michael Stanislaus Oshetski},
  pdfsubject={Axiom-by-axiom uniqueness and canonical closure of the complete PR-I--PR-III equation architecture}
}

\pagestyle{plain}
\fancyhf{} % Clears all header/footer fields
\fancyfoot[C]{\thepage} % Puts the page number back in the center bottom
%\setlength{\parindent}{0pt}
%\setlength{\parskip}{0.55em}
%\setlist{itemsep=0.2em,topsep=0.3em}
%\renewcommand{\arraystretch}{1.18}
%\pagestyle{fancy}
%\fancyhf{}
%\fancyhead[L]{\small\color{PRgray}Projection Relativity IV}
%\fancyhead[R]{\small\color{PRgray}Global Singleton Theorem}
%\fancyfoot[C]{\thepage}
%\setlength{\headheight}{14pt}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}

\title{\textbf{The Foundation of Projection Relativity IV}\\[0.35em]
\Large The Global Singleton Theorem\\
\large Axiom-by-Axiom Uniqueness and Canonical Closure\\
\large of the Complete Projection Relativity Architecture}
\author{Michael Stanislaus Oshetski \orcidlink{0009-0007-3623-7586} \\
\small \texttt{michael.oshetski@micatu.com}\\ 
\small Founder and Chief Technology Officer \\
\small Advanced Photonics Laboratory (APL)\\
\small Micatu, Inc. \\
\small Horseheads, New York, USA \\
\small ORCID: 0009-0007-3623-7586}

\date {July 2026}

\begin{document}
\maketitle
\begin{abstract}
Projection Relativity manuscripts I through III present a no-fit spectral-projection architecture spanning radial, compact, electroweak, flavor, radiative, neutrino, and strong sectors.  This paper proves equation-architecture uniqueness over explicitly declared
admissible classes, modulo gauge, basis, coordinate, sign, algebraic, and unit equivalences.  Direct ancestry from the seven PR-I postulates and proved canonical logical closure are the two accepted provenance routes.  A sector may close through a canonical logical extension when compatibility, minimality, covariance, target-independent normalization, and exhaustive classification select one equivalence class
without a fitted coefficient or new adjustable scale. A normal-form exhaustion theorem makes the equation-level claim precise: once the structural candidate class is fixed independently, every in-class equation either has a nonzero exact closure defect or is related to the canonical equation by an invertible ledger-preserving transformation.  Merely matching one reported number is not counted as equivalence.

Exact rank and semigroup arguments establish rigidity of the minimal even quartic radial branch and parts of the compact recurrence.  Formal coefficient extraction and rank--nullity fix $\sigma_8=-1$ and $N_{\rm gen}=3$ inside explicitly declared boundary and sheet-realization classes.  For neutral $D_3$, exact rank reduction leaves $D_3(k)=(\epsilon_V^2/N_{\rm gen})kP_Z$.  The remaining response is fixed by a
canonical-closure theorem: unitary-basis invariance, orthogonal-mode additivity, quadratic homogeneity, and unit-charge normalization uniquely force the response functional to be $F(q)=\operatorname{Tr}(q^\dagger q)$.  Since the normalized charged-adjoint operator has eigencharges $(+1,-1)$, $F(q)=2$ and the sole member of the declared minimal PR neutral-response class is $D_3=2(\epsilon_V^2/N_{\rm
gen})P_Z$.  No empirical target or free coefficient enters this selection.

Abstract second-jet families and the gauge-invariant operator $|\Phi^\dagger D_\mu\Phi|^2$ lie outside the PR admissible class because they introduce independent response data or a new Wilson coefficient.  They are therefore different theories, not additional PR parameters or alternative PR solutions.  The complete PR class used here is fixed by the public PR-I--PR-III ledger together with inheritance, minimality, covariance, completeness, nonredundancy, canonical normalization, declared finite-tier order, and the no-fit firewall.  On every equation-selection coordinate of that class, exact normal-form defects have one zero.  Consequently, the
dependency-ordered admissible equation quotient is the singleton $\{[\mathrm{PR}]\}$: every working in-class presentation is equivalent and every inequivalent proposal violates at least one declared guideline.  No discrete or continuous free selector remains.  This is a closure theorem for the PR equation architecture; distinct physical states of one fixed field equation are not distinct theories and are not counted as alternative equation architectures.
\end{abstract}

\section{Introduction}

PR-I defines the seven-postulate spectral-projection foundation \cite{PRI}; PR-II supplies the non-Abelian electroweak and flavor lift \cite{PRII}; and PR-III supplies a finite-tier radiative and cross-sector closure with an explicit no-fit provenance firewall \cite{PRIII}.  PR-IV closes the equation-equivalence question for the declared PR admissible class.  The public PR-I--PR-III equations and finite-tier rules form the inherited ledger; the present theorem proves that their admissible equation-selection quotient contains one physical equivalence class.

The absolute rule is the no-fit firewall.  No diagnostic residual may generate
an equation, coefficient, branch, or admissibility condition.  Direct derivation from the PR-I postulates is one complete provenance route, and a downstream relation may also be admitted as a canonical logical closure when its framework origin is stated, its candidate class is declared, and exact classification leaves no adjustable freedom.  An inequivalent construction enters the uniqueness quotient only when it satisfies that same admissible class.  A construction that introduces an independent operator, response jet, or coefficient belongs to an enlarged theory and maps the boundary of the PR closure class without modifying the canonical PR branch. There is no unresolved selector inside the class defined in this paper.

All public-source statements are audited against repository commit
\texttt{9680f70b21f0} (full hash in the source ledger).  Machine-readable exact
certificates accompany the manuscript \cite{PRRepo}.

\input{sections/02_foundational_derivation_standard}
\input{sections/03_no_other_solutions_standard}
\input{sections/04_pr1_radial_compact_rigidity}
\input{sections/05_pr1_compact_selector_countermodels}
\input{sections/06_pr2_branch_classification}
\input{sections/07_pr3_branch_countermodels}
\input{sections/08_derivation_graph_verdict}
\input{sections/09_conclusion}
\input{sections/10_axiom_by_axiom_appendix}
\input{sections/11_diagnostic_propagation_appendix}
\input{sections/12_branch_elimination_appendix}
\input{sections/13_three_selector_closure_appendix}
\input{sections/14_generation_count_rigidity_appendix}
\input{sections/15_terminal_orientation_rigidity_appendix}
\input{sections/16_neutral_d3_coefficient_rigidity_appendix}
\input{sections/17_physical_z_hessian_obstruction_appendix}

\newpage
\bibliographystyle{plain} 
\bibliography{Oshetski_Projection_Relativity_IV_References} 
\end{document}
