\section{Frozen-postulate Countermodels to Unconditional Compact Uniqueness}
\label{sec:pr1-compact-countermodels}

The seven PR-I postulates do not uniquely determine the compact return language, the signed terminal cofactor, or the finite radial slice.  This is a logical independence result, not merely the absence of a completed proof.  We hold fixed the master field, internal cylinder, metric, Hilbert space, separable spectral operator, projection-trace radial potential, trace alphabet $T_A=1/4$, $T_X=3/4$, and the published primitive-return denominator
\begin{equation}
 D_A=1-T_A^3-T_A^4=\frac{251}{256}.
\end{equation}
No diagnostic input is admitted.

For $\sigma\in\{-1,0,+1\}$ define the finite, integer-coefficient terminal cofactor
\begin{equation}
 N_\sigma=1+T_A^3+T_A^4+T_X\left(T_A^5+\sigma T_A^8\right).
 \label{eq:pr35-terminal-countermodels}
\end{equation}
Each member contains no continuous free parameter.  Nevertheless the three members yield distinct rational values of $N_\sigma$, $R_\sigma=N_\sigma/D_A$,
and
\begin{equation}
 c_\sigma=T_X\left(1+T_A^2-T_A^6R_\sigma\right).
\end{equation}
The published branch is $\sigma=-1$.  Postulates 1--6 contain no terminal-word orientation equation, and Postulate 7 requires projection maps without fixing the coefficient in Eq.~\eqref{eq:pr35-terminal-countermodels}.  The remaining two members are therefore inequivalent frozen-postulate countermodels.

The finite slice is independently underdetermined.  In the nondegenerate radial eigenbasis, each of
\begin{equation}
 \Pi_{1j}=|\phi_1\rangle\langle\phi_1|+
 |\phi_j\rangle\langle\phi_j|,\qquad j\in\{3,5,7\},
\end{equation}
is a rank-two, parity-preserving orthogonal spectral projector with no continuous coefficient.  Postulate 7 does not supply an index theorem selecting $j=3$.  Since the corresponding ranges contain different nondegenerate radial eigenvalues, these choices are not removable by sign or by a basis convention that preserves the radial operator.

The exact certificate therefore contains nine discrete cofactor/projector combinations, eight of which are nonpublished.  It follows that parameter-free provenance is insufficient for uniqueness.  Under the frozen-postulate policy, the correct disposition is to retain the published compact closure only as a conditional theorem inside its stated boundary-orientation class; it cannot enter the unconditional closed-solution theorem unless the missing selectors are derived from Postulates 1 through 7.
