\section{Closure Attempts for the Three Surviving Selectors}
\label{app:three-selector-closure}

The three values below now have exact uniqueness arguments inside explicitly
declared mathematical classes.  The remaining question in each case is
ancestry of that class from the frozen theory, not diagnostic preference.

\subsection{Terminal Orientation}

Let $E=XA^8$ be an independent terminal word.  In the signed finite-rank pre-projection exclusion class, the raw return grammar contributes one copy of $E$, the terminal counterterm contributes $\sigma_8E$, and admissibility requires zero total $E$ incidence.  Exact coefficient extraction gives
\begin{equation}
 [E](C_{\rm raw}+N_{\sigma})=1+\sigma_8=0,
 \qquad \sigma_8=-1.
\end{equation}
Every other value leaves the nonzero defect $(1+\sigma_8)E$.  P1 through P7 do not
yet derive the independent-word grammar or the pre-projection zero-incidence rule; if a later projector merely annihilates $E$, the signs become quotient-equivalent.  Appendix~\ref{app:terminal-orientation-rigidity} gives the full conditional theorem.

\subsection{Neutral Quadratic Representation Factor}

At one fixed $D_3$ Lorentz/momentum kernel and declared scalar order, an exact
rank reduction over all ten components of its real symmetric gauge-index
coefficient matrix on $(W^1,W^2,Z,A)$ gives dimensions four after residual
$U(1)$ invariance, three after requiring the charged sector unchanged, and one
after photon nullity.  The complete structural family within this fixed-kernel
matrix class is therefore
\begin{equation}
 D_3(k)=\frac{\epsilon_V^2}{N_{\rm gen}}kP_Z,
 \qquad k\in\mathbb R.
\end{equation}
Thus the structural gates fix a one-dimensional subspace but not its scalar.
Independent Lorentz/derivative structures remain outside this matrix
classification.  For the normalized
adjoint matrices $(F_a)_{bc}=-i\epsilon_{abc}$ and charged projector
$P_{\rm ch}=\operatorname{diag}(1,1,0)$, define
\begin{equation}
 K_{ab}=\operatorname{Tr}_{\rm ad}
 \!\left(P_{\rm ch}F_aP_{\rm ch}F_b\right).
\end{equation}
Direct contraction gives $K_{ab}=2\delta_{a3}\delta_{b3}$.  Hence, if the
PR-III operator is exactly
\begin{equation}
 (D_3)_{ab}=\frac{\epsilon_V^2}{N_{\rm gen}}K_{ab}
\end{equation}
with unit prefactor and no other same-order contribution, then its charged
entries vanish and $D_{3,Z}=2\epsilon_V^2/N_{\rm gen}$.  Thus $k=2$ is unique
in this contraction class.  On the complete structural family the exact
squared defect is
$(\epsilon_V^2/N_{\rm gen})^2(k-2)^2$, whose sole real zero is two.  Without
the unit-prefactor identity, however,
$D_\lambda=2\lambda(\epsilon_V^2/N_{\rm gen})P_Z$ is an exact counterfamily.
The locked one-sigma mass gate permits
$0.7684347876\ldots<k<3.1450923435\ldots$, including the fixed alternatives $k=1$, $2\cos^2\theta_W$, and $3$. Appendix~\ref{app:d3-coefficient-rigidity} gives the necessary-and-sufficient four-defect candidate characterization.  Its normalization defect becomes a physical exclusion only after the still-open determinant-Hessian and normalized physical-$Z$ map are derived.

\subsection{Generation Identification}

Let $V_{\rm br}$ be the three-dimensional broken electroweak tangent space and
$\Phi_N:S_N\to V_{\rm br}$ the terminal-sheet incidence map.  Completeness
makes $\Phi_N$ surjective and nonredundancy makes it injective.  Rank--nullity
then gives
\begin{equation}
 N=\operatorname{rank}\Phi_N+\dim\ker\Phi_N=3+0=3.
\end{equation}
Consequently, $N<3$ is incomplete and $N>3$ has a redundant sheet combination
in that realization class.  P1 through P7 do not yet construct $\Phi_N$ or prove its one-to-one interpretation as physical fermion generations.  Appendix
\ref{app:generation-count-rigidity} states the precise conditional theorem.

\subsection{Verdict}

All three values are conditionally rigid, and none is selected by best fit.
For $D_3$, the exhaustive fixed-kernel gauge-index classification also proves
unconditional nonuniqueness in the stated three-gate class.
The values are
not yet unconditional P1 though P7 consequences: signed boundary incidence, the
sheet-to-fermion map, and the complete determinant-Hessian plus normalized
trace-to-$D_3$ map remain explicit ancestry obligations.  The result is
therefore conditional closure of the three values, not a completed global
singleton theorem.
