\section{Generation-count Rigidity in the PR-II Sheet Class}
\label{app:generation-count-rigidity}

The generation ambiguity can be closed inside the generation-sheet class
actually used by PR-II.  Let
\begin{equation}
 G=SU(2)_L\times U(1)_Y,
 \qquad H=U(1)_{\rm em},
 \qquad V_{\rm br}=T_{[eH]}(G/H).
\end{equation}
The broken-direction space has the exact dimension
\begin{equation}
 \dim V_{\rm br}=\dim G-\dim H=(3+1)-1=3.
 \label{eq:pr35-broken-dimension}
\end{equation}

Let $S_N$ be the span of $N$ distinct terminal generation sheets, and let
\begin{equation}
 \Phi_N:S_N\longrightarrow V_{\rm br}
 \label{eq:pr35-sheet-incidence-map}
\end{equation}
be their broken-direction incidence map.  The direct mapping described in PR-II has two structural requirements.  Completeness requires $\Phi_N$ to be surjective, so no broken electroweak direction is omitted.  Nonredundancy requires $\Phi_N$ to be injective, so no nonzero sheet combination has a zero geometric image.

\begin{theorem}[Conditional PR-II Generation-count Rigidity]
A complete and nonredundant terminal-sheet realization exists if and only if $N=3$.  Consequently $N_{\rm gen}^{\rm PR}=3$ is the unique count in this construction class.
\end{theorem}

\begin{proof}
Surjectivity implies $\operatorname{rank}\Phi_N=\dim V_{\rm br}=3$, hence $N\ge3$.  Injectivity implies $\operatorname{nullity}\Phi_N=0$.  Rank--nullity then gives
\begin{equation}
 N=\dim S_N
 =\operatorname{rank}\Phi_N+\operatorname{nullity}\Phi_N
 =3+0=3.
\end{equation}
Conversely, a basis of $S_3$ can be mapped to a basis of $V_{\rm br}$, giving an isomorphism.  Therefore, three is necessary and sufficient.
\end{proof}

This proof exhausts every positive integer.  If $N<3$, the map has rank at
most $N$ and cannot cover the quotient.  If $N>3$, every surjective map has
nullity at least $N-3$, producing redundant or geometrically ungrounded sheet
combinations.  Thus every alternative count breaks either completeness or
nonredundancy.

The scope is important.  Equation~\eqref{eq:pr35-broken-dimension} alone does
not prove a universal theorem relating gauge-boson directions to fermion
families.  The result proves uniqueness within PR-II's declared terminal-sheet
realization, which directly maps the replicated matter ledger across the
broken compact projection directions.  No measured generation count, mass,
mixing angle, or diagnostic residual enters the proof.

For this result to become a frozen-postulate theorem, $\Phi_N$ must be
constructed uniformly from PR operators before choosing $N$, completeness and
nonredundancy must follow independently from the projection rules, and the
basis of $S_N$ must be proved to count inequivalent chiral fermion generations.
PR-II states the intended direct mapping and its $N=2$ and $N=4$ negative
controls, but an operator-level realization of $\Phi_N$ is not present in the
public derivation.  The integer exhaustion is therefore complete, whereas the
sheet-to-fermion ancestry remains an explicit open obligation.
