\documentclass[11pt]{article}
\usepackage{orcidlink}
\usepackage[margin=0.75in]{geometry}
\usepackage{amsmath,amssymb,amsfonts,bm,mathtools}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{booktabs,longtable,array,multirow}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage[most]{tcolorbox}
\usepackage{needspace}
\usepackage{float}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{authblk}
\hypersetup{hidelinks}


\setlength{\parindent}{0pt}
\setlength{\parskip}{0.55em}
\renewcommand{\arraystretch}{1.22}

\newcommand{\PR}{\mathrm{PR}}
\newcommand{\eff}{\mathrm{eff}}
\newcommand{\Kerr}{\mathrm{Kerr}}
\newcommand{\GR}{\mathrm{GR}}
\newcommand{\obs}{\mathrm{obs}}
\newcommand{\src}{\mathrm{src}}
\newcommand{\vac}{\mathrm{vac}}
\newcommand{\homPR}{\mathrm{hom}}
\newcommand{\TT}{\mathrm{TT}}
\newcommand{\Teuk}{\mathrm{Teuk}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\email}[1]{\href{mailto:#1}{\texttt{#1}}}
\renewcommand{\arraystretch}{1.4}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}

\title{The Foundation of Projection Relativity \uppercase\expandafter{\romannumeral3}\\
\Large Zero-Parameter Radiative and Cross-Sector Closure of the Projection Ledger}

\author{Michael Stanislaus Oshetski \orcidlink{0009-0007-3623-7586} \\
\small \email{michael.oshetski@micatu.com}\\
\small Founder and Chief Technology Officer \\
\small Advanced Photonics Laboratory (APL)\\
\small Micatu, Inc. \\
\small Horseheads, New York, USA \\
\small ORCID: 0009-0007-3623-7586
\date {July 2026}}

\begin{document}
\maketitle

\begin{abstract}
Projection Relativity III (PR-III) studies the finite-tier radiative and cross-sector closure of the theoretical framework introduced in the PR-I and PR-II preprints. Building upon the frozen PR-I spectral-projection geometry and the PR-II compact electroweak and flavor lift, this work evaluates electromagnetic, electroweak, neutrino, strong, anomaly, and running-continuity branches without importing the selected diagnostic observables as fitted inputs. The result is a closed, reproducible, no-fit equation ledger at the stated finite tier.

Numerically, the generated architecture achieves sub-sigma agreement with empirical targets. The fine-structure inverse matches its reference to within $+0.1376\sigma$, while the core electroweak constants $M_W$, $M_Z$, and $G_F$ align to within $+0.3566\sigma$, $+0.0364\sigma$, and $+0.6003\sigma$, respectively. Extending to the lepton sector, the neutrino branch is radiatively stable under the declared finite-tier multiplicative envelope and preserves the normal mass ordering, with the summed mass, effective beta observables, and $m_{\beta\beta}$ envelope remaining well below current empirical ceilings. The strong-sector ledger locks the $SU(3)_c$ color identities, active-flavor thresholds, and the one-loop asymptotic-freedom sign. This constrained architecture ultimately yields a strong anchor that agrees with diagnostic references to within $0.04\%$. Global structural audits successfully verify the cancellation of local gauge anomalies per generation and the absence of the Witten anomaly. Additionally, the residual electromagnetic branch remains purely vector-like, maintaining running continuity under strict no-fit provenance.

The charged-adjoint representation fixes the exact normalized quadratic invariant
\(\operatorname{Tr}_{\rm ch}(q^\dagger q)=2\).  PR-III identifies the neutral \(C_3\) term with the minimal physical-\(Z\) response: a charged-preserving, photon-null rank-one correction built from the inherited scale \(\rho_{\rm PR}\) and the unique additive, basis-invariant normalized quadratic
charge functional.  Within this declared admissible class the coefficient is uniquely \(k=2\), and no fitted freedom remains.  Exact normal-form reduction shows that every other in-class equation either has nonzero defect \(\rho_{\rm PR}^2(k-2)^2\) or is an invertible presentation of the same
residual law on the complete declared charge-operator domain.  The canonical finite-tier identity is established by the normalized-response theorem; a gauge-fixed neutral-Hessian presentation, when used, is an equivalent microscopic representation of the same in-class response law.  Broader operator families with independent higher-dimensional Wilson coefficients define different theory classes and are not additional PR parameters or alternative PR branches.  The reported \(C_3\)
value is therefore the canonical no-fit neutral closure at the stated tier, with its class-relative theorem status explicit.  With the completed PR-IV Global Singleton Theorem, the same normal-form, exact-defect, and equivalence trichotomy closes the registered PR-I--PR-III equation architecture: its admissible quotient is a singleton with no fitted or free continuous parameter.  This statement is relative to the declared postulates and finite-tier domain; additional fields, higher orders, and independent EFT coefficients define other theory classes rather than additional PR solutions.  The numerical branch, software, and audit checks are available in the public repository.
\end{abstract}

\section{Introduction}
\label{sec:priii-introduction}
Projection Relativity III (PR-III) investigates the finite-tier radiative and cross-sector closure of the Projection Relativity framework. Rather than establishing a new theoretical starting point, this manuscript builds directly upon the geometric and topological foundations laid in the Projection Relativity I \cite{OshetskiPR1Zenodo2026} and Projection Relativity II \cite{OshetskiPR2Zenodo2026} preprints.

In PR-I, we introduced the master projection field $\Psi(x,\xi)$ and the minimal internal geometry 
\begin{equation}
\mathcal{M}_{\rm int} = \mathbb{R}_w \times S_\theta^1.
\end{equation}
This architecture demonstrated that gravitational stiffness, displacement-generated inertia, and compact electromagnetic phase are not unrelated phenomena, but primary observable projections of a single internal spectral manifold. The radial spectral gap of this manifold supplied a finite coercive scale, enabling the finite-core regularization of the strong-field branch while preserving the exterior relativistic limit \cite{OshetskiPR1Zenodo2026}. 

PR-II subsequently lifted this compact boundary construction into the non-Abelian electroweak and flavor setting \cite{OshetskiPR2Zenodo2026}. By replacing the minimal phase circle with the parent compact electroweak fiber 
\begin{equation}
\mathcal{M}_{\rm int}^{\rm EW} = \mathbb{R}_w \times S_Y^1 \times SU(2)_L,
\end{equation}
the residual electromagnetic phase was recovered as the locked boundary of the larger fiber \cite{OshetskiPR2Zenodo2026}. This allowed weak mixing, the weak-scale structure, flavor hierarchy, and neutrino candidates to emerge as outputs of projection geometry rather than empirical insertions. The class-relative three-generation statement combines the broken-quotient dimension with a complete and nonredundant sheet-incidence map; rank--nullity then gives
\begin{equation}
N_{\rm gen}^{\rm PR} = \dim\left[(SU(2)_L \times U(1)_Y)/U(1)_{\rm em}\right] = 3.
\end{equation}
Dimension alone is not claimed to determine the physical sheet map.  To make the full incidence equation unique under normalized basis changes, the normalized-incidence closure additionally requires $\Phi_3^\dagger\Phi_3=I_3$; all such maps belong to one orthogonal equivalence orbit in the real realization (unitary after complexification).

The present paper begins from these frozen geometric structures.  Its purpose is to close the declared finite-tier radiative, strong-sector, and running-continuity architecture of PR-I and PR-II.  PR-III establishes reproducible consistency, stability, and no-fit provenance at that tier, and the companion PR-IV Global Singleton Theorem supplies equation-level exhaustion for the completed selector class.  Together they define a closed class-relative architecture with no inequivalent equation satisfying the same admissibility rules remaining.

\begin{figure}[h]
\centering
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[
  >=Stealth,
  font=\sffamily\footnotesize,
  panel/.style={rounded corners=9pt, draw=black!45, very thick, fill=black!2},
  title/.style={font=\sffamily\bfseries\large, align=center},
  subtitle/.style={font=\sffamily\footnotesize, align=center, text=black!70},
  equation/.style={font=\sffamily\footnotesize, align=center, text=black},
  branch/.style={rounded corners=5pt, draw=black!50, thick, fill=white, align=center, inner sep=4pt},
  prnode/.style={circle, draw=black!55, thick, fill=white, minimum size=0.9cm, align=center},
  flow/.style={->, very thick, draw=black!70},
  softflow/.style={->, thick, draw=black!45},
  broken/.style={->, very thick, dashed, draw=red!70!black},
  residual/.style={->, very thick, draw=blue!70!black},
  nofit/.style={rounded corners=8pt, draw=green!45!black, very thick, dashed, fill=green!5, align=center}
]

% Global Panel Positioning Settings
\def\panelH{10.2cm}
\def\titleY{4.3}
\def\subY{3.85}
\def\eqY{3.35}
\def\bottomTextY{-4.4}

% =========================================================
% PANEL A: PR-I
% =========================================================
\begin{scope}[shift={(0,0)}]
  \node[panel, minimum width=6.0cm, minimum height=\panelH] (Abox) at (0,0) {};
  \node[title] at (0,\titleY) {(A) PR-I};
  \node[subtitle] at (0,\subY) {minimal spectral projection geometry};
  \node[equation] at (0,\eqY) {$\mathcal M_{\rm int}=\mathbb R_w\times S^1_\theta$};

  % Cylinder representing R_w x S^1
  \draw[very thick, fill=gray!10] (-0.95,-0.65) -- (-0.95,1.85);
  \draw[very thick, fill=gray!10] (0.95,-0.65) -- (0.95,1.85);
  \draw[very thick, fill=gray!14] (0,1.85) ellipse (0.95cm and 0.28cm);
  \draw[very thick, dashed, gray!65] (-0.95,-0.65) arc (180:360:0.95cm and 0.28cm);
  \draw[very thick] (0.95,-0.65) arc (0:-180:0.95cm and 0.28cm);

  % Coordinates
  \draw[->, very thick, blue!70!black] (0,-1.4) -- (0,2.6) node[above, text=black] {$w$};
  \draw[->, very thick, red!70!black] (-0.95,0.7) arc (185:350:0.95cm and 0.28cm)
     node[right, text=black] {$\theta$};

  % Branches spaced
  \node[branch] (rad) at (-1.9, 1.9) {radial\\stiffness};
  \node[branch] (comp) at (1.9, 1.9) {compact\\phase};
  \node[branch] (disp) at (-1.7, -1.5) {displacement\\branch};

  \draw[softflow] (rad) -- (-0.95, 1.5);
  \draw[softflow] (comp) -- (0.95, 0.9);
  \draw[softflow] (disp) -- (-0.95, -0.1);

  \node[subtitle, text width=5.5cm] at (0,\bottomTextY)
    {PR-I fixes the spectral boundary ledger inherited by PR-III.};
\end{scope}

% =========================================================
% PANEL B: PR-II
% =========================================================
\begin{scope}[shift={(7.2,0)}] % Increased shift for wider spacing
  \node[panel, minimum width=6.2cm, minimum height=\panelH] (Bbox) at (0,0) {};
  \node[title] at (0,\titleY) {(B) PR-II};
  \node[subtitle] at (0,\subY) {compact electroweak lift};
  \node[equation] at (0,\eqY) {$\mathcal M_{\rm int}^{\rm EW}=\mathbb R_w\times S_Y^1\times SU(2)_L$};

  % Parent fiber stack
  \node[prnode, fill=blue!7] (RW) at (-1.6, 2.0) {$\mathbb R_w$};
  \node[prnode, fill=orange!10] (SY) at (0, 2.0) {$S_Y^1$};
  \node[prnode, fill=violet!10] (SU) at (1.6, 2.0) {$SU(2)_L$};
  
  \draw[softflow] (RW) -- (SY);
  \draw[softflow] (SY) -- (SU);

  % Locking plane
  \node[nofit, draw=cyan!60!black, fill=cyan!7, minimum width=4.8cm, minimum height=0.9cm] (Qplane) at (0, 0.2)
    {$Q=T_3+Y/2$\\projection locking};
    
  % Cleanly routed flows (Drawn BEFORE the text label)
  \draw[flow] (RW.south) -- (RW.south |- Qplane.north);
  \draw[flow] (SY.south) -- (Qplane.north);
  \draw[flow] (SU.south) -- (SU.south |- Qplane.north);

  % "Parent compact fiber" label (Drawn AFTER flows with a solid background to mask the lines)
  \node[subtitle, fill=black!2, inner sep=3pt] at (0, 1.0) {parent compact fiber};

  % Residual and broken outputs
  \node[branch, fill=blue!5] (gamma) at (0, -1.6) {$U(1)_{\rm em}$\\$\gamma$ residual};
  \node[branch, fill=red!5] (W) at (-1.8, -1.5) {$W^\pm$};
  \node[branch, fill=red!5] (Z) at (1.8, -1.5) {$Z$};

  \draw[residual] (0,-0.25) -- (gamma.north);
  \draw[broken] (-1.2,-0.25) .. controls (-1.2,-0.9) .. (W.north);
  \draw[broken] (1.2,-0.25) .. controls (1.2,-0.9) .. (Z.north);

  \node[subtitle, text width=5.5cm] at (0,\bottomTextY)
    {PR-II supplies the non-Abelian electroweak and flavor ledger.};
\end{scope}

% =========================================================
% PANEL C: PR-III
% =========================================================
\begin{scope}[shift={(15.0,0)}] % Increased shift to prevent "closure" arrow collision
  \node[panel, minimum width=7.0cm, minimum height=\panelH] (Cbox) at (0,0) {};
  \node[title] at (0,\titleY) {(C) PR-III};
  \node[subtitle] at (0,\subY) {finite-tier audit of the inherited ledger};

  % No-fit provenance envelope
  \node[nofit, minimum width=6.6cm, minimum height=5.2cm] (env) at (0, 0.8) {};
  \node[subtitle, text=green!35!black] at (0, 3.0) {frozen no-fit provenance envelope};

  % Central ledger
  \node[branch, fill=green!8, minimum width=2.6cm, minimum height=0.8cm] (ledger) at (0, 0.8)
    {PR-III\\finite-tier ledger};

  % Branches safely routed inside envelope boundaries
  \node[branch, fill=yellow!12] (alpha) at (-2.1, 2.0) {$\alpha$ radiative\\closure};
  \node[branch, fill=cyan!10] (ew) at (0, 2.1) {EW precision\\closure};
  \node[branch, fill=purple!8] (nu) at (2.1, 2.0) {neutrino\\stability};
  \node[branch, fill=red!6] (strong) at (-2.1, -0.4) {strong\\fiber};
  \node[branch, fill=gray!8] (anom) at (0, -0.6) {anomaly\\registry};
  \node[branch, fill=gray!8] (run) at (2.1, -0.4) {running\\continuity};

  \draw[softflow] (alpha) -- (ledger);
  \draw[softflow] (ew) -- (ledger);
  \draw[softflow] (nu) -- (ledger);
  \draw[softflow] (strong) -- (ledger);
  \draw[softflow] (anom) -- (ledger);
  \draw[softflow] (run) -- (ledger);

  % "No target inputs" intercepting the bottom dashed line of the envelope
  \node[fill=white, text=black!70!black, font=\sffamily\footnotesize\bfseries, inner sep=3pt, rounded corners=2pt] 
    at (0, -1.8) {No Target Inputs};

  % Diagnostic references securely below envelope
  \node[branch, fill=black!3, text width=5.0cm] (diag) at (0, -2.8)
    {diagnostic references\\used only after generation};
  
  % Arrow from envelope to diagnostic
  \draw[->, thick, draw=black!55] (0, -2.0) -- (diag.north);
  
  \node[subtitle, text width=6.765cm] at (0,\bottomTextY)
    {PR-III establishes the inherited ledger at the stated finite tier; PR-IV formalizes the corresponding equation-exhaustion theorems.};
\end{scope}

% =========================================================
% INTER-PANEL ARROWS (Adjusted for wider panel spacing)
% =========================================================
\draw[flow, ultra thick, black!50] (3.2,0) -- (3.9,0) node[midway, above, font=\sffamily\scriptsize] {lift};
\draw[flow, ultra thick, black!50] (10.5,0) -- (11.3,0) node[midway, above, font=\sffamily\scriptsize] {audit};

\end{tikzpicture}
}
\caption{\textbf{Geometric inheritance and no-fit closure across PR-I--PR-III.}
\textbf{(A)} PR-I begins with the minimal internal projection geometry
$\mathcal M_{\rm int}=\mathbb R_w\times S^1_\theta$, in which the non-compact
radial direction supplies the stiffness branch and the compact phase direction
supplies the residual electromagnetic phase.
\textbf{(B)} PR-II lifts this compact boundary into the electroweak parent fiber
$\mathcal M_{\rm int}^{\rm EW}=\mathbb R_w\times S_Y^1\times SU(2)_L$.
Projection locking through $Q=T_3+Y/2$ selects the unbroken residual
$U(1)_{\rm em}$ boundary, while the broken directions generate the massive
$W^\pm$ and $Z$ projection excitations.
\textbf{(C)} PR-III does not introduce a new topology; it evaluates a declared
finite-tier extension of the inherited PR-I/PR-II ledger inside a no-fit
provenance envelope. The electromagnetic,
electroweak, neutrino, strong, anomaly, running-continuity, and provenance
branches are generated and audited without using their diagnostic reference
values as generation inputs. The green enclosure denotes the closed
finite-tier admissibility domain and its audit provenance; structures with
additional orders, fields, coefficients, or postulates belong to a different
theory class rather than to an alternative PR-III branch.}
\label{fig:priii-geometric-inheritance-no-fit-closure}
\end{figure}

\subsection{Structural Roadmap and Organization of the Paper}
\label{subsec:priii-paper-organization}

To audit this finite-tier cross-sector ledger, the remainder of the paper is
organized as a sequential chain, outlined in
Table~\ref{tab:structural-roadmap}. PR-I supplies the spectral-projection
foundation. PR-II supplies the compact electroweak and flavor lift. PR-III
proves stability and mutual consistency of the implemented finite-tier branches
without importing target observables as fitted inputs.  The theorem is closed
in two layers: this manuscript establishes the declared finite-tier sectors,
and PR-IV proves that their completed selector quotient contains one
equivalence class.

\begin{table}[h]
\centering
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{@{} >{\bfseries}p{2.5cm} >{\bfseries}p{4.5cm} p{9.3cm} @{}}
\toprule
Section & Sector / Phase & Finite-Tier Actions and Objectives \\
\midrule
\ref{sec:priii-sandbox-roadmap} \& \ref{sec:priii-inheritance-baseline} & Foundation & Fixes the inherited PR-I/PR-II boundary ledger and alpha baseline policy, and reviews the scalar Hessian seed and gauge-null quotient needed to preserve the mass ledger. \\

\ref{sec:priii-alpha-radiative-closure} & Electromagnetic & Constructs the radiative extraction, locks the charged-mode supertrace inventory, and generates boundary-leakage corrections prior to comparison with external fine-structure references. \\

\ref{sec:priii-electroweak-closure} & Electroweak & Transports the electromagnetic closure into the electroweak running scale, refining the weak-angle, vector self-energy, and neutral-channel ledgers to current diagnostic precision. \\

\ref{sec:priii-neutrino-stability} & Neutrino & Audits the mass branch for radiative stability, normal ordering, and PMNS unitarity without importing external oscillation data or cosmological bounds as generation inputs. \\

\ref{sec:priii-strong-sector} & Strong & Locks the compact color-fiber architecture, assembling group identities, active-flavor thresholds, and strong anchors without treating external QCD quantities as fitted targets. \\

\ref{sec:priii-global-consistency} \& \ref{sec:priii-closed-admissibility-domain} & Global Consistency \& Uniqueness & Synthesizes the completed sectors into a global consistency statement, including the anomaly registry and cross-sector diagnostics, and states the closed admissibility domain and class-relative equation-exclusion theorem. \\
\bottomrule
\end{tabular}
\caption{The PR-III structural roadmap and paper organization, detailing the sequential closure of the inherited ledger.}
\label{tab:structural-roadmap}
\end{table} 

\subsection{Reader Prerequisites}
\label{subsec:priii-reader-prerequisites}

A reader can follow the main logic of this paper by keeping several foundational concepts in view. From PR-I, this includes the master-field picture $\Psi(x,\xi)$ and the minimal internal geometry $\mathbb{R}_w\times S^1_\theta$, which establish the interpretation of radial stiffness, displacement, and compact phase as unified projection sectors \cite{OshetskiPR1Zenodo2026}. %[cite: 2]
This foundation also provides the fixed PR-I boundary constants and the electromagnetic phase normalization \cite{OshetskiPR2Zenodo2026}. %[cite: 2]
From PR-II, the core prerequisites are the electroweak lift into the parent fiber $\mathbb{R}_w\times S_Y^1\times SU(2)_L$, the recovery of the residual electromagnetic boundary via $SU(2)_L\times U(1)_Y\to U(1)_{\rm em}$, and the geometric generation-sheet rule $N_{\rm gen}^{\rm PR}=3$ \cite{OshetskiPR2Zenodo2026}. %[cite: 1]
We note, the reader must keep in mind the strict methodological distinction between internally generated values and post-generation diagnostic references. The relevant prior derivations are reviewed here only where they are needed to define the PR-III ledger. Readers seeking the complete geometric construction should consult PR-I for the spectral-projection foundation and PR-II for the compact electroweak and flavor lift.

\subsection{The No-Fit Provenance Discipline}
\label{subsec:priii-no-fit-discipline}

A central rule is maintained throughout this manuscript: diagnostic references may evaluate PR-generated quantities, but they may never generate or tune them. Every value in this paper is strictly classified as either an inherited input from PR-I or PR-II, a PR-generated output, an explicitly declared closure quantity, or a post-generation diagnostic reference. This ``no-fit'' provenance discipline is why this manuscript distinguishes among structural identities, closure theorems, finite-tier relations, and diagnostic comparisons \cite{OshetskiPR1Zenodo2026}.  Absence of fitting is necessary for prediction, but it is logically distinct from the origin of a closure relation.  A finite-tier relation may be admitted either by direct derivation from inherited PR operators or as an explicitly declared logical closure extension.  In the latter case its admissible class, structural motivation, normalization, and uniqueness must be stated, and no empirical target or fitted continuous coefficient may select it.  Section~\ref{subsec:priii-ew-C3-neutral-refinement} applies this standard to the neutral \(C_3\) branch.

\subsection{Reproducibility and Test-Driven Method}
\label{sec:intro_reproducibility}

The development of PR-III follows the same test-driven standard as demonstrated in the previous manuscripts. Each construction is paired with a numerical or symbolic validation harness. The harnesses confirm the generated equations and include control cases that verify exclusion of structures incompatible with the declared PR ledger, including Abelianized $SU(2)$, photon-mass leakage, altered Fermi normalization, nonunitary flavor rotations, anomaly-incompatible fermion ledgers, inverted suppression factors, and target-observable leakage.

In PR-III this standard is applied to the full radiative and cross-sector ledger. The electromagnetic, electroweak, neutrino, strong, anomaly, running-continuity, and no-fit provenance branches are checked as ledger objects before they are compared with diagnostic references. The validation package establishes reproducibility of the encoded formulas and their provenance labels.  Numerical agreement alone proves neither derivation nor uniqueness.  The neutral \(C_3\) generator is instead justified by the canonical minimal-response theorem established in Theorem~\ref{thm:priii-conditional-k-two}.

\begin{quote}
\small
\textbf{Reproducibility statement.}
The PR-III ledger is supported by step-specific validation scripts, Python builders, and locked JSON artifacts. The harness ledger verifies the inheritance and alpha baseline, the scalar Hessian and tree electroweak block, gauge null removal, and the radiative determinant. It further audits the alpha radiative extraction with D1 and D2 refinements, electroweak scale transport alongside C1 and C2, and the arithmetic of the canonical C3 closure.  The proof below, rather than the arithmetic check, establishes the uniqueness of its normalized response functional.  The package also checks neutrino branch radiative stability including the $m_{\beta\beta}$ envelope, strong-sector phase-fiber calculations, global running continuity, and the anomaly registry. Target observables are governed by a no-fit provenance manifest and enter only as post-generation diagnostic (\texttt{DIAG}) references. These excluded generation inputs include reference values for the fine-structure constant ($\alpha$), $M_W$, $M_Z$, $G_F$, neutrino mass-squared splittings ($\Delta m^2_{21}$, $\Delta m^2_{31}$), PMNS mixing angles, cosmological neutrino mass bounds, and the strong coupling reference $\alpha_3$. The code, Markdown reports, and generated JSON outputs are maintained in the public repository:
\href{https://github.com/oshetskiresearch/Projection_Relativity}{\texttt{github.com/oshetskiresearch/Projection\_Relativity}}.
\end{quote}

\section{Radiative and Cross-Sector Closure in PR-III}
\label{sec:priii-sandbox-roadmap}

We begin by using the  PR-II compact electroweak and flavor endpoint, where PR-III extends the projection ledger from tree-level geometric structure to radiative and cross-sector precision.  The inherited inputs are not returned.  They are used as fixed boundary data for the electromagnetic, electroweak, neutrino, strong, anomaly, and running-continuity branches.  The result is a finite no-fit closure chain in which each sector is generated from inherited PR data and earlier PR-generated objects, and only afterward compared with diagnostic references. For a sector \(s\), the construction has the schematic form
\begin{equation}
\mathcal C_s:
\bigl(\mathcal I_{\rm PR-I/II},\mathcal G_{<s}\bigr)
\longrightarrow
\mathcal G_s,
\end{equation}
where \(\mathcal I_{\rm PR-I/II}\) denotes the frozen PR-I/PR-II projection ledger and \(\mathcal G_{<s}\) denotes earlier PR-III generated quantities.  Diagnostic references enter only through the later comparison map
\begin{equation}
\mathcal R_s=\mathcal D_s(\mathcal G_s;\mathcal E_s),
\qquad
\mathcal E_s\cap {\rm Dom}(\mathcal C_s)=\varnothing .
\end{equation}
This is the no-fit condition used throughout the paper.  Agreement with a reference value is therefore interpreted as a post-generation diagnostic result, not as a parameter fit.

\subsection{Summary of PR-III Closure Results}
\label{subsec:priii-summary-closure-results}

Before detailing the derivations, Table~\ref{tab:priii-principal-closures} summarizes the major PR-III closures. These milestones should be interpreted as the principal physical achievements of the paper, not merely as a computational log. Although our public repository provides the exact numerical provenance of every result, the underlying physics is governed strictly by the projection sequence developed in the following sections.

{\small
\begin{longtable}{
  >{\raggedright\arraybackslash}p{0.13\textwidth}
  >{\raggedright\arraybackslash}p{0.24\textwidth}
  >{\raggedright\arraybackslash}p{0.26\textwidth}
  >{\raggedright\arraybackslash}p{0.27\textwidth}
}
\caption{Principal PR-III closures starting from the PR-II endpoint.}
\label{tab:priii-principal-closures}\\
\toprule
\textbf{Sector} & \textbf{PR-II endpoint used as input} & \textbf{PR-III extension} & \textbf{Diagnostic status} \\
\midrule
\endfirsthead
\toprule
\textbf{Sector} & \textbf{PR-II endpoint used as input} & \textbf{PR-III extension} & \textbf{Diagnostic status} \\
\midrule
\endhead

Electromagnetic
& Residual compact electromagnetic boundary \(U(1)_{\rm em}\) and PR boundary constants
& Boundary-leakage radiative correction with mode-resolved \(D_1+D_2\) closure
& \(\alpha_{\rm PR}^{-1}=137.035999207513\ldots\), \(+0.1376\sigma\) against the selected current reference \\
\addlinespace

Electroweak
& Compact electroweak lift \(\mathbb R_w\times S_Y^1\times SU(2)_L\), weak mixing, and displacement scale
& Electromagnetic-to-weak transport, weak-mass reconstruction, vector self-energy, and neutral-channel refinement
& \(M_W:+0.3566\sigma\), \(M_Z:+0.0364\sigma\), \(G_F:+0.6003\sigma\) \\
\addlinespace

Neutrino
& PR-II normal-ordering and PMNS-linked branch
& Multiplicative radiative stability envelope, ordering audit, PMNS unitarity rule, and \(m_{\beta\beta}\) propagation
& Normal ordering preserved; \(\sum m_\nu=0.058733836680\,{\rm eV}\); \(m_\beta=8.8150\,{\rm meV}\); \(m_{\beta\beta}=1.5077\,{\rm meV}\) \\
\addlinespace

Strong
& Compact color-fiber seed, \(N_c=3\), and PR quark threshold sheets
& \(SU(3)_c\) identity lock, ordered active-flavor thresholds, and one-loop color-sign audit
& \(\alpha_{3,{\rm PR}}=0.117861507469150\), diagnostic-compatible at \(-0.03265\%\) relative residual \\
\addlinespace

Global structure
& Completed electromagnetic, electroweak, neutrino, and strong ledgers
& Anomaly registry, running-continuity audit, no-fit provenance manifest, and cross-sector diagnostic table
& Local anomalies cancel per generation; Witten anomaly absent; residual \(U(1)_{\rm em}\) vectorlike; running continuity and no-fit provenance pass \\

\bottomrule
\end{longtable}
}

\subsection{Electromagnetic Closure: Precision \texorpdfstring{$\alpha$}{alpha} result}
\label{subsec:priii-alpha-obligation}

The first extension is electromagnetic.  PR-II identifies the residual electromagnetic phase as the unbroken compact boundary of the electroweak lift.  PR-III turns that boundary statement into a radiative precision result.  The high-resolution tree baseline is fixed before comparison; the charged-mode inventory is evaluated by the electromagnetic \(Q^2\) trace; neutral modes are excluded from the direct charged trace; and the implemented finite-tier spectral kernel, coefficient, weight, and subtraction convention are fixed as part of the admissible PR-III class before evaluation. The boundary-leakage contribution is
\begin{equation}
D_1
=
-p_1^{\rm HR}\,\Delta_{\rm EW}^{\rm HR}\,\sin^2\theta_W^{\rm PR} .
\end{equation}
The three-sheet refinement is fixed by the inherited generation count,
\begin{equation}
\epsilon_2^{\rm PR}
=
\frac{\Delta_{\rm EW}^{\rm HR}}{\sqrt{N_{\rm gen}^{\rm PR}}},
\qquad
D_2=D_1\epsilon_2^{\rm PR} .
\end{equation}
The generated inverse fine-structure value is therefore
\begin{equation}
\alpha_{\rm PR,phys}^{-1}
=
\alpha_{\rm PR,tree}^{-1}+4\pi(D_1+D_2).
\end{equation}
Numerically, PR-III obtains

\begin{equation}
\begin{split}
\alpha_{\rm PR,phys}^{-1} ={} & 137.035999207513414958891346101616 \\
& 5946356776374900155369785562685848 \\
& 55576779314655494829901.
\end{split}
\end{equation}
This numerical resolution is a direct output of the high-resolution spectral audit and is maintained to ensure exact byte-for-byte reproducibility across the closure chain.
Only after this number is generated is it compared with the external fine-structure reference.  The residual against the selected current reference is
\begin{equation}
1.5134\times 10^{-9},
\qquad
\frac{\Delta\alpha^{-1}}{\sigma}=+0.1376 .
\end{equation}
The compact electromagnetic boundary becomes a current-precision no-fit result, rather than remaining only a tree-level phase normalization.

\subsection{Electroweak Closure: Transporting The Electromagnetic Result Into The Weak Scale}
\label{subsec:priii-electroweak-obligation}

The second extension transports this generated electromagnetic precision directly into the weak scale. Building upon the electroweak parent fiber and the residual locking map supplied by PR-II,
\begin{equation}
SU(2)_L\times U(1)_Y\longrightarrow U(1)_{\rm em},
\qquad
Q=T_3+\frac{Y}{2},
\end{equation}
PR-III propagates the derived electromagnetic coupling to the weak boundary. This allows for the exact reconstruction of the continuous electroweak couplings,
\begin{equation}
e_{\rm PR},\qquad
 g_{\rm PR}=\frac{e_{\rm PR}}{\sqrt{\sin^2\theta_W^{\rm PR}}},\qquad
 g'_{\rm PR}=\frac{e_{\rm PR}}{\sqrt{1-\sin^2\theta_W^{\rm PR}}},
\end{equation}
which subsequently generate the weak-mass ledger based solely on the inherited electroweak displacement scale:
\begin{equation}
M_W^2=\frac14 g_{\rm PR}^2 v_{\rm EW,PR}^2,
\qquad
M_Z^2=\frac14\left(g_{\rm PR}^2+g_{\rm PR}^{\prime 2}\right)v_{\rm EW,PR}^2,
\qquad
G_F=\frac{1}{\sqrt2\,v_{\rm EW,PR}^2} .
\end{equation}
The evaluation proceeds through three constrained refinements: the C1 transport establishes baseline weak-mass consistency, the C2 correction introduces the charged and vector self-energy dynamics, and the C3 branch applies the generation-weighted $D_3$ term.  The charged-adjoint algebra fixes the group factor in $D_3$ exactly, and the canonical minimal-response theorem in Sec.~\ref{subsec:priii-ew-C3-neutral-refinement} uniquely maps it to the normalized physical-$Z$ correction.  Evaluated sequentially on that target-independent closure branch, these yield:
\begin{align}
M_W^{\rm PR} &=80.373942851862121269660365960912048165641419593354\ {\rm GeV},\\
M_Z^{\rm PR} &=91.187676431043922257304294605837072137923832857910\ {\rm GeV},\\
G_F^{\rm PR} &=1.1663792201759949366003257867488874906911567673\times10^{-5}\ {\rm GeV}^{-2}.
\end{align}
When evaluated against empirical targets, the corresponding diagnostic distances are
\begin{equation}
M_W:+0.3566\sigma,\qquad
M_Z:+0.0364\sigma,\qquad
G_F:+0.6003\sigma .
\end{equation}
These values establish the stated diagnostic performance of the PR-III
electroweak closure branch.  The selected diagnostic targets are not inputs to its formulas.  The neutral \(C_3\) value is a theorem relative to the declared minimal-response class.  A complete Hessian presentation is an alternative microscopic representation of the same response equation and introduces no additional admissible coefficient.


\subsection{Neutrino Closure: Radiative Stability Of The Inherited Branch}
\label{subsec:priii-neutrino-obligation}

The third extension tests the PR-II neutrino branch under PR-III radiative stability.  The branch is fixed before comparison with oscillation data, cosmological mass ceilings, direct beta-decay bounds, or neutrinoless-double-beta limits.  The radiative kernel is used as a stability envelope, not as a fitted deformation. The final generated branch is
\begin{equation}
(m_1,m_2,m_3)
=
(0,\ 0.008627283010,\ 0.05010655367)\ {\rm eV},
\end{equation}
with
\begin{equation}
\sum_i m_i=0.058733836680\ {\rm eV},
\qquad
m_\beta=0.008815029409997968\ldots\ {\rm eV},
\qquad
m_{\beta\beta}=0.001507694477\ {\rm eV}.
\end{equation}
Normal ordering remains stable under the multiplicative envelope.  The effective Majorana envelope is narrow,
\begin{equation}
1.507519780849\ {\rm meV}
\leq
m_{\beta\beta}
\leq
1.507869173151\ {\rm meV},
\end{equation}
and the PMNS \cite{Pontecorvo1957, MakiNakagawaSakata1962} update is constrained to a unitary generator,
\begin{equation}
U_{\rm PMNS}^{\rm phys}
=
U_{\rm PMNS}^{0}\exp(A_\nu^{\rm PR}),
\qquad
(A_\nu^{\rm PR})^\dagger=-A_\nu^{\rm PR}.
\end{equation}
The neutrino branch therefore remains a stable normal-ordering projection branch whose mass sum, beta observable, and \(m_{\beta\beta}\) scale remain below the current diagnostic ceilings.

\subsection{Strong-Sector Closure: Compact Color Fiber and Active Flavor}
\label{subsec:priii-strong-obligation}

The fourth extension turns to the strong sector, firmly anchoring the compact color-fiber branch. PR-III establishes the geometric constraints on the $SU(3)_c$ gauge group, securing the standard algebraic constants:
\begin{equation}
N_c=3,\qquad
C_A=3,\qquad
C_F=\frac43,\qquad
T_F=\frac12,
\end{equation}
Simultaneously, we preserve the strictly ordered hierarchy of active-flavor thresholds derived from the internal projection sheets:
\begin{equation}
u<d<s<c<b<t .
\end{equation}

Evaluated at the generated electroweak matching scale of $\Lambda_{\rm EW}^{\rm PR}=173.67059834472832\,{\rm GeV}$, the framework naturally saturates the active-flavor count at
\begin{equation}
n_f^{\rm PR}=6.
\end{equation}
This comprehensively determines the reduced one-loop color coefficient,
\begin{equation}
\beta_0^{\rm PR}=11-\frac23 n_f^{\rm PR}=7,
\end{equation}
ensuring that the required negative sign for asymptotic freedom is securely preserved across all allowed active-flavor intervals. When evaluated dynamically, the projection establishes a final strong coupling anchor of
\begin{equation}
\alpha_{3,{\rm PR}}=0.117861507469150.
\end{equation}
Comparing this theoretically derived baseline to the external diagnostic target yields a relative residual of:
\begin{equation}
\alpha_{3,{\rm PR}}-\alpha_s^{\rm diag}
=-0.000038492530850,
\qquad
\frac{\Delta\alpha_3}{\alpha_s^{\rm diag}}=-0.0326484570399\% .
\end{equation}

This calculation is the closed theorem for the declared compact color-fiber, sharp-threshold, one-loop domain.  It verifies the active-threshold ordering and one-loop asymptotic-freedom sign in that class.  All-orders or nonperturbative QCD structures define a different domain and are not alternative solutions of the displayed PR-III equation. The displayed coupling comparison is post-generation only and neither fixes
the strong anchor nor defines an admissibility tier.

\subsection{Cross-Sector Audits: Anomaly, Continuity, and Provenance}
\label{subsec:priii-global-obligation}

The final extension compares the declared finite-tier branches through three
cross-sector structural audits:
\begin{itemize}
    \item \textbf{Anomaly Registry:} Verifies that local gauge anomalies cancel per generation, the Witten $SU(2)$ anomaly is absent, and the residual electromagnetic branch remains purely vector-like.
    \item \textbf{Running Continuity:} Confirms that the electromagnetic-to-electroweak, electroweak-to-neutrino, electroweak-to-strong, and anomaly-continuity links seamlessly integrate without breaking the generated ledger.
    \item \textbf{No-fit Provenance Manifest:} Ensures that forbidden target observables remain strictly excluded from generation, entering only as post-generation diagnostic references.
\end{itemize}

With these audits satisfied, the following finite-tier statuses are recorded:
\begin{itemize}
    \item \textbf{Precision Status:} The fundamental observables ($\alpha^{-1}$, $M_W$, $M_Z$, and $G_F$) successfully pass one-sigma diagnostic thresholds.
    \item \textbf{Compatibility Status:} The neutrino and strong branches remain radiatively stable and highly compatible with current diagnostic ceilings.
    \item \textbf{Structural Status:} Anomaly cancellation, running continuity, and strict no-fit provenance are fully preserved.
\end{itemize}

PR-III therefore provides a reproducible, no-fit, cross-sector ledger at the declared finite tier.  Its theorem domain is exactly the stated PR radiative and cross-sector construction.  Higher radiative orders, different threshold profiles, additional fields, and independent EFT operators change that domain and are therefore outside the PR-III solution class, not unresolved solutions within it.  The completed equation quotient is stated in Sec.~\ref{sec:priii-closed-admissibility-domain}.

\subsection{Organization of the Derivations}
\label{subsec:priii-remaining-sections-plan}

The remainder of this manuscript evaluates the finite-tier relations
and exact structural identities summarized above. We begin by freezing the
inherited PR-I and PR-II geometric baselines used for the PR-III fine-structure calculation. Following this, the framework examines the scalar displacement Hessian and gauge-quotient structure used to isolate the electroweak null directions.

With the inherited baseline frozen, the analysis proceeds sequentially through the phenomenological sectors.  The electromagnetic calculation evaluates the declared boundary-leakage and mode-resolved $D_1+D_2$ relation.  This finite-tier result is transported to the weak scale through the declared weak-mass and neutral-channel ledgers.  The neutrino section proves stability under its stated multiplicative envelope, while the strong-sector section verifies the compact color identities, threshold ordering, and one-loop sign.  PR-IV then applies the common admissibility and equivalence rules to the completed selectors and proves that their equation quotient is a singleton.

The calculations culminate in a cross-sector audit of anomaly cancellation,
running continuity, and strict no-fit provenance across the implemented
branches.  The manuscript concludes by recording the exact closed theorem
domain and the exclusion of every inequivalent in-class equation.

\section{Inherited Baseline and Alpha Policy}
\label{sec:priii-inheritance-baseline}

We now define the inherited baseline used by the alpha calculation and the electroweak seed refined in later sections.  Its role is to fix the geometry, the high-resolution tree value, and the no-fit rule before any precision comparison is made.

\subsection{Inherited Geometric and Projection Baselines}
\label{subsec:priii-frozen-projection-data}

The theoretical foundation of this framework rests upon the universal PR master field,
\begin{equation}
\Psi(x,\xi),
\end{equation}
defined over observable spacetime and the internal projection manifold. The internal geometry inherited from PR-I is given by
\begin{equation}
\mathcal M_{\rm int}=\mathbb R_w\times S^1_\theta,
\end{equation}
which admits the separable internal spectral operator
\begin{equation}
O_{\rm int}=O_X+O_\theta .
\end{equation}

The radial branch, strictly preserved from PR-I, takes the form
\begin{equation}
O_X=-\frac{d^2}{dw^2}+1+w^2+\frac34 w^4,
\label{eq:priii-radial-operator}
\end{equation}
wherein the quadratic coefficient is strictly determined by the unit local radial stiffness, and the quartic coupling is dictated by the projection trace. Within the locked, finite-resolution PR-I framework, this configuration yields a fixed radial spectral gap of
\begin{equation}
\mu_{\min}^2=3.052966743096.
\end{equation}

Correspondingly, the compact phase dynamics are governed by the operator
\begin{equation}
O_\theta=-\frac{1}{R_A^2}\frac{d^2}{d\theta^2},
\end{equation}
which furnishes the residual electromagnetic phase normalization. Sourced directly from the released finite-resolution preprint ledger, the inherited compact-boundary stiffness and its corresponding cofactor are fixed at
\begin{equation}
q_{\rm bc}=10.905007182855176,
\qquad
c_{\rm bc}=0.796684464847899,
\end{equation}
yielding a boundary-resolved electromagnetic normalization of
\begin{equation}
\left(\alpha_{\rm PR,bc}\right)^{-1}=137.036361812007 .
\end{equation}
We present this value as the tree-level phase baseline; it does not represent the final, radiatively corrected PR-III precision value for the fine-structure constant. From PR-II, the framework incorporates the compact electroweak lift, defined over the extended manifold
\begin{equation}
\mathcal M_{\rm int}^{\rm EW}=\mathbb R_w\times S_Y^1\times SU(2)_L,
\end{equation}
associated with the standard residual charge operator
\begin{equation}
Q=T_3+\frac{Y}{2}.
\end{equation}
The fundamental electroweak boundary data initialized for PR-III comprise the geometric displacement and the weak mixing angle,
\begin{equation}
\Delta_{\rm EW}=0.018644236701811,
\qquad
\sin^2\theta_W^{\rm PR}=0.231355763298189,
\end{equation}
alongside the tree-level custodial parameter
\begin{equation}
\rho_{\rm EW}^{(0)}=1 .
\end{equation}
Finally, the internal generation count is inherited as
\begin{equation}
N_{\rm gen}^{\rm PR}=3.
\end{equation}
This topological integer plays a critical role in the subsequent PR-III derivations, acting as a primary geometric constraint for both the mode-resolved fine-structure refinement and the neutral electroweak corrections.

\subsection{High-Resolution Asymptotic Tree Baseline}
\label{subsec:priii-high-resolution-alpha-baseline}

Transitioning from the structural classification of the PR-I and PR-II ledgers to the precision phenomenology examined in PR-III requires a formally strict geometric background. The previously released preprint value,
\begin{equation}
\left(\alpha_{\rm PR,bc}\right)^{-1}=137.036361812007,
\end{equation}
was sufficient for finite-resolution topological classification. However, evaluating quantum-scale radiative corrections fundamentally requires an unperturbed tree baseline whose inherent numerical resolution strictly exceeds the magnitude of the anticipated perturbative shift.  To assign physical meaning to the radiative sector, PR-III must therefore evaluate the alpha branch using the exact high-resolution asymptotic convergence limit:
\begin{equation}
\left(\alpha_{\rm PR,tree}\right)^{-1}
=
137.036041314016444 .
\label{eq:priii-alpha-tree-baseline}
\end{equation}
This baseline is locked prior to any radiative calculation. It is derived exclusively from the geometric convergence sequence of the PR architecture, entirely independent of external diagnostic fitting. This same high-resolution baseline concurrently locks the corresponding geometric boundary parameters:
\begin{equation}
q_{\rm bc}^{\rm HR}=10.904981678435453,
\qquad
c_{\rm bc}=0.796684464847899,
\qquad
p_1^{\rm HR}=7.685346950896231\times10^{-4},
\end{equation}
along with the refined radial spectral gap,
\begin{equation}
\left(\mu_{\min}^{\rm HR}\right)^2=3.053016666732689 .
\end{equation}
The shift from the previous finite-resolution boundary value to this high-resolution tree limit is mathematically exact:
\begin{equation}
\left(\alpha_{\rm PR,tree}\right)^{-1}
-
\left(\alpha_{\rm PR,bc}\right)^{-1}
=
-3.20497990556\times10^{-4} .
\end{equation}
It is imperative to emphasize that this displacement is not a radiative physical correction; it is purely the geometric convergence refinement of the tree-level boundary ledger. Only after Eq.~\eqref{eq:priii-alpha-tree-baseline} is formally fixed does the architecture permit the evaluation of radiative physical corrections.

\subsection{Strict Predictive Constraints and Diagnostic Firewall}
\label{subsec:priii-no-fit-alpha-policy}

To ensure the integrity of the theoretical derivation, PR-III enforces a strict predictive firewall against empirical tuning. Let $\alpha_{\rm ref}^{-1}$ denote an external empirical fine-structure reference used for terminal diagnostic comparison. The PR-III derivation imposes
\begin{equation}
\alpha_{\rm ref}^{-1}\notin {\rm Dom}(\mathcal C_\alpha),
\end{equation}
where $\mathcal C_\alpha$ is the formally defined PR fine-structure construction map. The mathematically permissible inputs for generation are restricted exclusively to inherited structural data. These inputs consist solely of the boundary quantities, the high-resolution tree baseline, the weak boundary deficit, the generation count, the charged-mode inventory, and the PR spectral kernel. The empirical diagnostic target is absolutely forbidden from entering the generation domain. Under this constrained topology, the physical alpha branch takes the form
\begin{equation}
\left(\alpha_{\rm PR,phys}\right)^{-1}
=
\left(\alpha_{\rm PR,tree}\right)^{-1}
+\Delta\alpha_{\rm PR,rad}^{-1},
\label{eq:priii-alpha-physical-policy}
\end{equation}
where the radiative shift $\Delta\alpha_{\rm PR,rad}^{-1}$ must emerge dynamically from native PR geometry. The diagnostic reference is permitted to enter the analysis only after Eq.~\eqref{eq:priii-alpha-physical-policy} has been fully evaluated.

To establish the required scale of this physical correction, we note that the selected empirical diagnostic reference utilized in the final precision audit is
\begin{equation}
\alpha_{\rm diag}^{-1}=137.035999206.
\end{equation}
While this value is strictly excluded from defining $\Delta\alpha_{\rm PR,rad}^{-1}$, it provides the phenomenological target. Relative to the high-resolution tree baseline, the empirical displacement is
\begin{equation}
\alpha_{\rm diag}^{-1}-\left(\alpha_{\rm PR,tree}\right)^{-1}
=
-4.2108016444\times10^{-5}.
\end{equation}
The central objective of the subsequent electromagnetic derivations is to demonstrate that native radiative boundary leakage naturally generates a physical correction of precisely this scale, emerging entirely from first principles without phenomenological adjustment.

\subsection{Tree-Level Electroweak Seed and Pre-Radiative Initialization}
\label{subsec:priii-tree-electroweak-seed}

The high-resolution electromagnetic baseline established above acts as the geometric seed for the electroweak sector, fixing the exact initial state prior to weak-scale transport and neutral-channel refinement. Propagating the exact tree-level fine-structure value,
\begin{equation}
\alpha_{\rm PR,tree}=\left(137.036041314016444\right)^{-1},
\end{equation}
the architecture analytically reconstructs the bare, pre-radiative gauge couplings:
\begin{align}
 e_{\rm PR} &=0.30282207421182286581809072020845327913143244571434,\\
 g_{\rm PR} &=0.62957484689764151178346495625282724825379638851140,\\
 g'_{\rm PR} &=0.34540199548414150920957567770984563383700364736773.
\end{align}

Coupling this continuous gauge sector to the inherited electroweak displacement scale,
\begin{equation}
v_{\rm EW}^{\rm PR}=246.21959589022453\ {\rm GeV},
\end{equation}
the framework generates the corresponding tree-level weak-mass baseline:
\begin{align}
M_{W,0}^{\rm PR}&=77.506832192893635832893671080594197560828951119835\ {\rm GeV},\\
M_{Z,0}^{\rm PR}&=88.40509587274585732715680415742085114480023483002\ {\rm GeV},\\
\rho_{\rm EW}^{(0)}&=1.
\end{align}

We note that these initial mass parameters do not represent the final phenomenological predictions of the theory. Rather, they constitute the mathematically exact pre-radiative geometric seed. As demonstrated in the ensuing derivations, the C1, C2, and C3 electroweak branches dynamically transport and refine this seed, incorporating necessary self-energy dynamics and neutral-channel corrections to elevate the baseline into the final, high-precision electroweak physical observables.

\subsection{Gauge-Null Quotient and Physical Scalar Isolation}
\label{subsec:priii-gauge-null-quotient-preview}

To evaluate and interpret the radiative determinant, it is mathematically necessary to isolate the physical scalar degrees of freedom from the unphysical gauge-null directions. Expanding the scalar sector in the standard basis,
\begin{equation}
(h_A,\pi_1,\pi_2,\pi_3),
\end{equation}
the corresponding symbolic Hessian spectrum evaluates to
\begin{equation}
\{H_{AA},0,0,0\}.
\end{equation}
The three degenerate null directions correspond exactly to the Goldstone modes associated with the broken gauge quotient,
\begin{equation}
(SU(2)_L\times U(1)_Y)/U(1)_{\rm em},
\end{equation}
leaving the physical scalar quotient entirely restricted to the radial amplitude direction, $h_A$. The dynamical stability of this symmetry-breaking configuration is strictly guaranteed by the positive-definite curvature condition,
\begin{equation}
H_{AA}=8\beta_A A_0^2>0,
\end{equation}
which requires both $\beta_A>0$ and $A_0^2>0$.

The neutral gauge sector geometry is locked to enforce a  massless photon trajectory orthogonal to a massive, positive-definite $Z$ direction. Projected into the $[W^3,B]$ gauge basis, the inherited weak mixing angle provides the rotational coefficients:
\begin{align}
\sin\theta_W^{\rm PR}&=0.480994556412220740217768765489223953539786055779711286076093,\\
\cos\theta_W^{\rm PR}&=0.876723580555360105457398073670122851235684044309931260035474.
\end{align}
By enforcing that the photon eigenvalue remains zero while the tree-level $Z$ eigenvalue is only positive, this quotient procedure formally prevents the subsequent radiative integration from artificially conflating unphysical gauge-null artifacts with genuine physical scalar curvature.

With the physical scalar and gauge-null directions separated, the inherited
baseline used by the finite-tier fine-structure calculation is now frozen for reproducibility.  This initialization fixes the PR-I spectral operators and boundary parameters, the declared $N_{\rm gen}^{\rm PR}=3$ realization, the pre-radiative electroweak seed, and the high-resolution tree baseline of $137.036041314016444\ldots$.  Empirical references are excluded from the generation map.  This makes the implemented determinant, charged-mode inventory, spectral kernel, weights, and subtractions a fixed no-fit finite-tier class.  The resulting $D_1+D_2$ value is compared with data only as a post-generation diagnostic; changing any registered kernel or subtraction defines a different class rather than a second solution of this one.

\section{Alpha and Electromagnetic Radiative Evaluation}
\label{sec:priii-alpha-radiative-closure}

The preceding section fixed the inherited PR-I/PR-II boundary data, the
high-resolution tree value of the compact electromagnetic normalization, and the exclusion of the diagnostic fine-structure reference from the generation map.  This section evaluates the declared PR-III electromagnetic relation. It does not fit \(\alpha\), and the later diagnostic displacement is not used to select the equation, coefficient, or operator class.

The starting point is the high-resolution tree baseline
\begin{equation}
\left(\alpha_{\rm PR,tree}\right)^{-1}
=
137.036041314016444 ,
\end{equation}
with the physical branch written as
\begin{equation}
\left(\alpha_{\rm PR,phys}\right)^{-1}
=
\left(\alpha_{\rm PR,tree}\right)^{-1}
+
\Delta\alpha_{\rm PR,rad}^{-1}.
\end{equation}
The radiative term is generated from the compact electroweak boundary deficit, the charged-mode inventory, and the PR spectral kernel.  The diagnostic fine-structure reference enters only after this construction has been evaluated.

\subsection{Radiative Determinant and Extraction Convention}
\label{subsec:priii-radiative-determinant-extraction}

The one-loop PR radiative architecture is organized by a reference-normalized supertrace determinant,
\begin{equation}
\Delta\Gamma_{\rm PR}^{(1)}[B]
=
\frac12
{\rm STr}_{\rm PR}^{\prime}
\log\!\left[
H_{\rm PR}[B]\,H_{\rm PR}[0]^{-1}
\right].
\label{eq:priii-reference-normalized-supertrace}
\end{equation}
The prime indicates that gauge-null modes and exact zero modes are either quotient-removed or reference-normalized.  In block form,
\begin{align}
\Delta\Gamma_{\rm PR}^{(1)}
=&\;
\frac12 {\rm Tr}_{\rm scalar}^{\prime}
\log\!\left(H_A/H_{A0}\right)
+
\frac12 {\rm Tr}_{\rm vector}^{\prime}
\log\!\left(O_V/O_{V0}\right) \nonumber\\
&\;
-
{\rm Tr}_{\rm ghost}^{\prime}
\log\!\left(M_{\rm gh}/M_{{\rm gh}0}\right)
-
{\rm Tr}_{\rm fermion}^{\prime}
\log\!\left(D_F/D_{F0}\right).
\end{align}
The physical scalar block is the quotient-retained radial amplitude direction \(H_A=H_{AA}\), while the gauge-null scalar directions have already been removed.  The photon is treated as the residual massless \(U(1)_{\rm em}\) background, not as a massive internal determinant mode.  The charged weak-vector, ghost, charged Goldstone partner, lepton, and quark sectors enter only through their allowed charged contributions.

The electromagnetic extraction convention is fixed by the coefficient of the residual background kinetic term,
\begin{equation}
\Delta\Gamma_{\rm PR}^{(1)}[F]
\supset
-\frac14\Delta Z_A^{\rm PR}
\int d^4x\,F_{\mu\nu}F^{\mu\nu}.
\end{equation}
The corresponding shift in the inverse fine-structure normalization is
\begin{equation}
\Delta\alpha_{\rm PR,rad}^{-1}
=
4\pi\,\Delta Z_A^{\rm PR}.
\label{eq:priii-alpha-radiative-shift}
\end{equation}
This convention is fixed before the numerical equation is evaluated.

\subsection{Charged-mode Inventory}
\label{subsec:priii-charged-mode-inventory}

Only modes carrying residual electromagnetic charge contribute directly to \(\Delta Z_A^{\rm PR}\).  The generic charged-mode structure is
\begin{equation}
\Delta Z_A^{\rm PR}
=
\sum_i
\sigma_i n_i Q_i^2 K_i^{\rm PR},
\label{eq:priii-charged-mode-supertrace}
\end{equation}
where \(\sigma_i\) is the supertrace sign, \(n_i\) is the multiplicity, \(Q_i\) is the residual electromagnetic charge, and \(K_i^{\rm PR}\) is the PR spectral kernel for that sector.

The charged weak vectors \(W^\pm\) contribute a charge-square sum of \(2\).  The charged electroweak ghost pair also carries charge-square sum \(2\), with the opposite ghost sign required by the gauge convention.  Gauge-fixing Goldstone partners may appear only as conditional partners of the vector/ghost block and are not counted as independent physical scalar modes.  The charged leptons contribute charge-square sum \(3\).  The color-resolved up-type quarks contribute \(4\), and the color-resolved down-type quarks contribute \(1\).  Thus the charged fermion charge-square sum is
\begin{equation}
\sum_{\rm charged\ fermions} Q_i^2 = 8,
\end{equation}
or \(8/3\) per generation.  Neutral modes, including the photon background, \(Z\), neutrinos, the neutral radial scalar, and gluons, have no direct \(Q^2\) contribution to the present electromagnetic extraction.

\subsection{PR Spectral Kernel}
\label{subsec:priii-pr-spectral-kernel}
To evaluate the physical radiative shift generated by the charged-mode inventory, the framework integrates over the internal fluctuation spectrum.  The declared finite-tier construction represents that integration by a fixed PR spectral-kernel class.  Its heat-kernel coefficients, weights, subtraction functions, domain, and power counting are registered as part of the admissibility definition.  The kernel is
\begin{equation}
K_i^{\rm PR}
=
\frac{C_i^{\rm hk}}{16\pi^2}\,
I_i^{\rm PR},
\qquad
\textit{with}
\qquad
\Delta Z_A^{\rm PR}
=
\sum_i\sigma_i n_i Q_i^2 K_i^{\rm PR}.
\end{equation}
The regulator is not an arbitrary cutoff.  It is tied to the internal PR spectral gap.  With
\begin{equation}
\mu_n^2=\lambda_n-\lambda_0,
\qquad
\mu_n^2\geq \left(\mu_{\min}^{\rm HR}\right)^2>0,
\end{equation}
the admissible kernel class has the schematic form
\begin{equation}
I_i^{\rm PR}(\tau_i)
=
\sum_{n\in S_i}\omega_{i,n}^{\rm PR}
\left[
\log\!\left(1+\frac{\tau_i}{\mu_n^2}\right)
-
R_i(\tau_i;\mu_n^2)
\right].
\end{equation}
For the electromagnetic closure branch the reference scale is not a free normalization. It is fixed to the inherited weak displacement anchor,
\begin{equation}
\Lambda_{\rm ref}
=
\Lambda_{\rm EW}^{\rm PR}
=
173.67059834472832\ {\rm GeV}.
\label{eq:priii-alpha-reference-scale}
\end{equation}
The threshold variable is therefore
\begin{equation}
\tau_i
=
\frac{M_i^2}{\left(\Lambda_{\rm EW}^{\rm PR}\right)^2}.
\label{eq:priii-alpha-threshold-variable}
\end{equation}
The allowed masses \(M_i\) are likewise restricted to frozen PR values, PR-II generated mass-sector outputs, PR-III derived masses, or symbolic placeholders awaiting PR derivation. Empirical masses, fitted thresholds, or values chosen to force the fine-structure residual are forbidden as generation inputs. For the alpha branch the locked boundary anchors are
\begin{equation}
p_1^{\rm HR}=7.685346950896231\times 10^{-4},
\qquad
q_{\rm bc}^{\rm HR}=10.904981678435453,
\qquad
c_{\rm bc}=0.796684464847899.
\end{equation}
The high-resolution weak boundary deficit is therefore
\begin{equation}
\boxed{
\Delta_{\rm EW}^{\rm HR}
=
\frac{1-c_{\rm bc}}{q_{\rm bc}^{\rm HR}}
=
0.018644280306692899718928776428403028768291215822597.}
\label{eq:priii-delta-ew-hr}
\end{equation}

\subsection{Minimal Boundary-Leakage Correction}
\label{subsec:priii-minimal-boundary-leakage}
The calculation of the radiative fine-structure shift starts by isolating the primary geometric contribution, formally designated as the minimal boundary-leakage term. This correction arises from the interplay among the inherited structural parameters of the high-resolution radial boundary anchor, the refined weak boundary deficit, and the native weak mixing angle. The framework formally defines this leading-order leakage as:
\begin{equation}
D_1
=
-p_1^{\rm HR}
\Delta_{\rm EW}^{\rm HR}
\sin^2\theta_W^{\rm PR}.
\label{eq:priii-alpha-D1}
\end{equation}
Using the frozen weak-angle output and Eq.~\eqref{eq:priii-delta-ew-hr}, PR-III obtains
\begin{equation}
D_1
=
-3.3150449735433222932326442973740154803469215638087\times 10^{-6}  .
\end{equation}
The induced inverse-alpha correction is
\begin{equation}
\Delta\alpha_{\rm PR,D1}^{-1}
=
4\pi D_1
=
-4.1658083740813887216904843821118454991063065733008\times 10^{-5},
\end{equation}
so the minimal physical branch is
\begin{equation}
\left(\alpha_{\rm PR,D1}\right)^{-1}
=
137.035999655932703186112783095156178881545008936934266992 .
\end{equation}
Compared only afterward with the selected diagnostic reference, this first
correction accounts numerically for \(98.9314797011\%\) of the difference
between the frozen tree value and that reference and leaves the diagnostic
residual
\begin{equation}
4.49932703186112783095156178881545008936934266992\times 10^{-7}.
\end{equation}
This comparison is reserved exclusively for post-generation diagnostic
assessment.  The structural sign, scale, and admissible class are defined by the PR construction independently of that comparison.

\subsection{Three-Sheet Mode Refinement}
\label{subsec:priii-three-sheet-D2-refinement}

The finite-tier electromagnetic branch next applies the target-independent
three-sheet scaling built from the inherited generation count, $N_{\rm gen}^{\rm PR}=3$.  Within the declared three-sheet closure class, the
square-root multiplicity rule is
\begin{equation}
\epsilon_2^{\rm PR}
=
\frac{\Delta_{\rm EW}^{\rm HR}}{\sqrt{N_{\rm gen}^{\rm PR}}},
\qquad
N_{\rm gen}^{\rm PR}=3.
\end{equation}

Numerically, we find the values to be:

\begin{table}[htbp]
\centering
\caption{Mode-resolved boundary leakage corrections and inverse fine-structure evaluation.}
\label{tab:alpha-refinement-steps}
\renewcommand{\arraystretch}{1.8}
\begin{tabular}{>{\raggedright\arraybackslash}p{0.4\textwidth} l}
\toprule
\textbf{Radiative Term} & \textbf{Generated Value} \\
\midrule
$\epsilon_2^{\rm PR}$ & 
{\small $\begin{aligned}[t]
 & 1.0764280253915984059993061466845953623 \\
& 291973168297815611743348884979166980206478 \times 10^{-2}

\end{aligned}$} \\
\midrule
$D_2 = D_1\epsilon_2^{\rm PR}$ & 
{\small $\begin{aligned}[t]
& {-3.5684073149555819954984631935783837502999439569} \\
& 8611894343571143823853634129916305743510899 \times 10^{-8}
\end{aligned}$} \\
\midrule
$\Delta Z_{A,D1D2}^{\rm PR} = D_1+D_2$ & 
{\small $\begin{aligned}[t]
& {-3.350729046692878113187628929309799317849} \\
& 92100337851630786204253710293778758370074941617298 \times 10^{-6}
\end{aligned}$} \\
\midrule
$\Delta\alpha_{D1D2}^{-1} = 4\pi(D_1+D_2)$ & 
{\small $\begin{aligned}[t]
& {-4.2106503029041108653898383405364322362509} \\
& 9844630214437314151444232206853445051700990393453 \times 10^{-5}
\end{aligned}$} \\
\bottomrule
\end{tabular}
\end{table}

Evaluating the declared mode-resolved boundary-leakage corrections on the
frozen high-resolution tree baseline gives the following finite-tier result. Its inputs are the inherited PR internal geometry, structural boundary deficit, and declared three-sheet scaling, and none is selected from the diagnostic fine-structure value.  This establishes reproducibility and no-fit provenance for the displayed calculation.  Under the completed selector rules proved in PR-IV, alterations of the registered $D_1/D_2$ operator data are out of class, while equivalent rewritings represent the same equation:
\begin{equation}
\boxed{
\begin{split}
\left(\alpha_{\rm PR,phys}\right)^{-1} = {} & 137.03599920751341495889134610161659463567763749 \\
& 0015536978556268584855576779314655494829901.
\label{eq:priii-alpha-phys-final}
\end{split}}
\end{equation}

\subsection{Precision Status}
\label{subsec:priii-alpha-precision-status}
To evaluate the predictive fidelity and numerical accuracy of the derived fine-structure constant, we subject the first-principles geometric output to an empirical confrontation. For this baseline comparison, the selected current empirical diagnostic reference and its associated experimental uncertainty are given by:

\begin{equation}
\alpha_{\rm diag}^{-1}=137.035999206,
\qquad
\sigma_{\rm diag}=1.1\times 10^{-8}.
\end{equation}
This reference has not entered the construction of Eq.~\eqref{eq:priii-alpha-phys-final}.  It is used only for the post-generation diagnostic residual,
\begin{equation}
\begin{split}
\Delta_{\rm diag}
=
\left(\alpha_{\rm PR,phys}\right)^{-1}
-
\alpha_{\rm diag}^{-1}
= {} &
1.51341495889134610161659463567763749001553 \\
& 6978556268584855576779314655494829901\times 10^{-9}.
\end{split}
\end{equation}
Equivalently,
\begin{equation}
\boxed{
\frac{\Delta_{\rm diag}}{\sigma_{\rm diag}}
=
+0.1376 ,}
\end{equation}
so the generated value lies inside the selected one-sigma diagnostic band. As a post-generation descriptive comparison only, the $D_1+D_2$ branch accounts for
\begin{equation}
\boxed{
99.9964058744945\%}
\end{equation}
of the high-resolution tree-to-diagnostic displacement.  Relative to the CODATA 2022 \cite{codata2022} recommended-value comparison, the same generated branch remains inside two sigma.

\subsection{Finite-Tier Status of the Electromagnetic Branch}
\label{subsec:priii-alpha-closure-status}

The PR-III electromagnetic equation is reproducibly evaluated at the declared finite tier.  The residual compact electromagnetic boundary inherited from PR-I/PR-II is carried from the tree normalization to the following no-fit finite-tier value:
\begin{equation}
\boxed{
\begin{split}
\left(\alpha_{\rm PR,tree}\right)^{-1}
\longrightarrow
\left(\alpha_{\rm PR,phys}\right)^{-1}
= {} &
137.035999207 \dots
\end{split}
}
\end{equation}
The construction uses the high-resolution boundary constants, weak boundary deficit, weak-angle output, generation count, charged-mode supertrace inventory, and internal PR spectral kernel.  It does not use the diagnostic fine-structure reference as a generation input.

This closes the electromagnetic equation at the declared tier.  The residual against the selected reference is nonzero and lies below the supplied experimental uncertainty; it is a diagnostic output, not an adjustable coefficient.  The invariant operator basis, kernel weights, subtractions, and power counting are fixed elements of the PR-III admissibility domain.  An all-orders series or a differently regulated kernel is a different theorem domain and is not a competing solution of the finite-tier equation proved
here.

\section{Electroweak Scale Transport and Precision Closure}
\label{sec:priii-electroweak-closure}

The electromagnetic closure obtained in the preceding section supplies the low-energy boundary condition for the weak sector,
\begin{equation}
\left(\alpha_{\rm PR,phys}(0)\right)^{-1}
=
137.035999207\dots.
\end{equation}
PR-III now transports this generated quantity to the inherited electroweak displacement scale
\begin{equation}
\Lambda_{\rm EW}^{\rm PR}
=
173.67059834472832\ {\rm GeV},
\qquad
v_{\rm EW}^{\rm PR}
=
246.21959589022453\ {\rm GeV}.
\end{equation}
Neither scale is selected from the weak-boson diagnostic values.  Both are inherited PR quantities, fixed before the electroweak construction begins. The electroweak calculation proceeds in three branches.  The \(C_1\) branch performs the minimal compact-boundary transport and reconstructs the weak couplings and tree-form mass ledger at the electroweak scale.  The \(C_2\) branch introduces a generation-weighted charged neutral vector self-energy split.  The \(C_3\) branch supplies the next neutral-channel correction while leaving the charged branch unchanged.  The diagnostic values of \(M_W\), \(M_Z\), and \(G_F\) enter only after each branch has been generated.

\subsection{Electromagnetic-to-electroweak Transport}
\label{subsec:priii-ew-scale-transport}

The PR transport equation is written as
\begin{equation}
\left(\alpha_{\rm PR}(\mu)\right)^{-1}
=
\left(\alpha_{\rm PR}(0)\right)^{-1}
-
\Delta_{\rm run}^{\rm PR}(0\rightarrow\mu).
\label{eq:priii-ew-alpha-transport}
\end{equation}
At the level of the full spectral construction,
\begin{equation}
\Delta_{\rm run}^{\rm PR}
=
\sum_i B_i^{\rm PR}L_i^{\rm PR},
\end{equation}
where the inventory preserves the charged-mode content of the electromagnetic supertrace.  Charged weak vectors, their gauge partners, charged leptons, and color-resolved quarks contribute; neutral modes have no direct electromagnetic \(Q^2\) contribution.  The spectral transport kernel is reference-normalized and tied to the PR gap,
\begin{equation}
\mu_n^2\geq
\left(\mu_{\min}^{\rm HR}\right)^2
=
3.053016666732689,
\end{equation}
with the matching scale fixed to \(\Lambda_{\rm EW}^{\rm PR}\).  Empirical weak masses and fitted thresholds are not admissible transport inputs. The minimal compact-boundary transport relation is
\begin{equation}
\Delta_{\rm run}^{C_1}
=
q_{\rm bc}^{\rm HR}c_{\rm bc},
\label{eq:priii-ew-C1-running}
\end{equation}
where
\begin{equation}
q_{\rm bc}^{\rm HR}=10.904981678435453,
\qquad
c_{\rm bc}=0.796684464847899.
\end{equation}
This result in 
\begin{equation}
\Delta_{\rm run}^{C_1}
=
8.687829492660492292065934163247,
\end{equation}
and Eq.~\eqref{eq:priii-ew-alpha-transport} gives
\begin{equation}
\begin{split}
\left(\alpha_{\rm PR}^{C_1}(\Lambda_{\rm EW}^{\rm PR})\right)^{-1}
= {} &
128.348169714852922666825411938369594635\\
&67763749001553697855626858485557677931466 .
\label{eq:priii-ew-alpha-C1}
\end{split}
\end{equation}

The transported electromagnetic coupling and the electroweak couplings are then reconstructed from the inherited weak angle,
\begin{align}
e_{\rm PR}^{C_1}
&=
\sqrt{4\pi\alpha_{\rm PR}^{C_1}}
=
0.3129032630130971839408029965751121711\ldots,
\\
g_{\rm PR}^{C_1}
&=
\frac{e_{\rm PR}^{C_1}}
{\sqrt{\sin^2\theta_W^{\rm PR}}}
=
0.6505338965726955536662186423635601421\ldots,
\\
g_{\rm PR}^{\prime\,C_1}
&=
\frac{e_{\rm PR}^{C_1}}
{\sqrt{1-\sin^2\theta_W^{\rm PR}}}
=
0.3569007038853554861535860269366292845\ldots,
\end{align}
with
\begin{equation}
\sin^2\theta_W^{\rm PR}=0.231355763298189.
\end{equation}

\subsection{The \(C_1\) Weak-Mass Ledger}
\label{subsec:priii-ew-C1-ledger}

Having dynamically transported the high-precision electromagnetic fine-structure closure up to the electroweak boundary, the architecture now recouple this refined gauge sector to the invariant geometric displacement scale, $v_{\rm EW}^{\rm PR}$. This interaction reconstructs the physical gauge-boson masses and the Fermi coupling from the transported continuous couplings and the native symmetry-breaking kinematics. We designate this initial structural reconstruction as the $C_1$ baseline weak-mass ledger. Prior to integrating the necessary self-energy and neutral-channel radiative loops, the $C_1$ relations are formally defined by:
\begin{align}
\left(M_W^{C_1}\right)^2
&=
\frac14\left(g_{\rm PR}^{C_1}\right)^2
\left(v_{\rm EW}^{\rm PR}\right)^2,
\\
\left(M_Z^{C_1}\right)^2
&=
\frac14\left[
\left(g_{\rm PR}^{C_1}\right)^2
+
\left(g_{\rm PR}^{\prime\,C_1}\right)^2
\right]
\left(v_{\rm EW}^{\rm PR}\right)^2,
\\
G_F^{\rm PR}
&=
\frac{1}{\sqrt{2}\left(v_{\rm EW}^{\rm PR}\right)^2},
\\
\rho_{\rm EW}^{C_1}
&=
\frac{\left(M_W^{C_1}\right)^2}
{\left(M_Z^{C_1}\right)^2\cos^2\theta_W^{\rm PR}} .
\end{align}
Numerically,
\begin{align}
M_W^{C_1}
&=
80.0870965635111\ {\rm GeV},
\\
M_Z^{C_1}
&=
91.3481721488317\ {\rm GeV},
\\
G_F^{\rm PR}
&=
1.166379220175995\times10^{-5}\ {\rm GeV}^{-2},
\\
\rho_{\rm EW}^{C_1}
&=
1 .
\end{align}

The \(C_1\) branch is internally consistent and preserves the tree-form \(\rho\) identity.  Its post-generation comparison is recorded only as a diagnostic: \(G_F\) lies within one standard deviation, whereas the \(W\) and \(Z\) values do not close uniformly.  This comparison neither generates nor fixes the next equation.  Any charged--neutral refinement must be justified independently by the non-Abelian representation and a target-independent projector-trace or operator-basis theorem.

\subsection{Charged and Neutral Vector Branches}
\label{subsec:priii-ew-angle-only-obstruction}

Before introducing a self-energy correction, PR-III tests whether a single shift in the weak angle could close both vector masses.  Holding the generated electromagnetic coupling and displacement scale fixed, the \(W\) diagnostic would require
\begin{equation}
\sin^2\theta_W\big|_W
=
0.2297344528823705608\ldots,
\end{equation}
whereas the \(Z\) diagnostic would require
\begin{equation}
\sin^2\theta_W\big|_Z
=
0.2325249689814497325\ldots .
\end{equation}
The required shifts have opposite signs,
\begin{align}
\Delta\sin^2\theta_W\big|_W
&=
-0.0016213104158184392\ldots,
\\
\Delta\sin^2\theta_W\big|_Z
&=
+0.0011692056832607325\ldots,
\end{align}
with spread
\begin{equation}
2.79051609907917\times10^{-3}.
\end{equation}
A single weak-angle displacement gives two different post-generation central-value reconstructions.  This is a diagnostic distinction within the
angle-only comparison class and is not used to infer the form, coefficient, or admissible class of the subsequent \(C_2\) equation.  The charged--neutral structure and normalization are defined independently at the representation and canonical-closure level.

\subsection{Generation-weighted vector self-energy: the \(C_2\) branch}
\label{subsec:priii-ew-C2-vector-self-energy}

The declared finite-tier \(C_2\) relation uses the same weak-boundary deficit and generation count that enter the electromagnetic refinement.  Its charged--neutral coefficient pair \((2,-1)\) is a target-independent PR closure at the stated tier.  Operators with an independent coefficient or a different kernel are excluded by the completed admissibility rules and belong to a different equation class.  Define
\begin{equation}
\epsilon_V^{\rm PR}
=
\frac{\Delta_{\rm EW}^{\rm HR}}
{\sqrt{N_{\rm gen}^{\rm PR}}},
\qquad
N_{\rm gen}^{\rm PR}=3,
\end{equation}
so that
\begin{equation}
\epsilon_V^{\rm PR}
=
0.0107642802539159840599930614668459536\ldots .
\end{equation}
The \(C_2\) vector self-energies are
\begin{equation}
\Pi_W^{C_2}
=
\frac{2}{N_{\rm gen}^{\rm PR}}\epsilon_V^{\rm PR},
\qquad
\Pi_Z^{C_2}
=
-\frac{1}{N_{\rm gen}^{\rm PR}}\epsilon_V^{\rm PR}.
\label{eq:priii-ew-C2-self-energies}
\end{equation}
Numerically,
\begin{equation}
\Pi_W^{C_2}
=
0.0071761868359439894\ldots,
\qquad
\Pi_Z^{C_2}
=
-0.0035880934179719947\ldots .
\end{equation}

The corrected vector masses are
\begin{equation}
M_W^{C_2}
=
M_W^{C_1}\sqrt{1+\Pi_W^{C_2}},
\qquad
M_Z^{C_2}
=
M_Z^{C_1}\sqrt{1+\Pi_Z^{C_2}},
\end{equation}
which give
\begin{align}
M_W^{C_2}
&=
80.3739428518621\ {\rm GeV},
\\
M_Z^{C_2}
&=
91.1841419901086\ {\rm GeV},
\\
\rho_{\rm EW}^{C_2}
&=
1.01080304257989 .
\end{align}
The \(C_2\) split reduces the absolute \(W\) and \(Z\) residuals relative to \(C_1\) by factors of approximately \(59.48\) and \(46.43\), respectively.  At this stage \(M_W\) and \(G_F\) lie inside one standard deviation, while \(M_Z\) lies inside two standard deviations but remains outside one.

\subsection{Neutral-channel \(D_3\): exact group factor and canonical-closure uniqueness}
\label{subsec:priii-ew-C3-neutral-refinement}

At \(C_3\) the charged branch and photon-null direction are held fixed, so the allowed neutral correction is classified before any diagnostic comparison. The \(C_2\) residual is reported only after this construction and does not select its coefficient.  Define
\begin{equation}
\rho_{\rm PR}
:=
\frac{\left(\epsilon_V^{\rm PR}\right)^2}
{N_{\rm gen}^{\rm PR}}
>0
\label{eq:priii-rho-pr-definition}
\end{equation}
At the declared fixed Lorentz/momentum kernel, equip the real gauge-index coefficient space with the canonical kinetic inner product and take the ordered field basis \((W^1,W^2,Z,A)\) to be orthonormal.  Let \(P_Z\) denote the resulting orthogonal projector onto the normalized physical
\(Z\) direction.

\begin{proposition}[Rank-one reduction under the stated \(C_3\) structural gates] \label{prop:priii-d3-structural-classification}
Let \(D_3\) be a real symmetric linear correction on the four-dimensional field space.  Suppose that it leaves the charged \(C_2\) branch unchanged and preserves the photon-null condition,
\begin{equation}
D_3W^1=D_3W^2=D_3A=0,
\label{eq:priii-d3-structural-gates}
\end{equation}
and suppose that its inherited scale is \(\rho_{\rm PR}\).  Then there is one and only one
dimensionless scalar \(k\in\mathbb R\) such that
\begin{equation}
D_3(k)=\rho_{\rm PR}kP_Z.
\label{eq:priii-d3-fixed-kernel-family}
\end{equation}
The structural gates reduce every admissible tensor to this one-coordinate
normal form; the normalized-response conditions below determine that
coordinate.
\end{proposition}

\begin{proof}
The three vectors in Eq.~\eqref{eq:priii-d3-structural-gates} span a subspace \(K\) contained in
\(\ker D_3\).  Symmetry gives
\(\langle y,D_3x\rangle=\langle D_3y,x\rangle=0\) for every \(y\in K\), so
\(\operatorname{im}D_3\subseteq K^\perp=\operatorname{span}\{Z\}\).  Hence \(D_3=dP_Z\) for a
unique \(d\in\mathbb R\).  Since \(\rho_{\rm PR}>0\), there is a unique
\(k=d/\rho_{\rm PR}\).  Conversely, every operator in
Eq.~\eqref{eq:priii-d3-fixed-kernel-family} obeys the stated gates.  Therefore
the gates reduce the tensor problem to one scalar coordinate.  The remaining
normalized-response gates are imposed in
Theorem~\ref{thm:priii-unique-quadratic-response}, after which
Theorem~\ref{thm:priii-conditional-k-two} fixes that coordinate to \(k=2\).
\end{proof}

The exact factor available from the PR-II charge algebra is the following.  Let
\begin{equation}
\mathcal H_{\rm ch}
=
\operatorname{span}_{\mathbb C}\{T^+,T^-\},
\qquad
q
:=
\left.\operatorname{ad}_Q\right|_{\mathcal H_{\rm ch}},
\label{eq:priii-charged-adjoint-definition}
\end{equation}
where the charged basis is orthonormal and \(Q=T_3+Y/2\).  The hypercharge generator commutes
with the \(SU(2)\) adjoint action on this subspace.

\begin{proposition}[Exact charged-adjoint trace]
\label{prop:priii-exact-charged-adjoint-trace}
With the PR-II generator normalization,
\begin{equation}
qT^+=T^+,
\qquad
qT^-=-T^-,
\qquad
\operatorname{Tr}_{\rm ch}(q^\dagger q)=2.
\label{eq:priii-exact-group-factor-two}
\end{equation}
This result contains no fitted coefficient and no continuous parameter.
\end{proposition}

\begin{proof}
The ladder relations are \([T_3,T^\pm]=\pm T^\pm\).  The commuting hypercharge term does not
alter them, so the matrix of \(q\) in the ordered basis \((T^+,T^-)\) is
\(\operatorname{diag}(1,-1)\).  Consequently \(q^\dagger q=I_2\), and its trace is exactly two.
\end{proof}

The minimal PR response class uses only the inherited scale, the physical
projector, and a quadratic functional of the normalized charged-adjoint
operator.  The functional itself is unique under the structural properties of
a spectral response.

\begin{theorem}[Unique normalized quadratic charge response]
\label{thm:priii-unique-quadratic-response}
Let \(\mathcal F\) assign a nonnegative real number to every normal
finite-dimensional charge operator and satisfy, for every dimension-compatible
unitary \(U\) and every \(a\in\mathbb C\),
\begin{align}
\mathcal F(UqU^\dagger)&=\mathcal F(q),
&\mathcal F(q_1\oplus q_2)&=\mathcal F(q_1)+\mathcal F(q_2),\nonumber\\
\mathcal F(aq)&=|a|^2\mathcal F(q),
&\mathcal F([1])&=1.
\label{eq:priii-canonical-response-conditions}
\end{align}
These conditions respectively impose charged-basis invariance,
orthogonal-mode additivity, quadratic homogeneity, and unit-charge
normalization.  Then, uniquely,
\begin{equation}
\mathcal F(q)=\operatorname{Tr}(q^\dagger q).
\label{eq:priii-unique-response-functional}
\end{equation}
\end{theorem}

\begin{proof}
Because \(q\) is normal, a unitary transformation diagonalizes it with
eigenvalues \(\lambda_i\).  Basis invariance and direct-sum additivity reduce
\(\mathcal F(q)\) to the sum of its one-dimensional mode values.  Homogeneity
and unit normalization give
\(\mathcal F([\lambda_i])=|\lambda_i|^2\), hence
\begin{equation}
\mathcal F(q)=\sum_i|\lambda_i|^2
=\operatorname{Tr}(q^\dagger q).
\end{equation}
Every step is forced, proving uniqueness.
\end{proof}

Define the target-independent fixed-kernel response-equation class before
selecting its member:
\begin{equation}
\mathfrak E_{C_3}
=
\left\{
 E_{\mathcal F}(D;q):=
 D-\rho_{\rm PR}\mathcal F(q)P_Z=0
 \;\middle|\;
 \mathcal F\text{ satisfies
 Eq.~\eqref{eq:priii-canonical-response-conditions}}
\right\}.
\label{eq:priii-c3-response-equation-class}
\end{equation}
The domain of every member is the complete set of normal finite-dimensional
charge operators used in
Theorem~\ref{thm:priii-unique-quadratic-response}; agreement only on the one
matrix $q=\operatorname{diag}(1,-1)$ is not equation equivalence.  The theorem
therefore derives, rather than assumes, the unique neutral response
law in this class:
\begin{equation}
\boxed{
\mathsf H_Z:\qquad
D_3^{\rm PR}
=
\rho_{\rm PR}\,
\operatorname{Tr}_{\rm ch}(q^\dagger q)P_Z .
}
\label{eq:priii-neutral-response-hypothesis}
\end{equation}
Here \(\mathsf H_Z\) is the conclusion of the four response conditions.  It
preserves the charged \(C_2\) branch and photon nullity,
uses only the inherited scale \(\rho_{\rm PR}\), and assigns unit weight to a
single normalized charged mode.  It is a fixed, target-independent logical
closure principle of PR-III, not a fitted parameter or a new P1-level
foundational postulate.  A complete background-field Hessian satisfying these
same gates is an equivalent microscopic presentation of the already fixed
response law.

Here uniqueness is a statement about equations modulo physical equivalence,
not about typography.  Within the declared \(C_3\) class, two residual equations
are operator-equivalent when an allowed normalized field or basis change and an
everywhere-invertible residual map relate them on the complete admissible
domain.  They are physically equivalent when this relation preserves the full
neutral tensor, quotient solution space, and every registered observable.
Matching one mass value is not sufficient.  An alternative formula is a
distinct \(C_3\) equation only if it satisfies the fixed-kernel classification,
charged-sector preservation, photon nullity, and all four normalized-response
conditions while remaining physically inequivalent.

\begin{theorem}[Canonical-closure uniqueness of the \(C_3\) coefficient]
\label{thm:priii-conditional-k-two}
In the target-independently defined response-equation class
$\mathfrak E_{C_3}$ of
Eq.~\eqref{eq:priii-c3-response-equation-class}, with the PR-II charge algebra,
the inherited scale in Eq.~\eqref{eq:priii-rho-pr-definition}, and the
structural gates in
Proposition~\ref{prop:priii-d3-structural-classification}, the only member of
the family in Eq.~\eqref{eq:priii-d3-fixed-kernel-family} is
\begin{equation}
k=2,
\qquad
D_{3,Z}^{\rm PR}
=
\frac{2}{N_{\rm gen}^{\rm PR}}
\left(\epsilon_V^{\rm PR}\right)^2.
\label{eq:priii-ew-D3-neutral}
\end{equation}
No free parameter remains in this declared class.
\end{theorem}

\begin{proof}
Theorem~\ref{thm:priii-unique-quadratic-response} gives
$\mathcal F(q)=\operatorname{Tr}(q^\dagger q)$ for every member of
$\mathfrak E_{C_3}$.  Proposition~\ref{prop:priii-exact-charged-adjoint-trace}
then gives \(D_3^{\rm PR}=2\rho_{\rm PR}P_Z\).  Comparison with
Eq.~\eqref{eq:priii-d3-fixed-kernel-family}, followed by division by the strictly positive
\(\rho_{\rm PR}\), gives \(k=2\).  Equivalently,
\begin{equation}
\left\|D_3(k)-2\rho_{\rm PR}P_Z\right\|_{F}^{2}
=
\rho_{\rm PR}^{2}(k-2)^2,
\end{equation}
where \(\|P_Z\|_F^2=1\).  This expression vanishes if and only if \(k=2\).
Therefore every in-class fixed-kernel equation either has the positive
normalized-response defect $\rho_{\rm PR}^2(k-2)^2$, or has \(k=2\) and equals
\(2\rho_{\rm PR}P_Z\).  Algebraically different residual maps related by a
ledger-preserving invertible transformation on the complete charge-operator
domain are equivalent and do not constitute additional equations.
\end{proof}

\begin{corollary}[Equation-level exhaustion of the canonical \(C_3\) class]
\label{cor:priii-c3-equation-exhaustion}
Let $E_{\operatorname{Tr}}$ denote the residual map obtained from
$\mathcal F(q)=\operatorname{Tr}(q^\dagger q)$.  Then
\begin{equation}
 \mathfrak E_{C_3}/\!\sim_{\rm op}
 =\{[E_{\operatorname{Tr}}]_{\rm op}\}.
 \label{eq:priii-c3-equation-singleton}
\end{equation}
Thus there is no second inequivalent \(C_3\) equation in this class, and all
members induce the same physical quotient solution space.  A broader
higher-derivative, nonlocal, additional-field, independent-second-jet, or
independent-Wilson-coefficient equation is outside this theorem and is not an
in-class alternative.
\end{corollary}

A complete physical-$Z$ background family may represent $\mathsf H_Z$ through
the displayed determinant.  Within the declared class this presentation is
required to reduce to the same canonical residual law; it cannot introduce a
second coefficient or equation.

\begin{lemma}[Second variation of a reference-normalized determinant]
\label{lem:priii-determinant-hessian}
Let \(z\) be a normalized physical-\(Z\) background coordinate and let
\begin{equation}
\Gamma(z)
=
\sum_i\eta_i\operatorname{Tr}'_i
\log\!\left(H_i(z)H_i(0)^{-1}\right),
\label{eq:priii-general-neutral-determinant}
\end{equation}
where \(\eta_i\) includes the statistics sign and determinant weight.  Assume that the primed
domains are fixed near \(z=0\), every \(H_i(0)\) is invertible on its primed domain, the families
are twice differentiable, and the relative operators
\(A_i(z):=H_i(z)H_i(0)^{-1}\) satisfy \(A_i(z)-I\), \(A_i'(z)\), and
\(A_i''(z)\) in the determinant/trace class required to differentiate the displayed trace on a
common logarithm branch.  Assume cyclicity is valid and the regularization adds no
multiplicative anomaly.  With
\begin{equation}
G_i=H_i(0)^{-1},
\qquad
V_i=H_i'(0),
\qquad
W_i=H_i''(0),
\end{equation}
one has
\begin{equation}
\Gamma''(0)
=
\sum_i\eta_i\operatorname{Tr}'_i
\left(G_iW_i-G_iV_iG_iV_i\right).
\label{eq:priii-exact-neutral-hessian}
\end{equation}
\end{lemma}

\begin{proof}
Under the stated hypotheses,
\(\frac{d}{dz}\operatorname{Tr}'\log A_i=\operatorname{Tr}'(A_i^{-1}A_i')\).
Since \(A_i(0)=I\), \(A_i'(0)=V_iG_i\), and \(A_i''(0)=W_iG_i\), differentiating once more gives
\begin{equation}
\left.\frac{d^2}{dz^2}\operatorname{Tr}'\log A_i(z)\right|_{0}
=
\operatorname{Tr}'\!\left(W_iG_i-V_iG_iV_iG_i\right).
\end{equation}
Cyclicity converts this expression to the corresponding summand in
Eq.~\eqref{eq:priii-exact-neutral-hessian}.
\end{proof}

Equation~\eqref{eq:priii-reference-normalized-supertrace} supplies the
determinant architecture, and the displayed operators instantiate its residual
electromagnetic background.  A complementary physical-$Z$ determinant
realization additionally specifies the complete $H_i(z)$, $V_i$, and $W_i$,
including the vector--ghost--Goldstone organization, matter contribution,
spectral normalization, and same-order operator ledger.  Under those data,
Eq.~\eqref{eq:priii-exact-neutral-hessian} provides the microscopic route to
Eq.~\eqref{eq:priii-neutral-response-hypothesis}.  The following broader family
characterizes the distinct second-jet comparison domain without introducing a
PR parameter or using numerical fitting.

\begin{proposition}[Broader fixed-kernel completion family]
\label{prop:priii-fixed-kernel-counterfamily}
For each fixed \(k\in\mathbb R\), let
\begin{equation}
X:=\frac{q^\dagger q}{2},
\qquad
H_k(z):=\exp\!\left(k\rho_{\rm PR}z^2X\right)
\quad\hbox{on }\mathcal H_{\rm ch}.
\label{eq:priii-neutral-counterfamily}
\end{equation}
Then \(H_k(0)=I\), \(H_k(z)\) is positive and analytic for real \(z\), and it preserves the same
charge algebra and exact group trace.  Nevertheless the corresponding reference-normalized
determinant
\begin{equation}
\Gamma_k(z)
:=
\frac12\operatorname{Tr}_{\rm ch}\log H_k(z)
=
\frac12k\rho_{\rm PR}z^2
\end{equation}
satisfies \(\Gamma_k''(0)=k\rho_{\rm PR}\).
\end{proposition}

\begin{proof}
The operator \(X=I_2/2\) is positive and has unit trace.  Functional calculus makes
\(H_k(z)\) positive and analytic, including for negative \(k\).  Since the logarithm of the
positive exponential is its self-adjoint exponent,
\begin{equation}
\Gamma_k(z)
=
\frac12 k\rho_{\rm PR}z^2\operatorname{Tr}_{\rm ch}X
=
\frac12 k\rho_{\rm PR}z^2,
\end{equation}
and two differentiations give the claim.
\end{proof}

Taking every other determinant block to be a \(z\)-independent spectator and defining the neutral
response extracted from this block by
\begin{equation}
D_3^{(k)}
:=
\Gamma_k''(0)P_Z
=
k\rho_{\rm PR}P_Z
\label{eq:priii-counterfamily-d3-response}
\end{equation}
embeds the entire classified family of Eq.~\eqref{eq:priii-d3-fixed-kernel-family} in the displayed
reference-normalized determinant architecture.

Thus \(k=1\), \(k=2\), and every other fixed value label different neutral
Hessians only after an independent second jet is admitted.  The PR-III
admissibility rules do not admit that extra datum.  These deliberately enlarged
abstract completions are therefore outside the PR equation class and do not
constitute additional solutions.  Inside the declared class, unit-mode
normalization fixes \(k=2\).

There is also a distinct physical-basis gate.  With
\(c:=\cos\theta_W^{\rm PR}\), \(s:=\sin\theta_W^{\rm PR}\), and the frozen PR-II angle satisfying
\(0<s,c<1\), PR-II uses
\begin{equation}
Z=cW^3-sB,
\qquad
A=sW^3+cB,
\qquad
c^2+s^2=1,
\end{equation}
and hence \(W^3=cZ+sA\).  Even if the charged-adjoint trace is embedded along the \(T_3\) gauge
direction, the literal tensor \(2P_{W^3}\) becomes
\begin{equation}
2P_{W^3}
=
2\begin{pmatrix}
c^2 & cs\\
cs & s^2
\end{pmatrix}_{(Z,A)},
\label{eq:priii-w3-to-physical-neutral-map}
\end{equation}
not \(2P_Z\).  The normalized physical \(Z\) map and cancellation of the photon
and mixed components are therefore independent admissibility gates, verified
by the source-level reconstruction below; the group trace is not used as a
substitute for those gates.

The source-level physical-\(Z\) coupling is reconstructed exactly as an
in-class consistency identity.

\begin{proposition}[Physical-\(Z\) connection reconstructed from PR-II]
\label{prop:priii-physical-z-connection}
Let \(t_Z:=T_3-s^2Q\), \(g_Z:=g/c\), and let
\(q_Z:=\operatorname{ad}_{g_Zt_Z}|_{\operatorname{span}\{T^+,T^-\}}\) be the
physical-\(Z\) charge operator on the charged weak-vector adjoint.  The PR-II neutral connection
satisfies
\begin{equation}
gW_\mu^3T_3+g'B_\mu\frac{Y}{2}
=
eA_\mu Q+g_ZZ_\mu t_Z .
\label{eq:priii-physical-z-connection}
\end{equation}
On the charged weak-vector adjoint,
\begin{equation}
[g_Zt_Z,T^\pm]=\pm gc\,T^\pm,
\qquad
\operatorname{Tr}_{\rm ch}
\!\left(q_Z^\dagger q_Z\right)
=2g^2c^2.
\label{eq:priii-physical-z-vector-trace}
\end{equation}
Consequently the normalized physical charge operator
\begin{equation}
\widehat q_Z:=(gc)^{-1}q_Z
\end{equation}
equals the dimensionless \(q=\operatorname{ad}_Q|_{\mathcal H_{\rm ch}}\) used in
Eq.~\eqref{eq:priii-charged-adjoint-definition}, and
\(\operatorname{Tr}_{\rm ch}(\widehat q_Z^\dagger\widehat q_Z)=2\).
Thus the bare trace two is obtained only after the physical vertex factor \(gc\) has been
factored into the background coordinate or spectral kernel.
\end{proposition}

\begin{proof}
Inverting the PR-II rotation gives \(W^3=sA+cZ\) and \(B=cA-sZ\).  Substitution into the
neutral connection gives the photon coefficient
\(gsT_3+g'cY/2=eQ\).  Using \(g'=gs/c\) and \(Y/2=Q-T_3\), the \(Z\) coefficient becomes
\begin{equation}
gcT_3-g's\frac{Y}{2}
=\frac{g}{c}(T_3-s^2Q)=g_Zt_Z.
\end{equation}
On the weak-vector adjoint \(Y=0\), hence \(Q=T_3\), \(t_Z=c^2T_3\), and
\([g_Zt_Z,T^\pm]=\pm gcT^\pm\).  Squaring the two eigenvalues gives
Eq.~\eqref{eq:priii-physical-z-vector-trace}; division by \(gc\) gives
\(\widehat q_Z=\operatorname{ad}_{T_3}|_{\mathcal H_{\rm ch}}=q\).
\end{proof}

The same reconstruction shows why the complete matter block cannot be silently omitted.  Put
\(x=s^2\) and sum the squared chiral charges \(t_Z=T_3-xQ\) over one PR-II generation,
including color multiplicity.  Directly from the PR-II charge ledger,
\begin{align}
S_{ZZ}^{(1)}(x)
&:=\sum_{f\,\mathrm{chiral}}n_c(f)\,t_Z(f)^2
=2-4x+\frac{16}{3}x^2
=\frac{16}{3}\left(x-\frac38\right)^2+\frac54>0,
\label{eq:priii-one-generation-z-charge-trace}
\\
S_{AZ}^{(1)}(x)
&:=\sum_{f\,\mathrm{chiral}}n_c(f)\,Q_f t_Z(f)
=2-\frac{16}{3}x .
\label{eq:priii-one-generation-az-charge-trace}
\end{align}
At the frozen PR-II value \(x=0.231355763298189\), both expressions are nonzero.  These charge
traces do not by themselves compute a loop kernel, but they prove that neither disappearance of
the matter response nor cancellation of the mixed \(AZ\) response follows from representation
algebra alone.

The exact boundary of the admissible operator class can now be isolated.  An
independently selectable physical-\(Z\) second jet, or seagull, crosses that
boundary.

\begin{theorem}[Exclusion of independent second-jet data]
\label{thm:priii-second-jet-obstruction}
Suppose a completion of the frozen determinant ledger fixes \(H_i(0)\), \(H_i'(0)\), the block
weights \(\eta_i\), and all frozen spectra and charge representations, but leaves
\(H_j''(0)\) unspecified for one common-domain \(C^2\) family of closed quadratic forms with
\(H_j^{(0)}(0)\ge mI\) and
\(H_j^{(0)}(z)\ge aH_j^{(0)}(0)\) near zero for constants \(m,a>0\), and with
\(\eta_j\ne0\).  Write \(H_j(0):=H_j^{(0)}(0)\).  Let \(X\) be a positive
finite-rank operator whose range lies
in the common form domain, commuting with the frozen charge action and satisfying
\(\operatorname{Tr}'X=1\).  For any fixed \(\lambda\in\mathbb R\), define locally, in
quadratic-form sense,
\begin{equation}
H_j^{(\lambda)}(z)
:=
H_j^{(0)}(z)
+\frac{\lambda\rho_{\rm PR}}{2\eta_j}z^2
\bigl(H_j^{(0)}(0)\bigr)^{1/2}X
\bigl(H_j^{(0)}(0)\bigr)^{1/2},
\label{eq:priii-second-jet-deformation}
\end{equation}
and leave every other block unchanged.  Then the deformation preserves the entire zero jet and
first jet, is a finite-rank relative-form perturbation that remains positive for sufficiently
small \(|z|\), and changes the determinant Hessian by
\begin{equation}
\Gamma_{\lambda}''(0)-\Gamma_0''(0)
=\lambda\rho_{\rm PR}.
\label{eq:priii-second-jet-hessian-shift}
\end{equation}
Consequently an independently selectable second jet supplies an additional
datum and lies outside the minimal-response class.  With the declared
minimal-response rule imposed, no such datum is available and \(k=2\) is the
sole admissible value.
\end{theorem}

\begin{proof}
The added term and its first derivative vanish at \(z=0\), whereas its second derivative is
\begin{equation}
\frac{\lambda\rho_{\rm PR}}{\eta_j}
H_j(0)^{1/2}XH_j(0)^{1/2}.
\end{equation}
In
Eq.~\eqref{eq:priii-exact-neutral-hessian}, the first-vertex term is therefore unchanged and the
new contribution is
\begin{equation}
\eta_j\operatorname{Tr}'\!\left[
H_j(0)^{-1}\frac{\lambda\rho_{\rm PR}}{\eta_j}
H_j(0)^{1/2}XH_j(0)^{1/2}\right]
=\lambda\rho_{\rm PR}\operatorname{Tr}'X
=\lambda\rho_{\rm PR}.
\end{equation}
The relative perturbation is the bounded finite-rank form
\((\lambda\rho_{\rm PR}/(2\eta_j))z^2X\).  The coercive bound remains positive whenever
\(\lvert\lambda\rho_{\rm PR}/(2\eta_j)\rvert z^2\lVert X\rVert<a\), so positivity is preserved
in a sufficiently small
neighborhood of \(z=0\).  The finite-rank support also makes the displayed cyclic trace
identity ordinary and anomaly-free on the deformed subspace.
\end{proof}

A broader effective-field-theory comparison also shows that electroweak gauge
invariance alone does not define the admissible PR class.  The parameter
\(\lambda\) below labels that comparison family and is not introduced into the
PR ledger.

\begin{proposition}[Broader-EFT same-symmetry neutral operator]
\label{prop:priii-local-neutral-counteroperator}
Let \(\Phi\) be the PR-II \(Y=1\) order doublet, let
\((M_{Z,0}^{\rm PR})^2:=g_Z^2(v_{\rm EW}^{\rm PR})^2/4\) denote the tree/reference neutral
mass, and define
\begin{equation}
\mathcal O_{HD}
:=
\left(\Phi^\dagger D_\mu\Phi\right)^*
\left(\Phi^\dagger D^\mu\Phi\right),
\qquad
\Delta\mathcal L_\lambda
:=
\frac{2\lambda\rho_{\rm PR}}
{(v_{\rm EW}^{\rm PR})^2}\,\mathcal O_{HD},
\quad \lambda\ge0.
\label{eq:priii-local-neutral-counteroperator}
\end{equation}
This operator is local, Lorentz invariant, and invariant under
\(SU(2)_L\times U(1)_Y\).  At the locked vacuum it produces
\begin{equation}
\Delta\mathcal L_\lambda\big|_{\Phi_0}
=
\frac12\lambda\rho_{\rm PR}(M_{Z,0}^{\rm PR})^2 Z_\mu Z^\mu,
\label{eq:priii-local-neutral-counteroperator-vev}
\end{equation}
while producing no \(W^\pm\) or photon mass term.  Thus
\(\delta M_Z^2/(M_{Z,0}^{\rm PR})^2=\lambda\rho_{\rm PR}\); under the relative
mass-squared normalization used by the displayed \(D_3\) numerical ledger, it realizes the entire
positive fixed-kernel family \(D_3(\lambda)=\lambda\rho_{\rm PR}P_Z\) without a diagnostic input.
\end{proposition}

\begin{proof}
Gauge covariance gives \(D_\mu\Phi\mapsto U D_\mu\Phi\), so
\(\Phi^\dagger D_\mu\Phi\) and its modulus square are gauge invariant.  For
\(\Phi_0=(0,v_{\rm EW}^{\rm PR})^T/\sqrt2\),
\begin{equation}
\Phi_0^\dagger D_\mu\Phi_0
=
\frac{i(v_{\rm EW}^{\rm PR})^2}{4}
\left(gW_\mu^3-g'B_\mu\right)
=
\frac{i(v_{\rm EW}^{\rm PR})^2g_Z}{4}Z_\mu .
\end{equation}
Therefore
\(\mathcal O_{HD}|_{\Phi_0}=(v_{\rm EW}^{\rm PR})^4g_Z^2Z_\mu Z^\mu/16\).
Using \((M_{Z,0}^{\rm PR})^2=g_Z^2(v_{\rm EW}^{\rm PR})^2/4\) gives
Eq.~\eqref{eq:priii-local-neutral-counteroperator-vev}.  The vacuum contraction contains neither
the charged directions nor the orthogonal photon direction.
\end{proof}

This \(\lambda\)-family is not an alternative PR branch, and \(\lambda\) is not
introduced into the PR ledger.  It belongs to a deliberately enlarged EFT
comparison class that permits an independent dimension-six Wilson
coefficient.  Away from the locked vacuum it also changes scalar/Goldstone
interactions.  It therefore proves only that gauge symmetry alone cannot
select \(k\).  The canonical PR finite-tier class excludes independent \(C_3\)
Wilson coefficients and requires the four target-independent normalized
response properties; these derive \(\mathsf H_Z\), and within that class
\(k=2\) is unique.  Any background-Hessian presentation admitted to this class
must satisfy the same response gates and therefore represents the same
equation.

\begin{tcolorbox}[colback=white!3,colframe=black!55!black,title={Exact status of the neutral \(C_3\) coefficient}]
\begin{itemize}[leftmargin=1.6em]
\item \textbf{Unconditional algebraic result:}
\(\operatorname{Tr}_{\rm ch}(q^\dagger q)=2\).
\item \textbf{Canonical uniqueness result:}
the unique normalized quadratic response functional gives one and only one
coefficient, \(k=2\), with no fitted parameter.
\item \textbf{Equation-exhaustion result:}
every proposed fixed-kernel equation either lies outside the declared
\(C_3\) response-functional class or has the positive defect
\(\rho_{\rm PR}^2(k-2)^2>0\); every member of the declared class is the same
trace residual law on the complete charge-operator domain, modulo allowed
operator equivalence.
\item \textbf{Scope result:}
broader families with independent second jets or Wilson coefficients are not
fixed by zero/first-jet data and gauge symmetry alone; they lie outside the
declared minimal PR response class and are not alternative PR branches.
\item \textbf{Microscopic-representation result:}
a gauge-fixed neutral background Hessian is an admissible presentation only
when its finite counterterms and same-order power counting reduce to the same
\(\mathsf H_Z\) identity; otherwise it defines a different class.
\end{itemize}
\end{tcolorbox}

Accordingly, the numerical \(C_3\) branch below evaluates the unique member of
the canonical minimal-response class.  It is not selected because it is a
better empirical fit.
Its fixed value is
\begin{equation}
D_{3,Z}^{\rm PR}
=
0.0000772464862565637081786207896848877\ldots .
\label{eq:priii-ew-D3-neutral-numerical}
\end{equation}
In the canonical minimal-response class, the \(C_3\) self-energies are
\begin{equation}
\Pi_W^{C_3}
=
\Pi_W^{C_2},
\qquad
\Pi_Z^{C_3}
=
\Pi_Z^{C_2}+D_{3,Z}^{\rm PR},
\end{equation}
with
\begin{equation}
\Pi_Z^{C_3}
=
-0.0035108469317154309784857330325970968\ldots .
\end{equation}
The corresponding canonical PR-III weak ledger is
\begin{align}
M_W^{\rm PR}
&=
M_W^{C_3}
=
80.3739428518621\ {\rm GeV},
\\
M_Z^{\rm PR}
&=
M_Z^{C_3}
=
91.1876764310439\ {\rm GeV},
\\
G_F^{\rm PR}
&=
1.166379220175995\times10^{-5}\ {\rm GeV}^{-2},
\\
\rho_{\rm EW}^{\rm PR}
&=
1.01072468650035 .
\end{align}
The charged branch is unchanged from \(C_2\); only the neutral channel receives the \(D_{3,Z}^{\rm PR}\) refinement.

\subsection{One-Sigma Diagnostics for the Canonical Closure Branch}
\label{subsec:priii-ew-final-precision}

For the selected post-generation diagnostic comparison,
\begin{align}
M_W^{\rm diag}
&=
80.3692\pm0.0133\ {\rm GeV},
\\
M_Z^{\rm diag}
&=
91.1876\pm0.0021\ {\rm GeV},
\\
G_F^{\rm diag}
&=
\left(1.1663788\pm0.0000007\right)
\times10^{-5}\ {\rm GeV}^{-2}.
\end{align}
The final residuals are
\begin{align}
M_W^{\rm PR}-M_W^{\rm diag}
&=
+0.0047428518621\ {\rm GeV},
\\
M_Z^{\rm PR}-M_Z^{\rm diag}
&=
+0.0000764310439\ {\rm GeV},
\\
G_F^{\rm PR}-G_F^{\rm diag}
&=
+4.201759949\times10^{-12}\ {\rm GeV}^{-2},
\end{align}
corresponding to
\begin{equation}
\boxed{
M_W:\,+0.3566\sigma,
\qquad
M_Z:\,+0.0364\sigma,
\qquad
G_F:\,+0.6003\sigma .
}
\label{eq:priii-ew-final-sigma}
\end{equation}

The progression from \(C_1\) to the canonical \(C_3\) closure is summarized in
Table~\ref{tab:priii-ew-closure-branches}.

\begin{table}[htbp]
\centering
\caption{Electroweak branches.  Diagnostic distances are computed only after each branch is generated.  The \(C_3\) row uses the target-independent canonical response law and no diagnostic value is used to select it.}
\label{tab:priii-ew-closure-branches}
\begin{tabular}{lccccc}
\toprule
\textbf{Branch}
& \(\boldsymbol{M_W}\) [GeV]
& \(\boldsymbol{M_Z}\) [GeV]
& \(\boldsymbol{M_W/\sigma}\)
& \(\boldsymbol{M_Z/\sigma}\)
& \(\boldsymbol{G_F/\sigma}\) \\
\midrule
\(C_1\)
& 80.08709656
& 91.34817215
& \(-21.2108\)
& \(+76.4629\)
& \(+0.6003\) \\
\(C_2\)
& 80.37394285
& 91.18414199
& \(+0.3566\)
& \(-1.6467\)
& \(+0.6003\) \\
\(C_3\)
& 80.37394285
& 91.18767643
& \(+0.3566\)
& \(+0.0364\)
& \(+0.6003\) \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Electroweak branch statement}
\label{subsec:priii-ew-closure-statement}

The low-energy fine-structure value is first generated by the electromagnetic calculation and then transported to the inherited weak scale.  The weak couplings and \(C_1\) masses follow from that transported value and the PR displacement scale.  The \(C_2\) formulas and the scale \(\rho_{\rm PR}\) contain no diagnostic weak mass.  For \(C_3\), the charged-adjoint trace fixes the exact group factor two, while the canonical response law \(\mathsf H_Z\) uniquely maps that factor to the physical \(Z\) kernel in the declared minimal class.

Under this target-independent canonical closure, PR-III obtains
\begin{equation}
\boxed{
\begin{split}
{} & M_W^{\rm PR}=80.3739428518621\ {\rm GeV},\\
& M_Z^{\rm PR}=91.1876764310439\ {\rm GeV},\\
& G_F^{\rm PR}=1.166379220175995\times10^{-5}\ {\rm GeV}^{-2},
\end{split}}
\end{equation}
with all three selected precision diagnostics inside one standard deviation. The diagnostics do not establish or select \(\mathsf H_Z\).  Its justification is instead the unique basis-invariant, additive, quadratically homogeneous, unit-normalized response theorem.  The displayed values are therefore a no-target-input finite-tier prediction within the declared canonical closure class.  A complete neutral Hessian presentation is equivalent only when it reduces to this same response law and therefore cannot change the no-fit uniqueness result.

\section{Radiative Stability of the Neutrino Branch}
\label{sec:priii-neutrino-stability}

The electromagnetic and electroweak branches determine the radiative environment in which the PR-II neutrino solution is tested for stability.  PR-III preserves the inherited, no-fit neutrino spectrum and evaluates whether the normal-ordering branch remains stable at the PR-III radiative scale, preserves its ordering and unitary flavor structure, and remains compatible with post-generation oscillation and direct-mass diagnostics. The inherited central branch is
\begin{equation}
\left(m_1^{(0)},m_2^{(0)},m_3^{(0)}\right)
=
\left(
0,\,
0.008627283010,\,
0.05010655367
\right)\ {\rm eV},
\label{eq:priii-neutrino-central-spectrum}
\end{equation}
with
\begin{equation}
\sum_i m_i^{(0)}
=
0.058733836680\ {\rm eV}.
\label{eq:priii-neutrino-central-sum}
\end{equation}
The inherited PMNS branch is specified by
\begin{align}
\sin^2\theta_{12}^{\rm PR}&=0.299447410807983,\\
\sin^2\theta_{23}^{\rm PR}&=0.565008899090616,\\
\sin^2\theta_{13}^{\rm PR}&=0.022270270124743,\\
\delta_{\rm CP}^{\rm PR}&=195.646778408^\circ .
\end{align}
The corresponding effective Majorana branch is
\begin{equation}
m_{\beta\beta}^{(0)}
=
1.507694477\ {\rm meV}.
\label{eq:priii-mbb-central}
\end{equation}
These quantities are fixed before comparison with oscillation fits, cosmological mass ceilings, direct beta-decay bounds, or neutrinoless-double-beta constraints.

\subsection{PR radiative kernel and protected massless branch}
\label{subsec:priii-neutrino-radiative-kernel}

The most general PR-III mass correction considered at this tier is written as
\begin{equation}
\Delta m_i^{\rm PR}
=
m_i^{(0)}R_{\nu i}^{\rm PR}
+
S_{\nu i}^{\rm PR},
\label{eq:priii-neutrino-general-correction}
\end{equation}
where the multiplicative term has the form
\begin{equation}
R_{\nu i}^{\rm PR}
=
\frac{1}{16\pi^2}
\left(
C_{W\nu}L_{W i}^{\rm PR}
+
C_{Z\nu}L_{Z i}^{\rm PR}
+
C_{M\nu}L_{M i}^{\rm PR}
\right).
\label{eq:priii-neutrino-multiplicative-kernel}
\end{equation}
The spectral factors \(L_{W i}^{\rm PR}\), \(L_{Z i}^{\rm PR}\), and \(L_{M i}^{\rm PR}\) are constrained by the already closed electromagnetic and electroweak ledgers and by the PR spectral gap.  The declared multiplicative class contains no additive term \(S_{\nu i}^{\rm PR}\); introducing one would add an independent Majorana-boundary structure and define a different equation class.

At the multiplicative order used here,
\begin{equation}
m_1^{(0)}=0
\quad\Longrightarrow\quad
\Delta m_1^{\rm PR}=0
\end{equation}
because no additive seed belongs to the declared domain.  The massless boundary branch is therefore protected at this order rather than lifted by hand.

\subsection{Electroweak stability scale}
\label{subsec:priii-neutrino-ew-stability-scale}

The dimensionless neutrino stability scale is inherited from the same weak-boundary deficit and three-sheet structure that enter the electromagnetic and electroweak refinements:
\begin{equation}
\epsilon_\nu^{\rm PR}
=
\frac{\Delta_{\rm EW}^{\rm HR}}
{\sqrt{N_{\rm gen}^{\rm PR}}},
\qquad
N_{\rm gen}^{\rm PR}=3.
\label{eq:priii-epsilon-nu}
\end{equation}
Using
\begin{equation}
\Delta_{\rm EW}^{\rm HR}
=
0.0186442803066928997189287764284030288\ldots,
\end{equation}
PR-III obtains
\begin{align}
\epsilon_\nu^{\rm PR}
&=
0.0107642802539159840599930614668459536\ldots,
\\
\left(\epsilon_\nu^{\rm PR}\right)^2
&=
0.0001158697293848455622679311845273316\ldots .
\end{align}

At the present tier this quantity defines a conservative multiplicative stability envelope rather than an asserted exact loop correction:
\begin{equation}
\left|\Delta m_i^{\rm PR}\right|
\leq
m_i^{(0)}
\left(\epsilon_\nu^{\rm PR}\right)^2,
\qquad
\left|\Delta m_{\beta\beta}^{\rm PR}\right|
\leq
m_{\beta\beta}^{(0)}
\left(\epsilon_\nu^{\rm PR}\right)^2.
\label{eq:priii-neutrino-envelope-rule}
\end{equation}
The resulting half-widths are
\begin{align}
\Delta m_1^{\rm env}&=0,\\
\Delta m_2^{\rm env}
&=
9.99640947695176\times10^{-7}\ {\rm eV},\\
\Delta m_3^{\rm env}
&=
5.80583281415014\times10^{-6}\ {\rm eV},\\
\Delta m_{\beta\beta}^{\rm env}
&=
1.74696151045016\times10^{-7}\ {\rm eV}\\
&=
1.74696151045016\times10^{-4}\ {\rm meV}.
\end{align}

\subsection{Mass ordering under the PR envelope}
\label{subsec:priii-neutrino-ordering-envelope}

The allowed intervals generated by Eq.~\eqref{eq:priii-neutrino-envelope-rule} are
\begin{align}
0.00862628336905230\ {\rm eV}
&\leq
m_2
\leq
0.00862828265094770\ {\rm eV},
\\
0.0501007478371858\ {\rm eV}
&\leq
m_3
\leq
0.0501123595028142\ {\rm eV}.
\end{align}
The summed mass remains in the interval
\begin{equation}
0.0587270312062382\ {\rm eV}
\leq
\sum_i m_i
\leq
0.0587406421537618\ {\rm eV}.
\label{eq:priii-neutrino-sum-envelope}
\end{equation}
Because the intervals do not overlap and \(m_1=0\) remains protected,
\begin{equation}
m_1<m_2<m_3
\end{equation}
throughout the PR stability envelope.

The central mass-squared splittings are
\begin{align}
\Delta m_{21}^{2,{\rm PR}}
&=
7.443001213463466\times10^{-5}\ {\rm eV}^2,
\\
\Delta m_{31}^{2,{\rm PR}}
&=
2.5106667206845905\times10^{-3}\ {\rm eV}^2,
\\
\Delta m_{32}^{2,{\rm PR}}
&=
2.4362367085499558\times10^{-3}\ {\rm eV}^2.
\end{align}
All three remain positive over the full envelope.  The normal-ordering branch is therefore stable under the PR-III multiplicative deformation.

\subsection{PMNS unitarity and admissible radiative deformation}
\label{subsec:priii-neutrino-pmns-stability}

The inherited angle branch corresponds to
\begin{align}
\theta_{12}^{\rm PR}&=33.1763566434167^\circ,\\
\theta_{23}^{\rm PR}&=48.7353104030270^\circ,\\
\theta_{13}^{\rm PR}&=8.58243805858008^\circ .
\end{align}
For the first row of the PMNS matrix,
\begin{align}
|U_{e1}|^2&=0.684951093794123,\\
|U_{e2}|^2&=0.292778636081134,\\
|U_{e3}|^2&=0.022270270124743,
\end{align}
and
\begin{equation}
|U_{e1}|^2+|U_{e2}|^2+|U_{e3}|^2=1.
\end{equation}

PR-III does not insert an empirical shift into the PMNS angles.  Every
admissible radiative deformation in the declared class preserves unitarity and is therefore restricted to
\begin{equation}
U_{\rm PMNS}^{\rm phys}
=
U_{\rm PMNS}^{(0)}
\exp\!\left(A_\nu^{\rm PR}\right),
\qquad
\left(A_\nu^{\rm PR}\right)^\dagger
=
-A_\nu^{\rm PR}.
\label{eq:priii-pmns-unitary-update}
\end{equation}
To first order,
\begin{equation}
\Delta U_{\rm PMNS}^{\rm PR}
=
U_{\rm PMNS}^{(0)}A_\nu^{\rm PR},
\end{equation}
so unitarity is maintained by construction.  The PR-III class fixes the frozen
unitary branch; a nonzero phase-sensitive \(A_\nu^{\rm PR}\) would add a
higher-order structure and is outside this class.

\subsection{Effective beta and Majorana masses}
\label{subsec:priii-neutrino-effective-masses}

The effective electron-neutrino mass is
\begin{equation}
m_\beta^2
=
\sum_i |U_{ei}|^2m_i^2.
\end{equation}
Using the generated PR spectrum and PMNS branch gives
\begin{equation}
m_\beta^{\rm PR}
=
0.00881502940999797\ {\rm eV}
=
8.81502940999797\ {\rm meV}.
\label{eq:priii-mbeta}
\end{equation}

The effective Majorana mass is
\begin{equation}
m_{\beta\beta}
=
\left|
\sum_i U_{ei}^2m_i
\right|,
\end{equation}
with central PR value from Eq.~\eqref{eq:priii-mbb-central}.  The radiative stability interval is
\begin{equation}
\boxed{
1.50751978084895\ {\rm meV}
\leq
m_{\beta\beta}
\leq
1.50786917315105\ {\rm meV}.
}
\label{eq:priii-mbb-envelope}
\end{equation}
Its half-width is only
\begin{equation}
\Delta m_{\beta\beta}^{\rm env}
=
0.000174696151045016\ {\rm meV},
\end{equation}
corresponding to a relative envelope of
\begin{equation}
115.869729384846\ {\rm ppm}.
\end{equation}
This is a stability statement, not a claim of experimental detection.

\subsection{Post-generation diagnostic comparison}
\label{subsec:priii-neutrino-diagnostics}

Only after the PR spectrum, ordering, PMNS branch, and stability envelope are fixed are external neutrino references introduced.  Using the selected representative normal-ordering comparison values,
\begin{align}
\Delta m_{21}^{2,{\rm diag}}
&=
7.49\times10^{-5}\ {\rm eV}^2,
\\
\Delta m_{31}^{2,{\rm diag}}
&=
2.513\times10^{-3}\ {\rm eV}^2,
\\
\sin^2\theta_{12}^{\rm diag}
&=
0.307,
\\
\sin^2\theta_{23}^{\rm diag}
&=
0.561,
\\
\sin^2\theta_{13}^{\rm diag}
&=
0.02215,
\end{align}
the relative PR residuals are
\begin{align}
\frac{\Delta m_{21}^{2,{\rm PR}}-\Delta m_{21}^{2,{\rm diag}}}
{\Delta m_{21}^{2,{\rm diag}}}
&=
-0.6275\%,
\\
\frac{\Delta m_{31}^{2,{\rm PR}}-\Delta m_{31}^{2,{\rm diag}}}
{\Delta m_{31}^{2,{\rm diag}}}
&=
-0.09285\%,
\\
\frac{\sin^2\theta_{12}^{\rm PR}-\sin^2\theta_{12}^{\rm diag}}
{\sin^2\theta_{12}^{\rm diag}}
&=
-2.4601\%,
\\
\frac{\sin^2\theta_{23}^{\rm PR}-\sin^2\theta_{23}^{\rm diag}}
{\sin^2\theta_{23}^{\rm diag}}
&=
+0.7146\%,
\\
\frac{\sin^2\theta_{13}^{\rm PR}-\sin^2\theta_{13}^{\rm diag}}
{\sin^2\theta_{13}^{\rm diag}}
&=
+0.5430\%.
\end{align}
The branch is therefore diagnostically compatible with the selected oscillation comparison without having used those quantities as generation inputs. For the selected direct and cosmological comparisons \cite{Planck2018Cosmology, KATRIN2022, KamLANDZen2023},
\begin{align}
\sum_i m_i^{\rm PR}
&=
0.058733836680\ {\rm eV}
<
0.12\ {\rm eV},
\\
m_\beta^{\rm PR}
&=
0.008815029410\ {\rm eV}
<
0.45\ {\rm eV},
\\
m_{\beta\beta}^{\rm PR}
&=
1.507694477\ {\rm meV}
<
70\ {\rm meV}.
\end{align}
The PR mass sum occupies \(48.9449\%\) of the selected \(0.12\ {\rm eV}\) ceiling, \(m_\beta\) occupies \(1.9589\%\) of the selected direct bound, and \(m_{\beta\beta}\) occupies \(2.1538\%\) of the selected direct-comparison scale \cite{PDG2024}.  These are post-generation compatibility statements and should be cited to the corresponding oscillation, cosmology, beta-decay, and neutrinoless-double-beta references in the final bibliography.

\begin{table}[htbp]
\centering
\caption{Generated PR-III neutrino observables and selected post-generation diagnostic status.}
\label{tab:priii-neutrino-summary}
\begin{tabular}{lll}
\toprule
\textbf{Quantity} & \textbf{PR-III value} & \textbf{Status} \\
\midrule
Ordering & \(m_1<m_2<m_3\) & Stable over PR envelope \\
\(\sum_i m_i\) & \(0.058733836680\ {\rm eV}\) & Below selected cosmology ceiling \\
\(m_\beta\) & \(8.815029410\ {\rm meV}\) & Below selected direct bound \\
\(m_{\beta\beta}\) & \(1.507694477\ {\rm meV}\) & Stable and below selected direct scale \\
\(\Delta m_{21}^2\) & \(7.4430012\times10^{-5}\ {\rm eV}^2\) & Diagnostic-compatible \\
\(\Delta m_{31}^2\) & \(2.5106667\times10^{-3}\ {\rm eV}^2\) & Diagnostic-compatible \\
PMNS first-row sum & \(1.000000000000000\) & Unitary \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Neutrino closure statement}
\label{subsec:priii-neutrino-closure-statement}

PR-III establishes that the inherited normal-ordering neutrino branch remains stable in the radiative environment generated by the closed electromagnetic and electroweak sectors.  The central spectrum is not retuned.  The massless branch remains protected at multiplicative order, the \(m_2\) and \(m_3\) intervals remain separated, all mass-squared splittings remain positive, the PMNS update rule is unitary, and the \(m_{\beta\beta}\) envelope is narrow.

The resulting finite-tier statement is
\begin{equation}
\boxed{
\begin{gathered}
(m_1,m_2,m_3)
=
(0,\ 0.008627283010,\ 0.05010655367)\ {\rm eV},
\\
\sum_i m_i
=
0.058733836680\ {\rm eV},
\qquad
m_\beta
=
8.815029410\ {\rm meV},
\\
m_{\beta\beta}
=
1.507694477\ {\rm meV},
\qquad
\text{normal ordering stable.}
\end{gathered}
}
\end{equation}

This is the exact neutrino theorem on the declared multiplicative finite-tier domain: the PR-II branch is radiatively stable and diagnostically compatible without importing neutrino target observables as fitted inputs. An additive Majorana seed, a new phase-sensitive deformation, or an all-orders series adds data not present in this domain and therefore defines a different equation class, not another solution of the PR-III neutrino equation.


\section{Strong-Sector Phase-Fiber and One-Loop Running Closure}
\label{sec:priii-strong-sector}

The final gauge-sector extension of PR-III is the compact color branch.  PR-II supplied a strong-coupling anchor and generated quark-sheet hierarchy; PR-III assembles the radiative sign, active-flavor structure, threshold ordering, and compatibility of the anchor with a weak-scale strong-coupling reference into one finite-tier ledger.  It performs that construction without importing an external value of \(\alpha_s\), external quark masses, or an external \(\Lambda_{\overline{\rm MS}}\) as generation inputs.

The inherited strong anchor is
\begin{equation}
\alpha_3^{\rm PR}
=
0.117861507469150,
\label{eq:priii-alpha3-anchor}
\end{equation}
or
\begin{equation}
\left(\alpha_3^{\rm PR}\right)^{-1}
=
8.4845342764833368725536701837814243566\ldots .
\end{equation}
This quantity is treated as a compact-boundary PR output.  The purpose of the present section is not to fit it, but to determine whether it belongs to a consistent \(SU(3)_c\) phase-fiber, threshold, and one-loop running structure.

\subsection{Compact Color-Fiber Ledger}
\label{subsec:priii-strong-color-fiber}
The theoretical derivation of the strong-sector dynamics relies on the algebraic classification of the inherited internal color projection, allowing the PR-III architecture to formally anchor the color branch within the topological invariants. We start by defining 

\begin{equation}
SU(3)_c,
\end{equation}
with generators \(T^a\) in the fundamental representation and the standard invariant normalization
\begin{equation}
{\rm Tr}\!\left(T^aT^b\right)
=
T_F\delta^{ab}.
\end{equation}
The PR color ledger fixes
\begin{equation}
N_c=3,
\qquad
{\rm dim}\,{\rm Adj}(SU(3))=8,
\end{equation}
and
\begin{equation}
C_A=3,
\qquad
C_F=\frac43,
\qquad
T_F=\frac12 .
\label{eq:priii-su3-invariants}
\end{equation}
These are group-theoretic identities, not fit parameters. Writing
\begin{equation}
\alpha_3^{\rm PR}
=
\frac{\left(g_3^{\rm PR}\right)^2}{4\pi},
\end{equation}
the PR running object has the form
\begin{equation}
\mu\frac{d\alpha_3^{\rm PR}}{d\mu}
=
\beta_3^{\rm PR}
\!\left(
\alpha_3^{\rm PR},
P_{\rm color},
K_3^{\rm PR}
\right),
\end{equation}
where \(P_{\rm color}\) denotes the compact color projection and \(K_3^{\rm PR}\) is the reference-normalized PR spectral kernel.

\subsection{Strong Spectral Kernel}
\label{subsec:priii-strong-spectral-kernel}
To evaluate the scale dependence and radiative transport of the strong coupling, the rigid algebraic identities established above must be dynamically coupled to the internal fluctuation spectrum. This evolution is governed by the native PR strong spectral kernel, which acts as a geometric filter mapping the topological supertrace of the color sector directly into a formal running equation. The one-loop organization is
\begin{equation}
\mu\frac{d\alpha_3^{\rm PR}}{d\mu}
=
-
\frac{\left(\alpha_3^{\rm PR}\right)^2}{2\pi}
\beta_0^{\rm PR}
K_3^{\rm PR}
+
\mathcal O\!\left((\alpha_3^{\rm PR})^3\right).
\label{eq:priii-strong-running-general}
\end{equation}
The spectral supertrace contains the adjoint gluon block, color ghosts, and the active quark color sheets.  Color-neutral leptons and electroweak residual backgrounds do not contribute directly to the pure \(SU(3)_c\) trace. For a color block \(a\), the admissible discrete kernel class is
\begin{equation}
K_{3a}^{\rm PR}(\mu_0\rightarrow\mu)
=
\sum_n\omega_{3a,n}^{\rm PR}
\log\!\left[
\frac{
M_a^2+\mu^2+\mu_n^2\left(\Lambda_3^{\rm PR}\right)^2
}{
M_a^2+\mu_0^2+\mu_n^2\left(\Lambda_3^{\rm PR}\right)^2
}
\right]
-
R_{3a}^{\rm run},
\label{eq:priii-strong-kernel}
\end{equation}
where
\begin{equation}
\mu_n^2
=
\lambda_n-\lambda_0
\geq
\left(\mu_{\min}^{\rm HR}\right)^2
=
3.053016666732689 .
\end{equation}
The subtraction \(R_{3a}^{\rm run}\) preserves the inherited strong anchor and cannot be selected to force agreement with an external \(\alpha_s\) reference.  The regulator is therefore tied to the positive PR spectral gap rather than to an arbitrary ultraviolet cutoff. At the present tier,
\begin{equation}
\Lambda_3^{\rm PR}
=
\Lambda_{\rm EW}^{\rm PR}\,\Xi_3^{\rm PR}
\end{equation}
is retained as a symbolic PR matching relation.  No numerical value of \(\Xi_3^{\rm PR}\) or \(\Lambda_3^{\rm PR}\) is inserted.  Consequently, PR-III fixes the group coefficient, threshold ledger, and running sign in its declared domain.  A fully integrated function \(\alpha_3^{\rm PR}(\mu)\) requires additional scale data and belongs to a different equation class.

\subsection{One-loop color coefficient}
\label{subsec:priii-strong-one-loop-coefficient}
To quantify the radiative transport of the strong coupling across the physical spectrum, the geometric kernel must be evaluated against the perturbative color $\beta$-function. The leading-order running behavior is determined by the dynamical balance between the gauge-boson self-interactions and the fermionic screening contributions. Extracted directly from the rigid topological invariants established in Eq.~\eqref{eq:priii-su3-invariants}, the one-loop color coefficient is formally defined as

\begin{equation}
\beta_0^{\rm PR}
=
\frac{11}{3}C_A
-
\frac{4}{3}T_F n_f^{\rm PR}.
\end{equation}
Using Eq.~\eqref{eq:priii-su3-invariants},
\begin{equation}
\boxed{
\beta_0^{\rm PR}
=
11-\frac23 n_f^{\rm PR}.
}
\label{eq:priii-beta0-reduced}
\end{equation}
The critical flavor number is
\begin{equation}
n_f^{\rm crit}
=
\frac{33}{2}
=
16.5.
\end{equation}
Hence
\begin{equation}
\beta_0^{\rm PR}>0
\qquad
\text{for}
\qquad
0\leq n_f^{\rm PR}\leq 6.
\end{equation}
For a positively oriented kernel \(K_3^{\rm PR}>0\), Eq.~\eqref{eq:priii-strong-running-general} therefore maintains a strictly negative sign throughout the full three-generation threshold sequence. This is the exact PR realization of the one-loop asymptotic-freedom condition \cite{Grosswilczek1973, Politzer1973}. 

The negative one-loop sign proves asymptotic freedom for the declared active-flavor ledger: the coupling decreases toward the ultraviolet, while the one-loop expression grows toward the infrared.  This perturbative sign is consistent with the conditions needed for dimensional transmutation, but it does not by itself prove confinement, a mass gap, or the infrared completion.  If \(n_f^{\rm PR}\geq17\), the one-loop sign would reverse and this asymptotic-freedom property would be lost.  The three-generation ledger has \(n_f^{\rm PR}=6<16.5\), so it remains on the asymptotically free side of the exact one-loop threshold.  The coefficient values are summarized in Table~\ref{tab:priii-strong-beta0}.

\begin{table}[htbp]
\centering
\caption{One-loop color coefficient over the PR active-flavor sequence.}
\label{tab:priii-strong-beta0}
\begin{tabular}{cccccccc}
\toprule
\(n_f^{\rm PR}\) & 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
\midrule
\(\beta_0^{\rm PR}\)
& \(11\)
& \(31/3\)
& \(29/3\)
& \(9\)
& \(25/3\)
& \(23/3\)
& \(7\) \\
\bottomrule
\end{tabular}
\end{table}

At the full three-generation count,
\begin{equation}
\left.
\mu\frac{d\alpha_3^{\rm PR}}{d\mu}
\right|_{n_f=6}
=
-
\frac{7}{2\pi}
\left(\alpha_3^{\rm PR}\right)^2
K_3^{\rm PR}
+\cdots .
\end{equation}
Evaluated at the inherited anchor, the leading prefactor is
\begin{equation}
-
\frac{7}{2\pi}
\left(\alpha_3^{\rm PR}\right)^2
=
-0.0154761223561545\ldots ,
\end{equation}
before multiplication by \(K_3^{\rm PR}\).

\subsection{PR quark thresholds and active flavors}
\label{subsec:priii-strong-thresholds}
The dynamical evolution of the strong coupling is intrinsically mediated by the exact sequence of fermion mass thresholds, which sequentially decouple from the radiative transport as the energy scale descends. These decoupling boundaries are not treated as empirical inputs or phenomenological phase transitions. Rather, they are strictly governed by the discrete, geometrically generated quark sheets derived in PR-II. Consequently, the complete active-flavor structure is constructed entirely by the following generated mass spectrum:

\begin{align}
m_u^{\rm PR}&=0.002146462595\ {\rm GeV},\\
m_d^{\rm PR}&=0.004761039493\ {\rm GeV},\\
m_s^{\rm PR}&=0.094028510538\ {\rm GeV},\\
m_c^{\rm PR}&=1.274964814257465\ {\rm GeV},\\
m_b^{\rm PR}&=4.1664504826753515\ {\rm GeV},\\
m_t^{\rm PR}&=172.8139732666624\ {\rm GeV},
\end{align}
which obey
\begin{equation}
m_u^{\rm PR}
<
m_d^{\rm PR}
<
m_s^{\rm PR}
<
m_c^{\rm PR}
<
m_b^{\rm PR}
<
m_t^{\rm PR}.
\end{equation}
These values are not imported from an external quark-mass table. At the present tier the active-flavor count is represented by the sharp-threshold rule
\begin{equation}
n_f^{\rm PR}(\mu)
=
\sum_{q=u,d,s,c,b,t}
\Theta\!\left(\mu-m_q^{\rm PR}\right).
\label{eq:priii-active-flavor-count}
\end{equation}
The corresponding intervals are shown in Table~\ref{tab:priii-strong-thresholds}.

\begin{table}[htbp]
\centering
\caption{PR active-flavor intervals and one-loop coefficients.}
\label{tab:priii-strong-thresholds}
\begin{tabular}{lcc}
\toprule
\textbf{Scale interval} & \(\boldsymbol{n_f^{\rm PR}}\) & \(\boldsymbol{\beta_0^{\rm PR}}\) \\
\midrule
\(0<\mu<m_u^{\rm PR}\) & 0 & \(11\) \\
\(m_u^{\rm PR}\leq\mu<m_d^{\rm PR}\) & 1 & \(31/3\) \\
\(m_d^{\rm PR}\leq\mu<m_s^{\rm PR}\) & 2 & \(29/3\) \\
\(m_s^{\rm PR}\leq\mu<m_c^{\rm PR}\) & 3 & \(9\) \\
\(m_c^{\rm PR}\leq\mu<m_b^{\rm PR}\) & 4 & \(25/3\) \\
\(m_b^{\rm PR}\leq\mu<m_t^{\rm PR}\) & 5 & \(23/3\) \\
\(\mu\geq m_t^{\rm PR}\) & 6 & \(7\) \\
\bottomrule
\end{tabular}
\end{table}

The electroweak matching scale lies above the generated top threshold:
\begin{equation}
\Lambda_{\rm EW}^{\rm PR}
-
m_t^{\rm PR}
=
0.85662507806592\ {\rm GeV}>0.
\end{equation}
Therefore
\begin{equation}
n_f^{\rm PR}\!\left(\Lambda_{\rm EW}^{\rm PR}\right)=6,
\qquad
\beta_0^{\rm PR}\!\left(\Lambda_{\rm EW}^{\rm PR}\right)=7.
\label{eq:priii-strong-nf-ew}
\end{equation}
Equation~\eqref{eq:priii-active-flavor-count} is the sharp-threshold rule of the declared one-loop class and fixes its active-flavor ordering and sign.  Smooth profiles or higher-loop coefficients alter the admissibility domain and are not alternative solutions of this equation.

\subsection{Post-generation strong-anchor comparison}
\label{subsec:priii-strong-diagnostic-comparison}

After the PR anchor, group ledger, and threshold structure have been fixed, the result may be compared with a selected weak-scale strong-coupling reference,
\begin{equation}
\alpha_s^{\rm diag}
=
0.1179.
\end{equation}
The residual is
\begin{equation}
\alpha_3^{\rm PR}-\alpha_s^{\rm diag}
=
-0.000038492530850,
\end{equation}
or
\begin{equation}
\frac{
\alpha_3^{\rm PR}-\alpha_s^{\rm diag}
}{
\alpha_s^{\rm diag}
}
=
-3.26484570398643\times10^{-4}.
\end{equation}
Equivalently,
\begin{equation}
\boxed{
\frac{
\alpha_3^{\rm PR}-\alpha_s^{\rm diag}
}{
\alpha_s^{\rm diag}
}
=
-0.0326484570399\%.
}
\label{eq:priii-strong-relative-residual}
\end{equation}
The generated anchor is therefore \(326.485\) ppm below the selected reference and has ratio
\begin{equation}
\frac{\alpha_3^{\rm PR}}{\alpha_s^{\rm diag}}
=
0.999673515429601\ldots .
\end{equation}
The diagnostic reference is introduced only at this stage and does not modify Eq.~\eqref{eq:priii-alpha3-anchor} or the threshold ledger \cite{PDG2024}.

Collectively, these evaluations close the stated one-loop strong-anchor
calculation.  Given the declared compact color projection, active-flavor
ledger, sharp-threshold convention, and positive kernel orientation, the
calculation fixes \(\beta_0^{\rm PR}=7\) at \(\Lambda_{\rm EW}^{\rm PR}\) and generates \(\alpha_3^{\rm PR}=0.1178615\dots\) without importing the diagnostic value as a fit.  The result agrees with that diagnostic to sub-\(0.04\%\). Different spectral subtractions, an independently supplied \(\Lambda_3^{\rm PR}\), smooth thresholds, higher loops, confinement, or mass-gap postulates are outside the declared one-loop strong class and do not constitute additional solutions within it.

\section{Global Anomaly, Running-Continuity, and No-Fit Consistency}
\label{sec:priii-global-consistency}

The electromagnetic, electroweak, neutrino, and strong branches have so far been constructed separately from a common inherited projection ledger.  The final physical question is whether those branches coexist as one consistent theory.  PR-III therefore imposes three global conditions.  First, the electroweak and color representation ledger must be free of local and global gauge anomalies.  Second, the quantities transferred between sectors must remain continuous under the declared projection maps and matching scales.  Third, the numerical agreements reported in the preceding sections must preserve the no-fit separation between generated quantities and diagnostic references. No new correction is introduced in this section, as this would be against the rules of the framework set in PR-I.  The analysis is an intersection of the already generated sector branches,
\begin{equation}
\mathcal L_{\rm PRIII}
=
\mathcal L_{\rm em}
\cap
\mathcal L_{\rm EW}
\cap
\mathcal L_{\nu}
\cap
\mathcal L_{3}
\cap
\ker\mathcal A
\cap
\mathcal P_{\rm no\mbox{-}fit},
\label{eq:priii-global-intersection}
\end{equation}
where \(\ker\mathcal A\) denotes the anomaly-free representation subspace and \(\mathcal P_{\rm no\mbox{-}fit}\) denotes the provenance condition that diagnostic observables do not enter the generation maps.

\subsection{One-generation Chiral Representation Ledger}
\label{subsec:priii-one-generation-representation-ledger}

All anomaly sums are evaluated using left-handed Weyl fields and the PR-II hypercharge convention \cite{PDG2024}
\begin{equation}
Q=T_3+\frac{Y}{2}.
\label{eq:priii-global-charge-convention}
\end{equation}
For one generation the representation content is shown in Table~\ref{tab:priii-left-weyl-ledger}.

\begin{table}[htbp]
\centering
\caption{One-generation left-handed Weyl representation ledger.  Charge-conjugated right-handed fields are written as left-handed conjugate fields.}
\label{tab:priii-left-weyl-ledger}
\begin{tabular}{lccc}
\toprule
\textbf{Field} & \(\boldsymbol{SU(3)_c\times SU(2)_L}\) & \(\boldsymbol{Y}\) & \textbf{Multiplicity} \\
\midrule
\(Q_L\)        & \((\mathbf 3,\mathbf 2)\)                  & \(1/3\)  & 6 \\
\(u_R^c\)      & \((\overline{\mathbf 3},\mathbf 1)\)       & \(-4/3\) & 3 \\
\(d_R^c\)      & \((\overline{\mathbf 3},\mathbf 1)\)       & \(2/3\)  & 3 \\
\(L_L\)        & \((\mathbf 1,\mathbf 2)\)                  & \(-1\)   & 2 \\
\(e_R^c\)      & \((\mathbf 1,\mathbf 1)\)                  & \(2\)    & 1 \\
\(\nu_R^c\)    & \((\mathbf 1,\mathbf 1)\)                  & \(0\)    & 1, optional \\
\bottomrule
\end{tabular}
\end{table}

The optional neutral singlet has \(Y=0\) and therefore contributes to none of the anomaly sums below.

\subsection{Local Anomaly Cancellation}
\label{subsec:priii-local-anomaly-cancellation}

The color cubic anomaly cancels because the two fundamental color components of \(Q_L\) are balanced by the two conjugate singlet branches:
\begin{equation}
\mathcal A\!\left[SU(3)_c^3\right]
=
2A(\mathbf 3)
+
A(\overline{\mathbf 3})
+
A(\overline{\mathbf 3})
=
0,
\end{equation}
where \(A(\overline{\mathbf 3})=-A(\mathbf 3)\).

The mixed color--hypercharge anomaly is
\begin{align}
\mathcal A\!\left[SU(3)_c^2U(1)_Y\right]
&=
2T_F\left(\frac13\right)
+
T_F\left(-\frac43\right)
+
T_F\left(\frac23\right)
\nonumber\\
&=
2\left(\frac12\right)\left(\frac13\right)
+
\left(\frac12\right)\left(-\frac43\right)
+
\left(\frac12\right)\left(\frac23\right)
\nonumber\\
&=0.
\end{align}

The mixed weak--hypercharge anomaly is
\begin{align}
\mathcal A\!\left[SU(2)_L^2U(1)_Y\right]
&=
3T_2\left(\frac13\right)
+
T_2(-1)
\nonumber\\
&=
3\left(\frac12\right)\left(\frac13\right)
+
\left(\frac12\right)(-1)
\nonumber\\
&=0.
\end{align}

The cubic hypercharge anomaly is
\begin{align}
\mathcal A\!\left[U(1)_Y^3\right]
={}&
6\left(\frac13\right)^3
+
3\left(-\frac43\right)^3
+
3\left(\frac23\right)^3
+
2(-1)^3
+
2^3
\nonumber\\
={}&0.
\end{align}
Likewise, the mixed gravitational--hypercharge anomaly vanishes:
\begin{align}
\mathcal A\!\left[{\rm grav}^2U(1)_Y\right]
={}&
6\left(\frac13\right)
+
3\left(-\frac43\right)
+
3\left(\frac23\right)
+
2(-1)
+
2
\nonumber\\
={}&0.
\end{align}

Therefore, all local gauge and mixed gravitational anomalies cancel within each generation.  Since the PR generation count is
\begin{equation}
N_{\rm gen}^{\rm PR}=3,
\end{equation}
generation replication multiplies zero anomaly residues by three and does not require additional compensating matter.  These cancellations follow from the inherited representation and hypercharge ledger; no external anomaly-canceling fields are inserted \cite{Adler1969, BellJackiw1969, Bardeen1969}.

\subsection{Global \texorpdfstring{$SU(2)$}{SU(2)} and Residual Electromagnetic Consistency}
\label{subsec:priii-witten-vectorlike-consistency}

The global \(SU(2)\) obstruction depends on the parity of the number of left-handed weak doublets.  One PR generation contains three color copies of \(Q_L\) and one lepton doublet:
\begin{equation}
N_D^{(1)}
=
3+1
=
4.
\end{equation}
For three generations,
\begin{equation}
N_D^{\rm PR}
=
N_{\rm gen}^{\rm PR}N_D^{(1)}
=
3\times4
=
12,
\end{equation}
which is even.  The Witten \(SU(2)\) anomaly is therefore absent, on a per-generation basis and globally \cite{Witten1982}.

After projection locking,
\begin{equation}
SU(2)_L\times U(1)_Y
\longrightarrow
U(1)_{\rm em},
\end{equation}
the charged matter branches occur in vectorlike left--right pairs:
\begin{equation}
u_L/u_R,\qquad
d_L/d_R,\qquad
e_L/e_R,
\end{equation}
with equal electric charges for the two chiralities, while the neutrino branch is electrically neutral.  The residual electromagnetic projection is therefore vectorlike.  This result is consistent with the exactly massless photon direction retained by the gauge-null quotient and with the charged-mode inventory used in the alpha calculation.

\subsection{Cross-sector Running Continuity}
\label{subsec:priii-running-continuity}

For clarification, we note that the term ``continuity'' means consistency of the quantities passed from one completed PR sector to the next on the registered finite-tier interfaces.  A complete all-scale renormalization-group flow has a different domain and is not an additional solution of this interface theorem.  The low-energy electromagnetic result supplies the boundary condition
\begin{equation}
\left(\alpha_{\rm PR}(0)\right)^{-1}
=
137.0359992075134149588913461016165946357\ldots .
\end{equation}
The electroweak transport gives
\begin{equation}
\left(\alpha_{\rm PR}^{C_1}
(\Lambda_{\rm EW}^{\rm PR})\right)^{-1}
=
\left(\alpha_{\rm PR}(0)\right)^{-1}
-
\Delta_{\rm run}^{C_1},
\end{equation}
with
\begin{equation}
\Delta_{\rm run}^{C_1}
=
8.687829492660492292065934163247,
\end{equation}
and therefore
\begin{equation}
\left(\alpha_{\rm PR}^{C_1}
(\Lambda_{\rm EW}^{\rm PR})\right)^{-1}
=
128.3481697148529226668254119383695946357\ldots .
\end{equation}
The inverse coupling decreases in the expected screening direction. The transported coupling then generates the \(C_3\) weak ledger.  The self-energy factors satisfy
\begin{equation}
1+\Pi_W^{C_3}>0,
\qquad
1+\Pi_Z^{C_3}>0,
\end{equation}
with
\begin{equation}
\Pi_W^{C_3}
=
0.0071761868359439894\ldots,
\qquad
\Pi_Z^{C_3}
=
-0.0035108469317154310\ldots .
\end{equation}
We find the final \(W\) and \(Z\) masses remain real and positive. The same dimensionless bridge appears in the weak-vector and neutrino stability sectors:
\begin{equation}
\epsilon_\nu^{\rm PR}
=
\epsilon_V^{\rm PR}
=
\frac{\Delta_{\rm EW}^{\rm HR}}
{\sqrt{N_{\rm gen}^{\rm PR}}}
=
0.0107642802539159841\ldots .
\label{eq:priii-shared-ew-neutrino-bridge}
\end{equation}
Therefore, the neutrino envelope is not normalized by a new fitted parameter; it inherits the same compact-boundary suppression scale that generated the electroweak vector split. The electroweak matching scale is also continuous with the strong threshold ledger:
\begin{equation}
\Lambda_{\rm EW}^{\rm PR}
=
173.67059834472832\ {\rm GeV}
>
m_t^{\rm PR}
=
172.8139732666624\ {\rm GeV}.
\end{equation}
So that
\begin{equation}
n_f^{\rm PR}\!
\left(\Lambda_{\rm EW}^{\rm PR}\right)
=
6,
\qquad
\beta_0^{\rm PR}\!
\left(\Lambda_{\rm EW}^{\rm PR}\right)
=
7.
\end{equation}
The electroweak scale therefore enters the six-flavor strong branch without an inconsistent threshold assignment. The resulting continuity chain may be summarized as
\begin{equation}
\alpha_{\rm PR}(0)
\longrightarrow
\alpha_{\rm PR}(\Lambda_{\rm EW}^{\rm PR})
\longrightarrow
\{M_W,M_Z,G_F\}_{\rm PR}
\longrightarrow
\epsilon_{\nu}^{\rm PR},
\end{equation}
together with
\begin{equation}
\Lambda_{\rm EW}^{\rm PR}
\longrightarrow
\{n_f^{\rm PR},\beta_0^{\rm PR}\}_{\rm strong}.
\end{equation}
Each arrow carries an already generated PR quantity; no new diagnostic reference is introduced at a sector boundary.

\subsection{No-fit Provenance Across Sectors}
\label{subsec:priii-global-no-fit-provenance}

For each sector \(s\), let \(\mathcal I_s^{\rm PR}\) denote the inherited or previously generated PR inputs and let \(\mathcal E_s\) denote the external quantities used for later comparison.  The global no-fit condition is
\begin{equation}
\mathcal E_s
\cap
{\rm Dom}(\mathcal C_s)
=
\varnothing
\qquad
\text{for every completed sector }s.
\label{eq:priii-global-no-fit-condition}
\end{equation}
The concrete separation is summarized in Table~\ref{tab:priii-global-provenance}.

\begin{table}[htbp]
\centering
\caption{Global no-fit separation.  The middle column lists the principal PR generation data; the final column lists quantities reserved for post-generation comparison.}
\label{tab:priii-global-provenance}
\small
\begin{tabular}{p{0.14\textwidth}p{0.39\textwidth}p{0.37\textwidth}}
\toprule
\textbf{Sector} & \textbf{PR generation data} & \textbf{Excluded diagnostic inputs} \\
\midrule
Electromagnetic
&
High-resolution spectral ledger, \(p_1^{\rm HR}\), \(q_{\rm bc}^{\rm HR}\), \(c_{\rm bc}\), \(\Delta_{\rm EW}^{\rm HR}\), \(N_{\rm gen}^{\rm PR}\), \(\sin^2\theta_W^{\rm PR}\), \(D_1\), \(D_2\)
&
Empirical or recommended \(\alpha\), manually fitted alpha residuals, weak or strong target values
\\[0.5em]

Electroweak
&
Generated \(\alpha_{\rm PR}(0)\), compact-boundary data, \(v_{\rm EW}^{\rm PR}\), \(\Lambda_{\rm EW}^{\rm PR}\), \(C_1\), \(C_2\), and \(C_3\)
&
Measured \(M_W\), \(M_Z\), \(G_F\), measured weak angle, fitted \(\kappa_W,\kappa_Z\), external oblique parameters
\\[0.5em]

Neutrino
&
Frozen PR-II spectrum and PMNS branch, PR electroweak stability scale, multiplicative envelope
&
Measured splittings and PMNS angles, cosmological mass ceilings, beta-decay and \(0\nu\beta\beta\) limits
\\[0.5em]

Strong
&
Frozen \(\alpha_3^{\rm PR}\), \(SU(3)_c\) identities, PR quark thresholds, generation count, PR spectral gap
&
External \(\alpha_s\) as a fit input, external quark masses, \(\Lambda_{\overline{\rm MS}}\), hadron or lattice targets
\\[0.5em]

Global structure
&
Inherited representation ledger, \(Q=T_3+Y/2\), locked sector outputs
&
External anomaly-canceling fields, empirical charge adjustments, observed CKM or PMNS entries
\\
\bottomrule
\end{tabular}
\end{table}

Equation~\eqref{eq:priii-global-no-fit-condition} is satisfied by every completed sector.  Diagnostic comparisons do not alter generated values, and no external fields are added to repair anomaly sums.

\subsection{Cross-sector Precision and Compatibility}
\label{subsec:priii-cross-sector-summary}

The principal generated observables and structural conditions are collected in Table~\ref{tab:priii-global-results}.  Precision quantities are reported in standard deviations where a selected uncertainty is available; compatibility quantities are reported as relative residuals or bound comparisons.

\begin{table}[htbp]
\centering
\caption{PR-III cross-sector closure summary.}
\label{tab:priii-global-results}
\small
\begin{tabular}{lll}
\toprule
\textbf{Quantity or condition} & \textbf{PR-III result} & \textbf{Status} \\
\midrule
\(\alpha^{-1}\)
& \(137.0359992075134\ldots\)
& \(+0.1376\sigma\) \\
\(M_W\)
& \(80.3739428518621\ {\rm GeV}\)
& \(+0.3566\sigma\) \\
\(M_Z\)
& \(91.1876764310439\ {\rm GeV}\)
& \(+0.0364\sigma\) \\
\(G_F\)
& \(1.166379220175995\times10^{-5}\ {\rm GeV}^{-2}\)
& \(+0.6003\sigma\) \\
\(\Delta m_{21}^2\)
& \(7.4430012\times10^{-5}\ {\rm eV}^2\)
& \(-0.6275\%\) relative \\
\(\Delta m_{31}^2\)
& \(2.5106667\times10^{-3}\ {\rm eV}^2\)
& \(-0.09285\%\) relative \\
\(\sum_i m_i\)
& \(0.058733836680\ {\rm eV}\)
& Below selected \(0.12\ {\rm eV}\) ceiling \\
\(m_\beta\)
& \(8.815029410\ {\rm meV}\)
& Below selected direct bound \\
\(m_{\beta\beta}\)
& \(1.507694477\ {\rm meV}\)
& Stable and below selected direct scale \\
\(\alpha_3\)
& \(0.117861507469150\)
& \(-0.0326485\%\) relative \\
Local anomalies
& All five sums vanish per generation
& Pass \\
Witten anomaly
& \(12\) weak doublets
& Absent \\
Residual \(U(1)_{\rm em}\)
& Charged branches vectorlike
& Pass \\
Running continuity
& All declared sector interfaces are consistent
& Pass \\
No-fit provenance
& Diagnostic inputs excluded from generation maps
& Pass \\
\bottomrule
\end{tabular}
\end{table}

The first four precision observables lie inside their selected one-sigma diagnostic bands.  The neutrino and strong branches satisfy the stated compatibility conditions.  The anomaly, continuity, and provenance conditions pass simultaneously.

\subsection{Global PR-III Consistency Statement}
\label{subsec:priii-global-consistency-statement}

The global intersection in Eq.~\eqref{eq:priii-global-intersection} is nonempty and contains the canonical PR-III branch, with its neutral \(C_3\) component fixed by the canonical response law \(\mathsf H_Z\).  Its diagnostic and structural status can be summarized as
\begin{equation}
\boxed{
\begin{gathered}
\alpha^{-1},\,M_W,\,M_Z,\,G_F
\quad\text{inside selected one-sigma diagnostics},\\
\text{the \(C_3\) neutral value unique in the minimal response class},\\
\text{neutrino and strong branches diagnostically compatible},\\
\mathcal A_{\rm local}=0,\qquad
\mathcal A_{\rm Witten}=0,\qquad
U(1)_{\rm em}\ \text{vectorlike},\\
\text{cross-sector continuity and no-fit provenance preserved}.
\end{gathered}
}
\label{eq:priii-global-consistency-result}
\end{equation}

This establishes simultaneous diagnostic and structural consistency of the stated branch.  The \(C_3\) value is selected by the target-independent closure theorem, not by this diagnostic intersection.

The domain of this result is the registered finite-tier PR-III architecture, not the class of arbitrary all-orders Standard-Model, QCD, or EFT constructions.  Complete neutral operators that reduce to \(\mathsf H_Z\) are
equivalent presentations.  All-orders electromagnetic series, independent Majorana seeds, new phase-sensitive deformations, smooth strong thresholds, higher-loop color running, and nonperturbative modules add structures excluded from the declared domain; they are not unresolved PR-III solutions.

The precise claim established here is finite-tier and class-relative: the stated PR-III branches coexist in one anomaly-free, continuity-preserving, no-target-input ledger whose current precision and compatibility diagnostics are mutually consistent, with the canonical theorem status of the neutral branch explicit.

\section{Closed Admissibility Domain and Equation-Architecture Uniqueness}
\label{sec:priii-closed-admissibility-domain}

PR-III closes a precisely declared radiative and cross-sector equation class inherited from PR-I and PR-II.  The electromagnetic, electroweak, neutrino, strong, anomaly, continuity, and provenance relations are not a menu of fitted alternatives: they form one registered construction whose inputs, operations, normalizations, orders, and equivalence rules are fixed before diagnostic comparison.  The central result is
\begin{equation}
\boxed{
\text{the completed admissible PR-I--PR-III equation quotient is a singleton}.
}
\label{eq:priii-closed-equation-claim}
\end{equation}
Here ``singleton'' is class-relative.  It means that no second inequivalent equation satisfies the same frozen postulates and admissibility rules.  It does not assert uniqueness among theories with different postulates, additional fields, higher orders, or independent EFT coefficients, and it is not a claim that an equation with several mathematical roots has only one physical state. Those are different domains, not alternative solutions inside this theorem.

\subsection{Frozen Inheritance and Registered Generation Map}
\label{subsec:priii-closed-inherited-data}

The PR-III generation map is the composition
\begin{equation}
\mathcal G_{\rm PRIII}
=
\mathcal F_{\rm III}
\!\left(
\mathcal I_{\rm PR-I},
\mathcal I_{\rm PR-II}
\right),
\label{eq:priii-conditional-on-pr1-pr2}
\end{equation}
where \(\mathcal I_{\rm PR-I}\) contains the radial spectral and compact-phase boundary data and \(\mathcal I_{\rm PR-II}\) contains the electroweak, generation, flavor, neutrino, quark-threshold, and strong-anchor branches.  The
following inherited quantities are frozen coordinates of this domain:
\begin{equation}
q_{\rm bc}^{\rm HR},
\quad
c_{\rm bc},
\quad
p_1^{\rm HR},
\quad
\sin^2\theta_W^{\rm PR},
\quad
v_{\rm EW}^{\rm PR},
\quad
\Lambda_{\rm EW}^{\rm PR},
\quad
N_{\rm gen}^{\rm PR},
\end{equation}
together with the PR-II neutrino branch, quark-sheet thresholds, and strong anchor.  Holding these inherited data fixed is the composition rule of the PR-I--PR-III theorem chain.  Every PR-III quantity is generated from that chain
without using the corresponding diagnostic target, so the inherited map adds no fitted coefficient and no unregistered freedom.

\subsection{Admissibility Gates and Equation Equivalence}
\label{subsec:priii-closed-admissibility-gates}

For each sector \(s\), let \(\mathcal A_s^{\rm PRIII}\) be the set of equations
that satisfy all of the following gates:
\begin{enumerate}
  \item they use only the frozen PR-I/PR-II objects and earlier registered
  PR-III outputs;
  \item they preserve the declared finite tier, spectral kernel, threshold
  convention, field content, and normalization;
  \item they introduce no fitted continuous coefficient and no diagnostic
  observable into the generation map;
  \item they preserve the applicable gauge-null, positivity, unitarity,
  anomaly, and cross-sector continuity identities; and
  \item they satisfy the sector-specific minimality rule, including the
  normalized additive quadratic response law for \(C_3\).
\end{enumerate}
The finite-tier qualification is therefore an intrinsic defining condition of \(\mathcal A_s^{\rm PRIII}\).  Adding a radiative order, field, independent second jet, Wilson coefficient, threshold profile, or new postulate changes the domain and produces an out-of-class theory.

Two admissible equations are equivalent, \(E\sim_{\rm PR}E'\), precisely when normalized basis or field changes and an everywhere-invertible residual map relate them on the complete registered domain while preserving the quotient solution set and all ledger observables.  Algebraically different notation is therefore not a second equation.

\begin{theorem}[Closed PR-I--PR-III equation architecture]
\label{thm:priii-closed-equation-architecture}
Let \(\mathfrak E_{\rm PRIII}\) be the product of the completed sector classes \(\mathcal A_s^{\rm PRIII}\), subject to the common anomaly, continuity, and no-fit gates above.  With the PR-I/PR-II inheritance fixed and the canonical closure rules used in this manuscript and proved selector-by-selector in
PR-IV,
\begin{equation}
\mathfrak E_{\rm PRIII}/\!\sim_{\rm PR}
=
\{[E_{\rm PRIII}]_{\rm PR}\}.
\label{eq:priii-architecture-singleton}
\end{equation}
Hence no inequivalent in-class equation and no free continuous parameter
remain.
\end{theorem}

\begin{proof}
The PR-IV axiom-by-axiom ledger reduces every completed selector to its registered normal form.  A proposed change either violates at least one gate, has a strictly nonzero registered defect, or is connected to the canonical residual by an allowed invertible presentation.  For the neutral selector this reduction is explicit in
Theorem~\ref{thm:priii-conditional-k-two}:
\(\|D_3(k)-2\rho_{\rm PR}P_Z\|_F^2
=\rho_{\rm PR}^2(k-2)^2\), which vanishes exactly at \(k=2\).
The same ledger-preserving equivalence rule identifies alternate notation and normalized bases.  Intersecting the singleton selector quotients with the already proved anomaly, continuity, positivity, unitarity, and no-fit gates leaves exactly the class in Eq.~\eqref{eq:priii-architecture-singleton}.
\end{proof}

\subsection{Diagnostic Separation and Zero-parameter Provenance}
\label{subsec:priii-closed-diagnostic-separation}

For every completed sector,
\begin{equation}
\mathcal E_s\cap{\rm Dom}(\mathcal C_s)=\varnothing .
\end{equation}
Thus empirical references do not select an equation, coefficient, branch, or root.  The reported standard-deviation distances and compatibility bounds are evaluations of the already generated output.  Their numerical values may track the diagnostic reference convention, but the PR equations and outputs remain fixed.  Equation uniqueness follows from the admissibility and equivalence proof above, independently of numerical proximity to a reference value.

\subsection{Closed Claim}
\label{subsec:priii-closed-claim}

The PR-I--PR-III chain fixes one class-relative equation architecture.  The PR-II charged algebra gives \(\operatorname{Tr}_{\rm ch}(q^\dagger q)=2\); the unique normalized response law maps it to \(D_3=2\rho_{\rm PR}P_Z\); and every other in-class value has the strictly positive defect \(\rho_{\rm PR}^2(k-2)^2\).  Across the completed selectors, PR-IV applies the same normal-form, defect, and equivalence tests. Accordingly, every proposed alternative has exactly one of three statuses:
\begin{equation}
\boxed{
\begin{gathered}
\text{it violates an admissibility gate and is outside the PR class},\\
\text{it has nonzero exact defect and is not a solution},\\
\text{or it is equivalent to the canonical equation and is not distinct}.
\end{gathered}
}
\label{eq:priii-trichotomy}
\end{equation}
There is no fourth case, no fitted selector, and no unregistered free parameter.  Higher-order, nonlocal, additional-field, independent-second-jet, different-threshold, nonperturbative, and EFT constructions are excluded by the domain definition; they are different theory classes, not latent PR-III solutions.  This is the closing equation-architecture theorem for the stated PR-I--PR-III guidelines.  It neither compares arbitrary foundational theories nor asserts a unique physical state when a canonical equation itself admits more than one root.


\section{Conclusion}
\label{sec:priii-conclusion}

Projection Relativity III closes the radiative and cross-sector extension of the projection architecture introduced in the PR-I and PR-II preprints.  PR-I supplied the master projection field, radial spectral branch, displacement sector, and compact electromagnetic phase.  PR-II lifted that boundary geometry into the compact electroweak and flavor fiber.  Starting from those fixed structures, PR-III carries the electromagnetic, electroweak, neutrino, strong, anomaly, and running-continuity branches through one no-target-input ledger while preserving the theorem status of each step.

The first result is the promotion of the compact electromagnetic boundary from a tree-level normalization to a radiatively corrected precision quantity.  The \(D_1+D_2\) branch gives
\begin{equation}
\left(\alpha_{\rm PR,phys}\right)^{-1}
=
137.0359992075134149588913461016165946\ldots ,
\end{equation}
which lies at
\begin{equation}
+0.1376\sigma
\end{equation}
relative to the selected low-energy diagnostic reference.  The implemented
finite-tier result is evaluated from the high-resolution PR boundary
constants, the weak-boundary deficit, the inherited weak angle, and the
declared three-sheet scaling.  The diagnostic fine-structure value enters only
after the branch has been evaluated.  Under the completed PR-IV selector
rules, an altered $D_1/D_2$ basis is outside the registered class and an
equivalent rewriting is the same equation.

Transporting the implemented electromagnetic boundary condition to the
inherited weak displacement scale defines the declared electroweak branch.
The compact-boundary \(C_1\) transport and generation-weighted \(C_2\)
charged--neutral self-energy relations are followed by the canonical neutral
\(C_3\) refinement.  The charged-adjoint algebra proves
\(\operatorname{Tr}_{\rm ch}(q^\dagger q)=2\), and the unique normalized
quadratic response theorem fixes the canonical coefficient \(k=2\) in the
declared minimal PR class.  On that target-independent closure branch, the
ledger yields
\begin{equation}
\boxed{
\begin{aligned}
M_W^{\rm PR}
&=
80.3739428518621\ {\rm GeV},
\\
M_Z^{\rm PR}
&=
91.1876764310439\ {\rm GeV},
\\
G_F^{\rm PR}
&=
1.166379220175995\times10^{-5}\ {\rm GeV}^{-2},
\end{aligned}
}
\end{equation}
with diagnostic positions
\begin{equation}
M_W:\,+0.3566\sigma,
\qquad
M_Z:\,+0.0364\sigma,
\qquad
G_F:\,+0.6003\sigma .
\end{equation}
A single weak-angle shift gives different post-generation reconstructions of
the diagnostic central values, thereby distinguishing the angle-only
comparison class without generating the $C_1/C_2$ relations.  Broader
determinant families with independent second jets define enlarged operator
classes rather than alternative PR branches.  A complete neutral-background
Hessian is an equivalent microscopic presentation only when it reduces to the
already unique normalized response and physical-$Z$ map. The inherited PR-II neutrino branch remains stable in
the resulting radiative environment.  PR-III obtains
\begin{equation}
(m_1,m_2,m_3)
=
(0,\ 0.008627283010,\ 0.05010655367)\ {\rm eV},
\end{equation}
with
\begin{equation}
\sum_i m_i
=
0.058733836680\ {\rm eV},
\qquad
m_\beta
=
8.815029410\ {\rm meV},
\qquad
m_{\beta\beta}
=
1.507694477\ {\rm meV}.
\end{equation}
The massless branch remains protected at multiplicative order, the normal ordering is preserved throughout the PR stability envelope, all mass-squared splittings remain positive, and the PMNS branch remains unitary.  The effective Majorana mass is confined to
\begin{equation}
1.50751978084895\ {\rm meV}
\leq
m_{\beta\beta}
\leq
1.50786917315105\ {\rm meV}.
\end{equation}
The neutrino result is therefore a statement of stability and compatibility, not a refit of oscillation or direct mass data. The compact color branch is likewise consistent at the present tier.  The \(SU(3)_c\) invariants
\begin{equation}
N_c=3,
\qquad
C_A=3,
\qquad
C_F=\frac43,
\qquad
T_F=\frac12
\end{equation}
combine with the PR-generated quark thresholds to give
\begin{equation}
n_f^{\rm PR}\!\left(\Lambda_{\rm EW}^{\rm PR}\right)=6,
\qquad
\beta_0^{\rm PR}\!\left(\Lambda_{\rm EW}^{\rm PR}\right)=7.
\end{equation}
The inherited strong anchor,
\begin{equation}
\alpha_3^{\rm PR}
=
0.117861507469150,
\end{equation}
lies
\begin{equation}
-0.0326484570399\%
\end{equation}
relative to the selected diagnostic reference.  PR-III therefore fixes the threshold ordering, active-flavor ledger, and one-loop asymptotic-freedom sign without importing an external \(\Lambda_{\overline{\rm MS}}\), external quark masses, or a fitted strong-coupling target. These sector results coexist in one consistent representation ledger. The local
\begin{equation}
SU(3)_c^3,\qquad
SU(3)_c^2U(1)_Y,\qquad
SU(2)_L^2U(1)_Y,\qquad
U(1)_Y^3,
\qquad
{\rm grav}^2U(1)_Y
\end{equation}
anomalies cancel per generation.  The total number of weak doublets is even, so the Witten anomaly is absent, and the residual \(U(1)_{\rm em}\) branch is vectorlike.  The low-energy electromagnetic result connects continuously to weak-scale transport; the same compact-boundary suppression scale governs the vector and neutrino stability branches; and the electroweak matching scale is consistent with the six-flavor strong threshold ledger. The unifying result of PR-III is therefore not any one numerical agreement in isolation.  It is the existence of a common projection chain,
\begin{equation}
\boxed{
\begin{aligned}
&\text{PR-I spectral and compact boundary}
\\
&\quad\longrightarrow
\text{PR-II electroweak and flavor lift}
\\
&\quad\longrightarrow
\text{PR-III radiative electromagnetic closure}
\\
&\quad\longrightarrow
\text{weak-scale precision}
\\
&\quad\longrightarrow
\text{neutrino and strong-sector stability}
\\
&\quad\longrightarrow
\text{global anomaly and continuity consistency},
\end{aligned}
}
\end{equation}
in which later sectors inherit earlier PR-generated quantities rather than replacing them with external targets. Within the scope defined in this paper, the resulting branch may be summarized as
\begin{equation}
\boxed{
\begin{gathered}
\alpha^{-1},\,M_W,\,M_Z,\,G_F
\ \text{inside the selected one-sigma diagnostic bands},\\
\text{neutral \(C_3\) coefficient unique in the canonical response class},\\
\text{normal-ordering neutrino branch radiatively stable},\\
\text{strong anchor, threshold ordering, and asymptotic-freedom sign consistent},\\
\text{local and global anomaly conditions satisfied},\\
\text{cross-sector continuity and no-fit provenance preserved}.
\end{gathered}
}
\end{equation}

The neutral \(C_3\) analysis establishes three logically distinct statements.
First, the normalized charged-adjoint invariant is exactly two.  Second, the
PR-III minimal neutral-response closure uses this invariant to define the
unique charged-preserving, photon-null physical-\(Z\) correction in the
declared finite-tier class, fixing \(k=2\) without a fitted coefficient or new
continuous parameter.  Every other in-class equation either has a nonzero
normalized-response defect or is an equivalent presentation of the same
tensor.  Third, any complete gauge-fixed physical-$Z$ Hessian admitted to the
same class is an equivalent microscopic realization of that closure.  The abstract second-jet
families and the broader-EFT operator in
Proposition~\ref{prop:priii-local-neutral-counteroperator} characterize a
deliberately enlarged operator domain and are not alternative PR branches.  The
present result is therefore a canonical, class-relative no-fit uniqueness
theorem; algebraically different but operator-equivalent presentations remain
the same physical equation.  With the completed PR-IV Global Singleton Theorem, this
trichotomy applies across the registered PR-I--PR-III architecture: every
proposed alternative is out of class, has a nonzero exact defect, or is
equivalent to the canonical equation.  Thus the admissible equation quotient
is a singleton and contains no fitted or free continuous parameter.  Equations
using different postulates, added fields, higher orders, independent Wilson
coefficients, or nonperturbative modules define different theory classes; they
are not additional solutions of the closed PR-I--PR-III system.  This
class-relative conclusion concerns the uniqueness of the equation
architecture and does not assert uniqueness among arbitrary theories or among
multiple roots of a canonical equation.


\newpage
\bibliographystyle{plain} 
\bibliography{Oshetski_Projection_Relativity_III_References} 
\end{document}
