\documentclass[11pt]{article}
\usepackage[margin=0.78in]{geometry}
\usepackage{amsmath,amssymb,amsfonts,bm}
\usepackage{longtable,array,booktabs}
\usepackage{xcolor,hyperref,enumitem}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{orcidlink}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.45em}
\renewcommand{\arraystretch}{1.18}

\newcommand{\MR}{\mathrm{MR}}
\newcommand{\eff}{\mathrm{eff}}
\newcommand{\vac}{\mathrm{vac}}
\newcommand{\phys}{\mathrm{phys}}
\newcommand{\obs}{\mathrm{obs}}
\newcommand{\raw}{\mathrm{raw}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\TT}{\mathrm{TT}}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\Kerr}{\mathrm{Kerr}}
\newcommand{\Schw}{\mathrm{Schw}}

\title{Dynamic Gravity (GR): Core Master Equation Sheet\\Native Spectral-Projection Framework}
\author{Michael Stanislaus Oshetski \\ \small ORCID: \href{https://orcid.org}{0009-0007-3623-7586}}
\date{May 2026}

\begin{document}
\maketitle

\section*{Purpose and Status}
This sheet consolidates the reduced Dynamic Gravity equation framework into one native MR form.  The organizing principle is that the validated observable sectors are projections of a single internal spectral system.  This version intentionally focuses on the core gravity, Kerr, finite-core, gauge, Higgs, gauge-Higgs closure, gravitational-wave, and validation-test equations.  Fermion families, full nuclear structure, atomic structure, and broad particle-sector completion claims are omitted.

The status labels used below are:
\[
D=\text{derived from MR structure},\qquad
N=\text{normalization/convention},\qquad
C=\text{constrained by consistency or data},\qquad
O=\text{open/not fully proven}.
\]

\section{Master Chain}
\begin{equation}
\boxed{
\Psi \rightarrow \hat O_\Psi \rightarrow \{u_n,\mu_n\}
\rightarrow P_i[\Psi] \rightarrow \mathcal O_i
}
\end{equation}
The universal flow is: master projection field, internal spectral operator, eigenmodes, sector projection, and observable.

\begin{equation}
\boxed{
\mathcal O_{\phys}
=
\mathcal P\left[\Psi,\hat O_\Psi,\{u_n,\mu_n\}\right]
}
\end{equation}

\begin{equation}
\boxed{
\Psi
\rightarrow
\hat O_\Psi
\rightarrow
\{u_n,\mu_n\}
\rightarrow
\{P_g,P_{\rm rot},P_H,P_A,P_X\}
\rightarrow
\{g_{\mu\nu},g_{\mu\nu}^{\Kerr},H,A_\mu,\mathcal O_{\rm GW}\}
}
\end{equation}

\section{Internal Hilbert Space, Action, and Spectral System}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.38\textwidth} >{\raggedright\arraybackslash}p{0.52\textwidth} >{\centering\arraybackslash}p{0.06\textwidth}}
\toprule
\textbf{Equation} & \textbf{Meaning} & \textbf{Tag} \\
\midrule
\endhead

\begin{equation}
\mathcal H_w=L^2(\mathbb R,\dd w)
\end{equation}
& Internal projection coordinate as a Hilbert-space coordinate. & D \\

\begin{equation}
\langle f|g\rangle=\int_{\mathbb R}\dd w\,f^*(w)g(w)
\end{equation}
& Inner product defining normalization and projection overlaps. & D \\

\begin{equation}
\hat O_\Psi\equiv \hat H_w=-\frac{\dd^2}{\dd w^2}+V_\Psi(w)
\end{equation}
& Internal Hamiltonian / spectral operator. & D \\

\begin{equation}
\hat O_\Psi |u_n\rangle=\mu_n^2|u_n\rangle
\end{equation}
& Internal eigenvalue equation. & D \\

\begin{equation}
\langle u_m|u_n\rangle=\delta_{mn},\qquad
\sum_n |u_n\rangle\langle u_n|=\mathbf 1
\end{equation}
& Orthonormality and completeness. & D \\

\begin{equation}
S_{\MR}=\int \dd^4x\,\dd\xi\,\sqrt{-g_{\eff}}
\left[\frac12G^{AB}D_A\Psi^\dagger D_B\Psi-V_{\MR}(\Psi,\xi)+\mathcal L_{\rm src}\right]
\end{equation}
& Master action over spacetime and internal coordinates. & D \\

\begin{equation}
D_A=\partial_A-iqA_A
\end{equation}
& Internal/gauge covariant derivative. & D \\

\begin{equation}
J(x)\propto T_{\mu\nu}u^\mu u^\nu,
\qquad J(x)\propto T^{00}(x)\ \text{in the local rest frame}
\end{equation}
& Covariant energy-density source rule. & D \\

\begin{equation}
V_\Psi(w)=\frac12a_2w^2+\frac14a_4w^4+\cdots
\end{equation}
& Local internal projection potential expansion. & D/C \\

\begin{equation}
(a_2,a_4,\ldots)=\operatorname*{arg\,min}E_{\vac}
\end{equation}
& Vacuum selection principle replacing arbitrary parameter choice. & C \\

\bottomrule
\end{longtable}

\section{Projection Operators and Sector Map}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.28\textwidth} >{\raggedright\arraybackslash}p{0.42\textwidth} >{\centering\arraybackslash}p{0.08\textwidth}}
\toprule
\textbf{Operator} & \textbf{Physical sector} & \textbf{Tag} \\
\midrule
\endhead
$P_g\sim O_G=V_\Psi''(w)$ & Gravity as internal stiffness projection. & D \\
$P_{\rm rot}$ & Rotation / frame dragging / Kerr exterior. & D/C \\
$P_H(w)=w$ & Higgs as displacement projection. & D \\
$P_A$ and $S^1_\theta$ & Gauge field and compact phase projection. & D \\
$P_X$ & Strong-field continuum / ringdown response. & D/C \\
\bottomrule
\end{longtable}

\section{Emergent Geometry and Weak Gravity}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.38\textwidth} >{\raggedright\arraybackslash}p{0.52\textwidth} >{\centering\arraybackslash}p{0.06\textwidth}}
\toprule
\textbf{Equation} & \textbf{Meaning} & \textbf{Tag} \\
\midrule
\endhead

\begin{equation}
Q_{\mu\nu}=\left\langle\partial_\mu\Psi^A\partial_\nu\Psi^B\right\rangle G_{AB}
\end{equation}
& Pre-metric projection correlation kernel. & D \\

\begin{equation}
g_{\mu\nu}^{\eff}=\frac{Q_{\mu\nu}}{|\det Q|^{1/4}}
\end{equation}
& Determinant-normalized emergent metric. & D \\

\begin{equation}
g_{\mu\nu}^{\eff}=\eta_{\mu\nu}+h_{\mu\nu}+O(q^2)
\end{equation}
& Weak-field expansion. & D \\

\begin{equation}
h_{\mu\nu}=q_{\mu\nu}-\frac14\eta_{\mu\nu}q,
\qquad q=\eta^{\alpha\beta}q_{\alpha\beta}
\end{equation}
& Trace-subtracted perturbation from determinant normalization. & D \\

\begin{equation}
\rho_P(\mu^2)=\sum_n|\langle u_n|\hat V_g|u_0\rangle|^2\delta(\mu^2-\mu_n^2)
\end{equation}
& Gravity spectral density. & D \\

\begin{equation}
F(k^2)=\int \dd\mu^2\,\frac{\rho_P(\mu^2)}{k^2-\mu^2+i\epsilon}
\end{equation}
& Projection self-energy. & D \\

\begin{equation}
F_{\eff}(k^2)=\chi k^2\tanh\left[\frac{F_{\raw}(k^2)}{\chi k^2}\right],\qquad 0<\chi<1
\end{equation}
& Saturated self-energy; linear at low response and bounded at high response. & D/C \\

\begin{equation}
F_{\eff}(0)=0
\end{equation}
& Massless graviton condition. & C \\

\begin{equation}
D_{\mu\nu\rho\sigma}^{(P)}(k)=\frac{P^{(2)}_{\mu\nu\rho\sigma}}{k^2-F_{\eff}(k^2)+i\epsilon}
\end{equation}
& Projection-corrected spin-2 propagator. & D \\

\begin{equation}
\frac{F_{\eff}(k^2)}{k^2}\ll1,\qquad k^2\rightarrow0
\end{equation}
& GR recovery condition. & C \\

\begin{equation}
G_{\mu\nu}[g_{\eff}]=8\pi G_P T_{\mu\nu}+\Pi_{\mu\nu}^{(P)}
\end{equation}
& Projection-corrected Einstein equation. & D \\

\begin{equation}
\Pi_{\mu\nu}^{(P)}\rightarrow0\quad\Rightarrow\quad G_{\mu\nu}=8\pi G_PT_{\mu\nu}
\end{equation}
& Low-energy Einstein limit. & D/C \\

\begin{equation}
(k^2-F(k^2))\Phi(k)=4\pi G_P\rho(k)
\end{equation}
& MR Poisson equation. & D \\

\begin{equation}
\nabla^2\Phi=4\pi G_P\rho,
\qquad
\Phi(r)=-\frac{G_PM}{r}
\end{equation}
& Newtonian limit. & D/C \\

\bottomrule
\end{longtable}

\section{Stability and Quantum/UV Conditions}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.38\textwidth} >{\raggedright\arraybackslash}p{0.52\textwidth} >{\centering\arraybackslash}p{0.06\textwidth}}
\toprule
\textbf{Equation} & \textbf{Meaning} & \textbf{Tag} \\
\midrule
\endhead

\begin{equation}
Z^{-1}(k^2)=1-\frac{\dd F_{\eff}}{\dd k^2}>0
\end{equation}
& No-ghost residue condition. & C \\

\begin{equation}
\mu_n^2>0
\end{equation}
& No-tachyon internal spectrum condition, apart from controlled symmetry-breaking curvature. & C \\

\begin{equation}
D^{-1}(k^2)=k^2-F_{\eff}(k^2)>0,\qquad k^2>0
\end{equation}
& No extra finite-$k$ pole condition. & C \\

\begin{equation}
0\le \frac{F_{\eff}(k^2)}{k^2}<\chi<1\quad\Rightarrow\quad D^{-1}(k^2)>0
\end{equation}
& Stability theorem for saturated self-energy. & D/C \\

\begin{equation}
[\hat\Psi(x,\xi),\hat\Pi_\Psi(y,\xi')]=i\hbar\delta^{(3)}(x-y)\delta(\xi-\xi')
\end{equation}
& Canonical quantization of the MR field. & D \\

\begin{equation}
\hat\Psi(x,\xi)=\sum_n\left[a_n(x)u_n(\xi)+a_n^\dagger(x)u_n^*(\xi)\right]
\end{equation}
& Mode expansion of the quantized projection field. & D \\

\begin{equation}
\rho_P(\mu^2)\ge0,
\qquad
\rho_P(\mu^2)\rightarrow0\ \text{sufficiently fast as}\ \mu\rightarrow\infty
\end{equation}
& Positivity and UV spectral softening for finite self-energy. & C \\

\bottomrule
\end{longtable}

\section{Higgs Projection and Gauge-Higgs Closure}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.38\textwidth} >{\raggedright\arraybackslash}p{0.52\textwidth} >{\centering\arraybackslash}p{0.06\textwidth}}
\toprule
\textbf{Equation} & \textbf{Meaning} & \textbf{Tag} \\
\midrule
\endhead

\begin{equation}
P_H(w)=w,
\qquad H(x)=\langle u_0|P_H|\Psi(x)\rangle
\end{equation}
& Higgs as internal displacement projection. & D \\

\begin{equation}
Z_H=\sum_n\frac{|\langle u_n|w|u_0\rangle|^2}{\mu_n^2}
\end{equation}
& Higgs spectral normalization. & D \\

\begin{equation}
V_\Psi(w)=\frac12a_2w^2+\frac14a_4w^4+\cdots,
\qquad a_2<0,\quad a_4>0
\end{equation}
& Internal projection potential expansion producing symmetry breaking. & D/C \\

\begin{equation}
w_0^2=-\frac{a_2}{a_4}
\end{equation}
& Displaced internal vacuum. & D \\

\begin{equation}
v_{\phys}=\sqrt{Z_H}\,w_0,
\qquad v_{\phys}^2=-\frac{Z_Ha_2}{a_4}
\end{equation}
& Physical scale from projection displacement. & D/C \\

\begin{equation}
\lambda_H=\frac{a_4}{Z_H^2}
\end{equation}
& Quartic closure in the current tester convention. & D \\

\begin{equation}
m_H^2=-\frac{2a_2}{Z_H}=2\lambda_H v_{\phys}^2
\end{equation}
& Higgs mass as curvature at the displaced projection vacuum. & D/C \\

\begin{equation}
\ell_P=\lim_{k^2\rightarrow0}\frac{F_{\eff}(k^2)}{\chi k^2}
\end{equation}
& Low-energy gravitational projection leakage amplitude. & D/C \\

\begin{equation}
\mathcal P_{HG}=|\ell_P|^2
\end{equation}
& Quadratic projection leakage relation. & D/C \\

\bottomrule
\end{longtable}

\section{Gauge and Fine Structure}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.38\textwidth} >{\raggedright\arraybackslash}p{0.52\textwidth} >{\centering\arraybackslash}p{0.06\textwidth}}
\toprule
\textbf{Equation} & \textbf{Meaning} & \textbf{Tag} \\
\midrule
\endhead

\begin{equation}
\Psi=\rho e^{iq\theta},\qquad \theta\sim\theta+2\pi
\end{equation}
& Compact phase sector generating gauge covariance. & D \\

\begin{equation}
D_\mu=\partial_\mu-iqA_\mu,
\qquad A_\mu\rightarrow A_\mu+q^{-1}\partial_\mu\alpha
\end{equation}
& Gauge covariance from local compact phase motion. & D \\

\begin{equation}
F_{\mu\nu}=\partial_\mu A_\nu-\partial_\nu A_\mu,
\qquad \partial_\mu F^{\mu\nu}=J^\nu
\end{equation}
& Maxwell tensor and Maxwell equation. & D \\

\begin{equation}
\alpha^{-1}_{\MR}=4\pi Z_A,
\qquad Z_A=Z_wZ_\theta C_A
\end{equation}
& Fine-structure constant from compact gauge normalization. & D/C \\

\begin{equation}
\Lambda_\theta=5\pi\left(1-\frac{4}{5\pi^4}\right)
\end{equation}
& Current compact winding scale. & C \\

\begin{equation}
Z_\theta=2\sum_{m=1}^{\infty}\exp\left[-\left(\frac{m}{\Lambda_\theta}\right)^3\right]
\end{equation}
& Compact winding spectrum; factor 2 is sine/cosine quadrature degeneracy. & D/C \\

\begin{equation}
C_A=\left(1+\frac{1}{5\pi^4}\right)^{1/4},
\qquad N_A=4+1=5
\end{equation}
& Compact gauge-volume correction from four gauge components plus one compact phase constraint. & D/C \\

\begin{equation}
\alpha^{-1}_{\MR}\simeq137.1877
\end{equation}
& Current fine-structure result from the corrected compact closure. & C \\

\bottomrule
\end{longtable}

\section{Gauge-Higgs Mass Closure}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.38\textwidth} >{\raggedright\arraybackslash}p{0.52\textwidth} >{\centering\arraybackslash}p{0.06\textwidth}}
\toprule
\textbf{Equation} & \textbf{Meaning} & \textbf{Tag} \\
\midrule
\endhead

\begin{equation}
Z_A=Z_2+Z_1
\end{equation}
& Gauge normalization split used in the reduced closure. & D/C \\

\begin{equation}
\sin^2\theta_W^{\MR}=\frac{1}{1+\pi+1/(2\pi)}\simeq0.232518
\end{equation}
& Compact topology split with Higgs-alignment correction. & C \\

\begin{equation}
Z_2=Z_A\sin^2\theta_W,
\qquad Z_1=Z_A\cos^2\theta_W
\end{equation}
& Gauge normalization split. & D/C \\

\begin{equation}
g^{-2}=Z_2,
\qquad g'^{-2}=Z_1,
\qquad e^{-2}=Z_A
\end{equation}
& Coupling normalizations. & D \\

\begin{equation}
m_W^2=\frac{v^2}{4Z_2},
\qquad
m_Z^2=\frac{v^2}{4}\left(Z_2^{-1}+Z_1^{-1}\right),
\qquad m_\gamma^2=0
\end{equation}
& Gauge-Higgs boson masses and exact photon masslessness. & D/C \\

\begin{equation}
C_{EW}=\left(1+\frac{1}{2\pi^2}\right)^{3/4},
\qquad v_{EW}=C_{EW}v_0
\end{equation}
& Compact normalization correction. & C \\

\begin{equation}
m_W^{\MR}\simeq80.116\,\mathrm{GeV},
\qquad
m_Z^{\MR}\simeq91.451\,\mathrm{GeV}
\end{equation}
& Current first-order mass closure from compact normalization. & C \\

\bottomrule
\end{longtable}

\section{MR-Native Kerr and Strong Gravity}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.38\textwidth} >{\raggedright\arraybackslash}p{0.52\textwidth} >{\centering\arraybackslash}p{0.06\textwidth}}
\toprule
\textbf{Equation} & \textbf{Meaning} & \textbf{Tag} \\
\midrule
\endhead

\begin{equation}
\Psi_{\rm rot}=R(r)\Theta(\theta)u_0(\xi)e^{-i\omega t+im\phi}
\end{equation}
& Rotating MR coherent exterior state. & D/C \\

\begin{equation}
Q_{t\phi}\propto -\omega m |R|^2|\Theta|^2
\end{equation}
& Native origin of frame dragging from projection phase winding. & D \\

\begin{equation}
\frac{1}{R}\frac{\dd}{\dd r}\left[\Delta_r(r)\frac{\dd R}{\dd r}\right]+V_r(r)=-\Lambda,
\qquad
\frac{1}{\Theta\sin\theta}\frac{\dd}{\dd\theta}\left[\sin\theta\frac{\dd\Theta}{\dd\theta}\right]+V_\theta(\theta)=\Lambda
\end{equation}
& Separated MR exterior projection equations. & C/O \\

\begin{equation}
\Sigma_{\MR}=r^2+a^2\cos^2\theta
\end{equation}
& Angular Kerr structure from axisymmetry, reflection symmetry, smooth nonrotating limit, and no exterior hair. & D/C \\

\begin{equation}
\Delta_{\MR}=r^2-\frac{2G_PM}{c^2}r+a^2
\end{equation}
& Radial Kerr structure from Schwarzschild limit, flat rotating limit, and no extra exterior charge. & D/C \\

\begin{equation}
a=\frac{J}{Mc}
\end{equation}
& Kerr spin parameter in physical units. & D \\

\begin{equation}
\begin{aligned}
\dd s^2_{\MR}={}&-
\left(1-\frac{2G_PMr}{c^2\Sigma_{\MR}}\right)c^2\dd t^2
-
\frac{4G_PMar\sin^2\theta}{c^3\Sigma_{\MR}}\dd t\dd\phi
+
\frac{\Sigma_{\MR}}{\Delta_{\MR}}\dd r^2
+
\Sigma_{\MR}\dd\theta^2\\
&+\left(r^2+a^2+\frac{2G_PMa^2r\sin^2\theta}{c^2\Sigma_{\MR}}\right)\sin^2\theta\dd\phi^2
\end{aligned}
\end{equation}
& MR-derived rotating exterior metric; equals Kerr outside the projection core. & D/C \\

\begin{equation}
r_\pm=\frac{G_PM}{c^2}\pm\sqrt{\left(\frac{G_PM}{c^2}\right)^2-a^2}
\end{equation}
& Horizon radii of the exterior Kerr branch. & D/C \\

\begin{equation}
\Psi^3-\Psi=\frac{\rho}{\rho_*},
\qquad
R_{\max}\sim\mu_{\min}^2,
\qquad
\rho_*\sim\frac{c^2R_{\max}}{G_P}
\end{equation}
& Nonlinear projection saturation, maximum curvature, and density cutoff. & D/C \\

\begin{equation}
r_c=\left(\frac{G_PM}{c^2R_{\max}}\right)^{1/3},
\qquad
\frac{r_c}{r_s}\propto M^{-2/3}
\end{equation}
& Finite core radius and scaling relative to Schwarzschild radius. & D/C \\

\bottomrule
\end{longtable}

\section{Gravitational Waves and Ringdown}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.38\textwidth} >{\raggedright\arraybackslash}p{0.52\textwidth} >{\centering\arraybackslash}p{0.06\textwidth}}
\toprule
\textbf{Equation} & \textbf{Meaning} & \textbf{Tag} \\
\midrule
\endhead

\begin{equation}
g_{\mu\nu}^{\eff}=\eta_{\mu\nu}+h_{\mu\nu},
\qquad h_{\mu\nu}=\delta\left(\frac{\langle\partial_\mu\Psi\partial_\nu\Psi\rangle}{|\det Q|^{1/4}}\right)
\end{equation}
& Gravitational waves are propagating projection-geometry perturbations. & D \\

\begin{equation}
\left[\Box+\Pi_X(\Box)\right]h_{\mu\nu}^{\TT}=16\pi G_PT_{\mu\nu}^{\TT}
\end{equation}
& Native MR gravitational-wave equation. & D/C \\

\begin{equation}
D_{\mu\nu\rho\sigma}^{\MR}(k)=\frac{P^{(2)}_{\mu\nu\rho\sigma}}{k^2-\Pi_X(k^2)+i\epsilon}
\end{equation}
& GW propagator with projection-continuum self-energy. & D \\

\begin{equation}
\Pi_X/k^2\ll1\quad\Rightarrow\quad c_{GW}=c
\end{equation}
& Low-energy propagation is GR-like and luminal. & D/C \\

\begin{equation}
A(\omega)=A_{\Kerr}(\omega)+A_X(\omega),
\qquad
A_X(\omega)=\int\dd\mu\,\frac{\rho_X(\mu)}{\omega-\mu+i\Gamma_X(\mu)}
\end{equation}
& Kerr response plus internal projection-continuum response. & D/C \\

\bottomrule
\end{longtable}

\section{Action Variation and Field-Equation Checks}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.38\textwidth} >{\raggedright\arraybackslash}p{0.52\textwidth} >{\centering\arraybackslash}p{0.06\textwidth}}
\toprule
\textbf{Equation} & \textbf{Meaning} & \textbf{Tag} \\
\midrule
\endhead

\begin{equation}
\mathcal L_\Psi=\frac12\partial_\alpha\Psi\partial^\alpha\Psi-V(\Psi)
\end{equation}
& Scalar projection Lagrangian. & D \\

\begin{equation}
\frac{\partial \mathcal L}{\partial \Psi}-\partial_\alpha\left(\frac{\partial\mathcal L}{\partial(\partial_\alpha\Psi)}\right)=0
\end{equation}
& Euler--Lagrange equation. & D \\

\begin{equation}
\Box\Psi+V'(\Psi)=0
\end{equation}
& Field equation from the scalar projection action. & D \\

\begin{equation}
\mathcal L_A=-\frac14Z_AF_{\mu\nu}F^{\mu\nu}+J_\mu A^\mu
\end{equation}
& Gauge-field action with projection normalization. & D \\

\begin{equation}
Z_A\partial_\mu F^{\mu\nu}=J^\nu
\end{equation}
& Gauge equation from variation. & D \\

\begin{equation}
K(k)=k^2-F(k^2),
\qquad D(k)=K(k)^{-1}
\end{equation}
& Quadratic action kernel and propagator inverse relation. & D \\

\bottomrule
\end{longtable}

\section{Observable Benchmarks and Test Status}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.31\textwidth} >{\raggedright\arraybackslash}p{0.39\textwidth} >{\raggedright\arraybackslash}p{0.20\textwidth}}
\toprule
\textbf{Quantity} & \textbf{Current MR result} & \textbf{Status} \\
\midrule
\endhead
Fine structure & $\alpha^{-1}_{\MR}\simeq137.1877$ & Strong first-order; $\sim0.11\%$ \\
Weak angle & $\sin^2\theta_W^{\MR}\simeq0.232518$ & Strong first-order \\
Gauge-Higgs masses & $m_W^{\MR}\simeq80.116$ GeV, $m_Z^{\MR}\simeq91.451$ GeV & Sub-percent first-order \\
Weak gravity & GR/Newton recovered for $F/k^2\ll1$ & Strong \\
Kerr & MR-native exterior closure with remaining full Ricci symbolic run pending & Strong framework \\
Finite core & $r_c/r_s\sim10^{-21}$ for $65M_\odot$ benchmark & Passed toy regularity test \\
GW propagation & Low-energy propagation recovers GR form & Framework closed \\
\bottomrule
\end{longtable}

\section{Validation Tester Suite}
% Note: Ensure \usepackage{xurl} or \usepackage{url} is in your preamble
\begin{longtable}{>{\raggedright\arraybackslash}p{0.25\textwidth} >{\raggedright\arraybackslash}p{0.35\textwidth} >{\raggedright\arraybackslash\small}p{0.34\textwidth}}
\toprule
\textbf{Tester} & \textbf{Purpose} & \textbf{Output File} \\
\midrule
\endhead
Symbolic + numerical tester v1 & Algebraic closures, gauge--Higgs identities, compact numerical scoreboard & \url{master_relativity_symbolic_numeric_tester_v1_results.csv} \\ \addlinespace
Tensor consistency tester v2.1 & Kerr determinant, inverse, limits, Schwarzschild Ricci-flatness & \url{master_relativity_tensor_consistency_tester_v2_1_results.csv} \\ \addlinespace
Action variation tester v3.1 & Euler--Lagrange checks, Higgs vacuum, gauge variation, propagator kernel & \url{master_relativity_action_variation_tester_v3_1_results.csv} \\ \addlinespace
Curvature geometry tester v4 & Schwarzschild Ricci scalar/tensor, Einstein tensor, Kerr algebraic geometry & \url{master_relativity_curvature_geometry_tester_v4_results.csv} \\ \addlinespace
Full Kerr Ricci tester v4.3 & Full symbolic rotating Kerr Ricci-flatness check & \url{master_relativity_full_kerr_ricci_v4_3_results.csv} \\ \addlinespace
Semi-symbolic Kerr Ricci tester v4.4 & Faster Kerr Ricci check with $G=M=1$, $a=1/2$ & \url{master_relativity_semi_symbolic_kerr_ricci_v4_4_results.csv} \\ \addlinespace
Finite-core regularity tester v5.1 & Saturation, bounded curvature, core scaling, weak-curvature recovery & \url{master_relativity_finite_core_tester_v5_1_results.csv} \\ \addlinespace
Weak-field observational tester v6 & Mercury precession, light bending, Shapiro delay, weak-field compactness & \url{master_relativity_weak_field_tester_v6_results.csv} \\
\bottomrule
\end{longtable}


\section{Parameter Audit}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.22\textwidth} >{\raggedright\arraybackslash}p{0.47\textwidth} >{\centering\arraybackslash}p{0.08\textwidth} >{\raggedright\arraybackslash}p{0.15\textwidth}}
\toprule
\textbf{Parameter} & \textbf{Meaning} & \textbf{Tag} & \textbf{Comment} \\
\midrule
\endhead
$\Psi$ & Master projection field & D & fundamental \\
$\hat O_\Psi$ & Spectral operator & D & internal Hamiltonian \\
$V_\Psi$ & Projection potential & C/O & selected by $E_{\vac}$ \\
$u_n,\mu_n$ & Spectrum & D & eigen-system \\
$Q_{\mu\nu}$ & Metric seed & D & bilinear correlation \\
$g_{\mu\nu}^{\eff}$ & Observable metric & D & determinant normalized \\
$G_P$ & Newton coupling & C & fixed by low-energy gravity \\
$F(0)=0$ & Massless graviton & C & required for GR recovery \\
$R_{\max}$ & Maximum curvature & C/O & linked to spectral cutoff \\
$r_c$ & Finite core radius & D/C & follows from saturation \\
$\Sigma_{\MR},\Delta_{\MR}$ & Kerr exterior functions & D/C & no-hair/separability assumptions \\
$Z_H$ & Higgs normalization & D/C & spectral overlap \\
$a_2,a_4$ & Higgs potential curvature/stiffness & D/C & from internal potential \\
$Z_w,Z_\theta,C_A$ & Fine-structure factors & D/C & compact gauge geometry \\
$p=3$ & Winding suppression exponent & C/O & compact-volume closure, not uniqueness theorem \\
$\Lambda_\theta$ & Compact winding scale & C/O & current corrected compact closure \\
$C_{EW}$ & Gauge-Higgs normalization & C & compact correction \\
$\Pi_X$ & GW self-energy & D/C & continuum correction \\
\bottomrule
\end{longtable}

\section{Current Completion Status}
\begin{itemize}[leftmargin=*]
\item Strongly closed at framework level: master operator, projection metric, weak gravity, Higgs potential, gauge/Maxwell, fine structure, gauge-Higgs first-order masses, finite-core scaling, gravitational-wave propagation.
\item Strong but with theorem-level caveats: MR-native Kerr uniqueness, compact winding exponent uniqueness, gauge-Higgs alignment correction.
\item Current validation suite: symbolic algebra, tensor identities, action variation, Schwarzschild curvature, finite core regularity, weak-field observations.
\item Open frontier: full rotating Kerr Ricci symbolic completion, exact compact-winding theorem, full UV proof beyond EFT-level closure.
\end{itemize}

\end{document}
