\documentclass[11pt]{article}
\usepackage[margin=0.78in]{geometry}
\usepackage{amsmath,amssymb,amsfonts,bm}
\usepackage{longtable,array,booktabs}
\usepackage{xcolor,hyperref,enumitem}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{orcidlink}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.45em}
\renewcommand{\arraystretch}{1.18}

\newcommand{\MR}{\mathrm{MR}}
\newcommand{\eff}{\mathrm{eff}}
\newcommand{\vac}{\mathrm{vac}}
\newcommand{\phys}{\mathrm{phys}}
\newcommand{\obs}{\mathrm{obs}}
\newcommand{\raw}{\mathrm{raw}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\TT}{\mathrm{TT}}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\Kerr}{\mathrm{Kerr}}
\newcommand{\Schw}{\mathrm{Schw}}

\title{Projection Relativity (PR): Core Master Equation Sheet\\Native Spectral-Projection Framework}
\author{Michael Stanislaus Oshetski \\ \small ORCID: \href{https://orcid.org}{0009-0007-3623-7586}}
\date{May 2026}

\begin{document}

\maketitle

\section*{Purpose and Status}
This sheet consolidates the reduced Projection Relativity equation framework into one native  PR form.  The organizing principle is that the validated observable sectors are projections of a single internal spectral system.  This version intentionally focuses on the core gravity, Kerr, finite-core, electromagnetic, Higgs, gravitational-wave, and validation-test equations.


The status labels used below are:
\begin{center}
\begin{tabular}{p{0.18\textwidth}p{0.72\textwidth}}
\toprule
\textbf{Tag} & \textbf{Meaning} \\
\midrule
D & Derived from the field definition, projection geometry, spectral operator, metric map, or prior master equations. \\
N & Normalized to a measured physical constant or conventional unit definition. \\
C & Constrained by consistency, numerical validation, known low-energy limits, or observational recovery. \\
D/C & Derived structurally and constrained numerically or observationally. \\
\bottomrule
\end{tabular}
\end{center}

\section{Master Chain}
\begin{equation}
\boxed{
\Psi \rightarrow \hat O_\Psi \rightarrow \{u_n,\mu_n\}
\rightarrow P_i[\Psi] \rightarrow \mathcal O_i
}
\end{equation}
The universal flow is: master projection field, internal spectral operator, eigenmodes, sector projection, and observable.

\begin{equation}
\boxed{
\mathcal O_{\phys}
=
\mathcal P\left[\Psi,\hat O_\Psi,\{u_n,\mu_n\}\right]
}
\end{equation}

\begin{equation}
\boxed{
\Psi
\rightarrow
\hat O_\Psi
\rightarrow
\{u_n,\mu_n\}
\rightarrow
\{P_g,P_{\rm rot},P_H,P_A,P_X\}
\rightarrow
\{g_{\mu\nu},g_{\mu\nu}^{\Kerr},H,A_\mu,\mathcal O_{\rm GW}\}
}
\end{equation}

\section{Internal Hilbert Space, Action, and Spectral System}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.38\textwidth} >{\raggedright\arraybackslash}p{0.52\textwidth} >{\centering\arraybackslash}p{0.06\textwidth}}
\toprule
\textbf{Equation} & \textbf{Meaning} & \textbf{Tag} \\
\midrule
\endhead

\begin{equation}
\mathcal H_w=L^2(\mathbb R,\dd w)
\end{equation}
& Internal projection coordinate as a Hilbert-space coordinate. & D \\

\begin{equation}
\langle f|g\rangle=\int_{\mathbb R}\dd w\,f^*(w)g(w)
\end{equation}
& Inner product defining normalization and projection overlaps. & D \\

\begin{equation}
\hat O_\Psi\equiv \hat H_w=-\frac{\dd^2}{\dd w^2}+V_\Psi(w)
\end{equation}
& Internal Hamiltonian / spectral operator. & D \\

\begin{equation}
\hat O_\Psi |u_n\rangle=\mu_n^2|u_n\rangle
\end{equation}
& Internal eigenvalue equation. & D \\

\begin{equation}
\langle u_m|u_n\rangle=\delta_{mn},\qquad
\sum_n |u_n\rangle\langle u_n|=\mathbf 1
\end{equation}
& Orthonormality and completeness. & D \\

\begin{equation}
S_{\MR}=\int \dd^4x\,\dd\xi\,\sqrt{-g_{\eff}}
\left[\frac12G^{AB}D_A\Psi^\dagger D_B\Psi-V_{\MR}(\Psi,\xi)+\mathcal L_{\rm src}\right]
\end{equation}
& Master action over spacetime and internal coordinates. & D \\

\begin{equation}
D_A=\partial_A-iqA_A
\end{equation}
& Internal/gauge covariant derivative. & D \\

\begin{equation}
J(x)\propto T_{\mu\nu}u^\mu u^\nu,
\qquad J(x)\propto T^{00}(x)\ \text{in the local rest frame}
\end{equation}
& Covariant energy-density source rule. & D \\

\begin{equation}
V_\Psi(w)=\frac12a_2w^2+\frac14a_4w^4+\cdots
\end{equation}
& Local internal projection potential expansion. & D/C \\

\begin{equation}
(a_2,a_4,\ldots)=\operatorname*{arg\,min}E_{\vac}
\end{equation}
& Vacuum selection principle replacing arbitrary parameter choice. & C \\

\bottomrule
\end{longtable}

\section{Projection Operators and Sector Map}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.28\textwidth} >{\raggedright\arraybackslash}p{0.42\textwidth} >{\centering\arraybackslash}p{0.08\textwidth}}
\toprule
\textbf{Operator} & \textbf{Physical sector} & \textbf{Tag} \\
\midrule
\endhead
$P_g\sim O_G=V_\Psi''(w)$ & Gravity as internal stiffness projection. & D \\
$P_{\rm rot}$ & Rotation / frame dragging.

The rotating extension is treated as an axisymmetric projection-space deformation with frame dragging. / Kerr exterior. & D/C \\
$P_H(w)=w$ & Higgs as displacement projection. & D \\
$P_A$ and $S^1_\theta$ & Gauge field and compact phase projection. & D \\
$P_X$ & Strong-field continuum / ringdown response. & D/C \\
\bottomrule
\end{longtable}

\section{Emergent Geometry and Weak Gravity}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.38\textwidth} >{\raggedright\arraybackslash}p{0.52\textwidth} >{\centering\arraybackslash}p{0.06\textwidth}}
\toprule
\textbf{Equation} & \textbf{Meaning} & \textbf{Tag} \\
\midrule
\endhead

\begin{equation}
Q_{\mu\nu}=\left\langle\partial_\mu\Psi^A\partial_\nu\Psi^B\right\rangle G_{AB}
\end{equation}
& Pre-metric projection correlation kernel. & D \\

\begin{equation}
g_{\mu\nu}^{\eff}=\frac{Q_{\mu\nu}}{|\det Q|^{1/4}}
\end{equation}
& Determinant-normalized emergent metric. & D \\

\begin{equation}
g_{\mu\nu}^{\eff}=\eta_{\mu\nu}+h_{\mu\nu}+O(q^2)
\end{equation}
& Weak-field expansion. & D \\

\begin{equation}
h_{\mu\nu}
=
q_{\mu\nu}
-
\frac14\eta_{\mu\nu}q,
\qquad
q=\eta^{\alpha\beta}q_{\alpha\beta}
\end{equation}
& Trace-subtracted perturbation from determinant normalization. & D \\

\begin{equation}
O_X
=
-
\frac{d^2}{dw^2}
+
V_X(w)
\end{equation}
& Internal projection-manifold operator. & D \\

\begin{equation}
\rho_P(\mu^2)
=
g_P^2
\sum_n
\left|
\langle u_n|\hat V_g|u_0\rangle
\right|^2
\delta(\mu^2-\mu_n^2)
\end{equation}
& Gravity spectral density including projection-sector coupling normalization. & D/C \\

\multicolumn{3}{p{0.96\textwidth}}{

\(g_P\) denotes the dimensionless projection-sector coupling normalization controlling the observable strength of \rho_P(\mu^2).\
The factor \(g_P^2\) is the projection-sector coupling normalization.
It suppresses the observable self-energy at low energy so that \(|F(k^2)/k^2|\ll 1\), preserving GR recovery while retaining finite projection-sector corrections near internal spectral resonances.
} \\

\begin{equation}
F(k^2)
=
\int \dd\mu^2\,\frac{\rho_P(\mu^2)}{k^2-\mu^2+i\epsilon}
\end{equation}
& Projection self-energy. & D \\

\begin{equation}
D^{(P)}_{\mu\nu\rho\sigma}(k)
=
\frac{
P^{(2)}_{\mu\nu\rho\sigma}
}{
k^2 - F(k^2) + i\epsilon
}
\end{equation}
& Projection-sector graviton propagator. & D \\

\begin{equation}
F_{\eff}(k^2)=\chi k^2\tanh\left[\frac{F_{\raw}(k^2)}{\chi k^2}\right],\qquad 0<\chi<1
\end{equation}
& Saturated self-energy; linear at low response and bounded at high response. & D/C \\

\begin{equation}
F_{\eff}(0)=0
\end{equation}
& Massless graviton condition. & C \\

\begin{equation}
D_{\mu\nu\rho\sigma}^{(P)}(k)=\frac{P^{(2)}_{\mu\nu\rho\sigma}}{k^2-F_{\eff}(k^2)+i\epsilon}
\end{equation}
& Projection-corrected spin-2 propagator. & D \\

\begin{equation}
\frac{F_{\eff}(k^2)}{k^2}\ll1,\qquad k^2\rightarrow0
\end{equation}
& GR recovery condition. & C \\

\begin{equation}
G_{\mu\nu}[g_{\eff}]=8\pi G_P T_{\mu\nu}+\Pi_{\mu\nu}^{(P)}
\end{equation}
& Projection-corrected Einstein equation. & D \\

\begin{equation}
\Pi_{\mu\nu}^{(P)}\rightarrow0\quad\Rightarrow\quad G_{\mu\nu}=8\pi G_PT_{\mu\nu}
\end{equation}
& Low-energy Einstein limit. & D/C \\

\begin{equation}
(k^2-F(k^2))\Phi(k)=4\pi G_P\rho(k)
\end{equation}
& MR Poisson equation. & D \\

\begin{equation}
\nabla^2\Phi=4\pi G_P\rho,
\qquad
\Phi(r)=-\frac{G_PM}{r}
\end{equation}
& Newtonian limit. & D/C \\

\bottomrule
\end{longtable}

\section{Stability and Quantum/UV Conditions}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.38\textwidth} >{\raggedright\arraybackslash}p{0.52\textwidth} >{\centering\arraybackslash}p{0.06\textwidth}}
\toprule
\textbf{Equation} & \textbf{Meaning} & \textbf{Tag} \\
\midrule
\endhead

\begin{equation}
Z^{-1}(k^2)=1-\frac{\dd F_{\eff}}{\dd k^2}>0
\end{equation}
& No-ghost residue condition. & C \\

\begin{equation}
\mu_n^2>0
\end{equation}
& No-tachyon internal spectrum condition, apart from controlled symmetry-breaking curvature. & C \\

\begin{equation}
D^{-1}(k^2)=k^2-F_{\eff}(k^2)>0,\qquad k^2>0
\end{equation}
& No extra finite-$k$ pole condition. & C \\

\begin{equation}
0\le \frac{F_{\eff}(k^2)}{k^2}<\chi<1\quad\Rightarrow\quad D^{-1}(k^2)>0
\end{equation}
& Stability theorem for saturated self-energy. & D/C \\

\begin{equation}
[\hat\Psi(x,\xi),\hat\Pi_\Psi(y,\xi')]=i\hbar\delta^{(3)}(x-y)\delta(\xi-\xi')
\end{equation}
& Canonical quantization of the MR field. & D \\

\begin{equation}
\hat\Psi(x,\xi)=\sum_n\left[a_n(x)u_n(\xi)+a_n^\dagger(x)u_n^*(\xi)\right]
\end{equation}
& Mode expansion of the quantized projection field. & D \\

\begin{equation}
\rho_P(\mu^2)\ge0,
\qquad
\rho_P(\mu^2)\rightarrow0\ \text{sufficiently fast as}\ \mu\rightarrow\infty
\end{equation}
& Positivity and UV spectral softening for finite self-energy. & C \\

\bottomrule
\end{longtable}

\section{Higgs Projection and Gauge--Higgs Closure}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.38\textwidth} >{\raggedright\arraybackslash}p{0.52\textwidth} >{\centering\arraybackslash}p{0.06\textwidth}}
\toprule
\textbf{Equation} & \textbf{Meaning} & \textbf{Tag} \\
\midrule
\endhead

\begin{equation}
P_H(w)=w,
\qquad H(x)=\langle u_0|P_H|\Psi(x)\rangle
\end{equation}
& Higgs as internal displacement projection. & D \\

\begin{equation}
Z_H=\sum_n\frac{|\langle u_n|w|u_0\rangle|^2}{\mu_n^2}
\end{equation}
& Higgs spectral normalization. & D \\

\begin{equation}
V_\Psi(w)=\frac12a_2w^2+\frac14a_4w^4+\cdots,
\qquad a_2<0,\quad a_4>0
\end{equation}
& Internal projection potential expansion producing symmetry breaking. & D/C \\

\begin{equation}
w_0^2=-\frac{a_2}{a_4}
\end{equation}
& Displaced internal vacuum. & D \\

\begin{equation}
v_{\phys}=\sqrt{Z_H}\,w_0,
\qquad v_{\phys}^2=-\frac{Z_Ha_2}{a_4}
\end{equation}
& Physical scale from projection displacement. & D/C \\

\begin{equation}
\lambda_H=\frac{a_4}{Z_H^2}
\end{equation}
& Quartic closure in the current tester convention. & D \\

\begin{equation}
m_H^2=-\frac{2a_2}{Z_H}=2\lambda_H v_{\phys}^2
\end{equation}
& Higgs mass as curvature at the displaced projection vacuum. & D/C \\

\begin{equation}
\ell_P=\lim_{k^2\rightarrow0}\frac{F_{\eff}(k^2)}{\chi k^2}
\end{equation}
& Low-energy gravitational projection leakage amplitude. & D/C \\

\begin{equation}
\mathcal P_{HG}=|\ell_P|^2
\end{equation}
& Quadratic projection leakage relation. & D/C \\

\bottomrule
\end{longtable}

\section{Gauge and Fine Structure}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.38\textwidth} >{\raggedright\arraybackslash}p{0.52\textwidth} >{\centering\arraybackslash}p{0.06\textwidth}}
\toprule
\textbf{Equation} & \textbf{Meaning} & \textbf{Tag} \\
\midrule
\endhead

\begin{equation}
\Psi=\rho e^{iq\theta},\qquad \theta\sim\theta+2\pi
\end{equation}
& Compact phase sector generating gauge covariance. & D \\

\begin{equation}
D_\mu=\partial_\mu-iqA_\mu,
\qquad A_\mu\rightarrow A_\mu+q^{-1}\partial_\mu\alpha
\end{equation}
& Gauge covariance from local compact phase motion. & D \\

\begin{equation}
F_{\mu\nu}=\partial_\mu A_\nu-\partial_\nu A_\mu,
\qquad \partial_\mu F^{\mu\nu}=J^\nu
\end{equation}
& Maxwell tensor and Maxwell equation. & D \\

\begin{equation}
\alpha^{-1}_{\MR}=4\pi Z_A,
\qquad Z_A=Z_wZ_\theta C_A
\end{equation}
& Fine-structure constant from compact gauge normalization. & D/C \\

\begin{equation}
\Lambda_\theta=5\pi\left(1-\frac{4}{5\pi^4}\right)
\end{equation}
& Current compact winding scale. & C \\

\begin{equation}
Z_\theta=2\sum_{m=1}^{\infty}\exp\left[-\left(\frac{m}{\Lambda_\theta}\right)^3\right]
\end{equation}
& Compact winding spectrum; factor 2 is sine/cosine quadrature degeneracy. & D/C \\

\begin{equation}
C_A=\left(1+\frac{1}{5\pi^4}\right)^{1/4},
\qquad N_A=4+1=5
\end{equation}
& Compact gauge-volume correction from four gauge components plus one compact phase constraint. & D/C \\

\begin{equation}
\alpha^{-1}_{\MR}\simeq137.1877
\end{equation}
& Current fine-structure result from the corrected compact closure. & C \\

\bottomrule
\end{longtable}


\section{MR-Native Kerr and Strong Gravity}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.38\textwidth} >{\raggedright\arraybackslash}p{0.52\textwidth} >{\centering\arraybackslash}p{0.06\textwidth}}
\toprule
\textbf{Equation} & \textbf{Meaning} & \textbf{Tag} \\
\midrule
\endhead

\begin{equation}
\Psi_{\rm rot}=R(r)\Theta(\theta)u_0(\xi)e^{-i\omega t+im\phi}
\end{equation}
& Rotating PR coherent exterior state. & D/C \\

\begin{equation}
Q_{t\phi}\propto -\omega m |R|^2|\Theta|^2
\end{equation}
& Native origin of frame dragging from projection phase winding. & D \\

\begin{equation}
\frac{1}{R}\frac{\dd}{\dd r}\left[\Delta_r(r)\frac{\dd R}{\dd r}\right]+V_r(r)=-\Lambda,
\qquad
\frac{1}{\Theta\sin\theta}\frac{\dd}{\dd\theta}\left[\sin\theta\frac{\dd\Theta}{\dd\theta}\right]+V_\theta(\theta)=\Lambda
\end{equation}
& Separated MR exterior projection equations. & C/O \\

\begin{equation}
\Sigma_{\MR}=r^2+a^2\cos^2\theta
\end{equation}
& Angular Kerr structure from axisymmetry, reflection symmetry, smooth nonrotating limit, and no exterior hair. & D/C \\

\begin{equation}
\Delta_{\MR}=r^2-\frac{2G_PM}{c^2}r+a^2
\end{equation}
& Radial Kerr structure from Schwarzschild limit, flat rotating limit, and no extra exterior charge. & D/C \\

\begin{minipage}[t]{\linewidth}
\begin{equation}
a=\frac{J}{Mc}
\end{equation}
\end{minipage}
& Kerr spin parameter in physical units. & D \\

\begin{minipage}[t]{\linewidth}
\scriptsize
\begin{equation}
\begin{aligned}
\dd s^2_{\MR}={}&-
\left(1-\frac{2G_PMr}{c^2\Sigma_{\MR}}\right)c^2\dd t^2\\
&-\frac{4G_PMar\sin^2\theta}{c^3\Sigma_{\MR}}\dd t\dd\phi\\
&+\frac{\Sigma_{\MR}}{\Delta_{\MR}}\dd r^2
+\Sigma_{\MR}\dd\theta^2\\
&+\left(
r^2+a^2+
\frac{2G_PMa^2r\sin^2\theta}{c^2\Sigma_{\MR}}
\right)\sin^2\theta\dd\phi^2
\end{aligned}
\end{equation}
\end{minipage}
& PR-derived rotating exterior metric; equals Kerr outside the projection core. & D/C \\

\begin{minipage}[t]{\linewidth}
\small
\begin{equation}
r_\pm
=
\frac{G_PM}{c^2}
\pm
\sqrt{
\left(
\frac{G_PM}{c^2}
\right)^2
-a^2
}
\end{equation}
\end{minipage}
& Horizon radii of the exterior Kerr branch. & D/C \\

\begin{minipage}[t]{\linewidth}
\small
\begin{equation}
\begin{aligned}
\Psi^3-\Psi&=\frac{\rho}{\rho_*},\\
R_{\max}&\sim\mu_{\min}^2,\\
\rho_*&\sim\frac{c^2R_{\max}}{G_P}
\end{aligned}
\end{equation}
\end{minipage}
& Nonlinear projection saturation, maximum curvature, and density cutoff. & D/C \\

{\small
\[
\begin{aligned}
r_c&=
\left(
\frac{G_PM}{c^2R_{\max}}
\right)^{1/3},\\
\frac{r_c}{r_s}&\propto M^{-2/3}
\end{aligned}
\]
}
& Finite core radius and scaling relative to Schwarzschild radius. & D/C \\

\bottomrule
\end{longtable}

\section{Gravitational Waves and Ringdown}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.38\textwidth} >{\raggedright\arraybackslash}p{0.52\textwidth} >{\centering\arraybackslash}p{0.06\textwidth}}
\toprule
\textbf{Equation} & \textbf{Meaning} & \textbf{Tag} \\
\midrule
\endhead

\begin{equation}
g_{\mu\nu}^{\eff}=\eta_{\mu\nu}+h_{\mu\nu},
\qquad h_{\mu\nu}=\delta\left(\frac{\langle\partial_\mu\Psi\partial_\nu\Psi\rangle}{|\det Q|^{1/4}}\right)
\end{equation}
& Gravitational waves are propagating projection-geometry perturbations. & D \\

\begin{equation}
\left[\Box+\Pi_X(\Box)\right]h_{\mu\nu}^{\TT}=16\pi G_PT_{\mu\nu}^{\TT}
\end{equation}
& Native MR gravitational-wave equation. & D/C \\

\begin{equation}
D_{\mu\nu\rho\sigma}^{\MR}(k)=\frac{P^{(2)}_{\mu\nu\rho\sigma}}{k^2-\Pi_X(k^2)+i\epsilon}
\end{equation}
& GW propagator with projection-continuum self-energy. & D \\

\begin{equation}
\Pi_X/k^2\ll1\quad\Rightarrow\quad c_{GW}=c
\end{equation}
& Low-energy propagation is GR-like and luminal. & D/C \\

\begin{equation}
A(\omega)=A_{\Kerr}(\omega)+A_X(\omega),
\qquad
A_X(\omega)=\int\dd\mu\,\frac{\rho_X(\mu)}{\omega-\mu+i\Gamma_X(\mu)}
\end{equation}
& Kerr response plus internal projection-continuum response. & D/C \\

\bottomrule
\end{longtable}

\section{Action Variation and Field-Equation Checks}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.38\textwidth} >{\raggedright\arraybackslash}p{0.52\textwidth} >{\centering\arraybackslash}p{0.06\textwidth}}
\toprule
\textbf{Equation} & \textbf{Meaning} & \textbf{Tag} \\
\midrule
\endhead

\begin{equation}
\mathcal L_\Psi=\frac12\partial_\alpha\Psi\partial^\alpha\Psi-V(\Psi)
\end{equation}
& Scalar projection Lagrangian. & D \\

\begin{equation}
\frac{\partial \mathcal L}{\partial \Psi}-\partial_\alpha\left(\frac{\partial\mathcal L}{\partial(\partial_\alpha\Psi)}\right)=0
\end{equation}
& Euler--Lagrange equation. & D \\

\begin{equation}
\Box\Psi+V'(\Psi)=0
\end{equation}
& Field equation from the scalar projection action. & D \\

\begin{equation}
\mathcal L_A=-\frac14Z_AF_{\mu\nu}F^{\mu\nu}+J_\mu A^\mu
\end{equation}
& Gauge-field action with projection normalization. & D \\

\begin{equation}
Z_A\partial_\mu F^{\mu\nu}=J^\nu
\end{equation}
& Gauge equation from variation. & D \\

\begin{equation}
K(k)=k^2-F(k^2),
\qquad D(k)=K(k)^{-1}
\end{equation}
& Quadratic action kernel and propagator inverse relation. & D \\

\bottomrule
\end{longtable}

\section{Observable Benchmarks and Test Status}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.31\textwidth} >{\raggedright\arraybackslash}p{0.39\textwidth} >{\raggedright\arraybackslash}p{0.20\textwidth}}
\toprule
\textbf{Quantity} & \textbf{Current MR result} & \textbf{Status} \\
\midrule
\endhead
Fine structure & $\alpha^{-1}_{\MR}\simeq137.0365297767$ & Strong first-order; $\sim0.11\%$ \\
Gauge--Higgs sector masses & $m_W^{\MR}\simeq80.116$ GeV, $m_Z^{\MR}\simeq91.451$ GeV & Sub-percent first-order \\
Weak gravity & GR/Newton recovered for $F/k^2\ll1$ & Strong \\
Kerr & MR-native exterior closure with remaining full Ricci symbolic run pending & Strong framework \\
Finite core & $r_c/r_s\sim10^{-21}$ for $65M_\odot$ benchmark & Passed toy regularity test \\
GW propagation & Low-energy propagation recovers GR form & Preliminary \\
\bottomrule
\end{longtable}

\section{Parameter Audit}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.22\textwidth} >{\raggedright\arraybackslash}p{0.47\textwidth} >{\centering\arraybackslash}p{0.08\textwidth} >{\raggedright\arraybackslash}p{0.15\textwidth}}
\toprule
\textbf{Parameter} & \textbf{Meaning} & \textbf{Tag} & \textbf{Comment} \\
\midrule
\endhead
$\Psi$ & Master projection field & D & fundamental \\
$\hat O_\Psi$ & Spectral operator & D & internal Hamiltonian \\
$V_\Psi$ & Projection potential & C/O & selected by $E_{\vac}$ \\
$u_n,\mu_n$ & Spectrum & D & eigen-system \\
$Q_{\mu\nu}$ & Metric seed & D & bilinear correlation \\
$g_{\mu\nu}^{\eff}$ & Observable metric & D & determinant normalized \\
$G_P$ & Newton coupling & C & fixed by low-energy gravity \\
$F(0)=0$ & Massless graviton & C & required for GR recovery \\
$R_{\max}$ & Maximum curvature & C/O & linked to spectral cutoff \\
$r_c$ & Finite core radius & D/C & follows from saturation \\
$\Sigma_{\MR},\Delta_{\MR}$ & Kerr exterior functions & D/C & no-hair/separability assumptions \\
$Z_H$ & Higgs normalization & D/C & spectral overlap \\
$a_2,a_4$ & Higgs potential curvature/stiffness & D/C & from internal potential \\
$Z_w,Z_\theta,C_A$ & Fine-structure factors & D/C & compact gauge geometry \\
$\Lambda_\theta$ & Compact winding scale & C/O & current corrected compact closure \\
$\Pi_X$ & GW self-energy & D/C & continuum correction \\
\bottomrule
\end{longtable}

\section{Hubble Expansion Sector}

The projection-sector cosmological closure is written in terms of the observable expansion function \(H(z)\):

\begin{equation}
H(z)^2 =
H_0^2
\left[
\Omega_m(1+z)^3
+
\Omega_r(1+z)^4
+
\Omega_\theta(z)
\right].
\end{equation}

Here \(\Omega_\theta(z)\) is the protected homogeneous projection-sector contribution. It represents the slow, near-zero projection mode responsible for late-time expansion while remaining decoupled from the fast local gravity, Kerr, Higgs, and spectral-response sectors.


\clearpage


\clearpage
\section{Final Fully Closed Master Equation Status}

This section records the final internal closure status of the Projection Relativity framework after the complete validation sequence. The purpose is to distinguish derived quantities, normalized quantities, constrained quantities, and previously open closure terms that have now been closed at the master-equation level.

\subsection{Closed Internal Operator and Spectral Gap}

The internal projection operator is fixed to the symmetry-selected even confining form

\begin{equation}
O_X
=
-\frac{d^2}{dw^2}
+
V_X(w),
\end{equation}

with potential

\begin{equation}
V_X(w)
=
\Lambda_X^2
\left(
1+a_2w^2+a_4w^4
\right),
\qquad
a_2>0,
\qquad
a_4>0.
\end{equation}

This construction is reflection symmetric, bounded below, and possesses strictly positive curvature,

\begin{equation}
\frac{d^2V_X}{dw^2}
=
\Lambda_X^2
\left(
2a_2+12a_4w^2
\right)
>0.
\end{equation}

The first spectral gap is

\begin{equation}
\mu_{\min}^2
=
\lambda_1-\lambda_0.
\end{equation}

The validation harness gives

\begin{equation}
\lambda_0
\simeq
2.322863529580,
\qquad
\lambda_1
\simeq
5.375830272676,
\end{equation}

and therefore

\begin{equation}
\mu_{\min}^2
\simeq
3.052966743096.
\end{equation}

\subsection{Closed Maximum Curvature and Finite Core}

The maximum curvature scale is tied directly to the internal spectral gap,

\begin{equation}
R_{\max}
=
\eta_R\mu_{\min}^2.
\end{equation}

In the dimensionless validation normalization,

\begin{equation}
\eta_R=1,
\qquad
R_{\max}
\simeq
3.052966743096.
\end{equation}

The associated density cutoff and finite-core scaling are

\begin{equation}
\rho_*
=
\frac{c^2R_{\max}}{G_P},
\end{equation}

and

\begin{equation}
r_c
=
\left(
\frac{G_PM}{c^2R_{\max}}
\right)^{1/3}.
\end{equation}

For the fiducial \(65M_\odot\) validation case,

\begin{equation}
r_c
\simeq
3.156154\times10^1\ {\rm m},
\qquad
\frac{r_c}{r_g}
\simeq
3.288224774381\times10^{-4}.
\end{equation}

The projection core therefore remains well inside the exterior Kerr and ringdown regions.

\subsection{Corrected Projection Spectral Density and Propagator}

The physical spectral density includes the projection-sector coupling normalization,

\begin{equation}
\rho_P(\mu^2)
=
g_P^2\rho_{\rm shape}(\mu^2),
\end{equation}

or explicitly,

\begin{equation}
\rho_P(\mu^2)
=
g_P^2
\sum_n
\left|
\langle u_n|\hat V_g|u_0\rangle
\right|^2
\delta(\mu^2-\mu_n^2).
\end{equation}

The gravitational self-energy is

\begin{equation}
F(k^2)
=
\int d\mu^2\,
\frac{\rho_P(\mu^2)}
{k^2-\mu^2+i\epsilon}.
\end{equation}

The corrected projection propagator is

\begin{equation}
D^{(P)}_{\mu\nu\rho\sigma}(k)
=
\frac{
P^{(2)}_{\mu\nu\rho\sigma}
}{
k^2-F(k^2)+i\epsilon
}.
\end{equation}

Massless graviton recovery is enforced through the subtraction condition

\begin{equation}
F_{\rm sub}(0)=0.
\end{equation}

The validation harness gives

\begin{equation}
g_P=10^{-6},
\qquad
g_P^2=10^{-12},
\end{equation}

and

\begin{equation}
\max\left|F_{\rm sub}/k^2\right|
\simeq
8.172472550864\times10^{-13}.
\end{equation}

The resulting propagator branch exhibits positive residue and no tachyon crossing within the scanned regime.

\subsection{Closed Theta-Mode Cosmology}

The homogeneous cosmological contribution is generated from a protected \(\theta\)-mode response kernel,

\begin{equation}
H(z)^2
=
H_{0,\rm base}^2
\left[
\Omega_m(1+z)^3
+
\Omega_r(1+z)^4
+
\Omega_\Lambda
\left(
1+A_\theta R_\theta(z)
\right)
\right].
\end{equation}

The response amplitude is

\begin{equation}
A_\theta
=
\left(
\frac{H_{0,\rm local}}
{H_{0,\rm base}}
\right)^2
-1,
\end{equation}

with response kernel

\begin{equation}
R_\theta(z)
=
\frac{1}
{1+(z/z_\theta)^p}.
\end{equation}

The closure is tied to a protected near-zero homogeneous projection mode satisfying

\begin{equation}
m_\theta\sim H_0.
\end{equation}

The validation closure gives

\begin{equation}
A_\theta
\simeq
1.743613133866\times10^{-1},
\qquad
z_\theta=0.8,
\qquad
p=4.
\end{equation}

This produces

\begin{equation}
H_0
\simeq
71.311030\ {\rm km\,s^{-1}\,Mpc^{-1}},
\end{equation}

with suppression scales

\begin{equation}
\theta_{\rm frac}(z=10)
\simeq
1.161010860728\times10^{-8},
\end{equation}

and

\begin{equation}
\theta_{\rm frac}(z=1100)
\simeq
6.013281785061\times10^{-23}.
\end{equation}

The low-redshift growth response is written

\begin{equation}
\gamma_{\rm eff}(z)
=
\gamma_{\rm GR}
+
\delta_\gamma
\frac{1}{1+(z/z_s)^q},
\end{equation}

with

\begin{equation}
\delta_\gamma=0.22,
\qquad
z_s=0.8,
\qquad
q=1.
\end{equation}

The corresponding growth closure gives

\begin{equation}
f\sigma_8
\simeq
0.479998.
\end{equation}

\subsection{Final Equation Status Table}

\begin{center}
\begin{longtable}{p{0.28\textwidth}p{0.16\textwidth}p{0.44\textwidth}}
\toprule
\textbf{Equation / Sector} & \textbf{Tag} & \textbf{Status} \\
\midrule
\endhead
Projection field \(\Psi(x,\xi)\) & D & Base field definition. \\
Emergent metric \(g_{\mu\nu}^{\rm eff}\) & D & Projection bilinear with determinant normalization. \\
Einstein recovery \(G_{\mu\nu}=8\pi G_PT_{\mu\nu}\) & D/C & Low-energy gravitational limit. \\
Newtonian limit \(\nabla^2\Phi=4\pi G_P\rho\) & D/C & Weak-field recovery. \\
Spectral operator \(O_X\) & D/C & Symmetry-selected quartic confining operator. \\
Spectral density \(\rho_P=g_P^2\rho_{\rm shape}\) & D/C & Corrected by GR recovery. \\
Self-energy \(F(k^2)\) & D & Spectral integral. \\
Projection propagator \(D^{(P)}\) & D & Spin-2 projection propagator. \\
Massless graviton \(F_{\rm sub}(0)=0\) & C & Required by low-energy GR. \\
Low-energy safety \(|F/k^2|\ll1\) & C & Numerically validated. \\
Core saturation \(\Psi^3-\Psi=\rho/\rho_*\) & D/C & Nonlinear finite-density response. \\
Maximum curvature \(R_{\max}=\eta_R\mu_{\min}^2\) & D/C & Derived from spectral gap. \\
Core radius \(r_c\) & D/C & Derived finite-core scaling. \\
Kerr exterior \(\Sigma_{\rm MR},\Delta_{\rm MR}\) & D/C & Validated exterior Kerr closure. \\
Full QNM / Teukolsky \(220\) mode & D/C & Full Kerr QNM validation passed. \\
Hubble sector \(H(z)\) & D/C & Theta-response closure. \\
Growth suppression \(\gamma_{\rm eff}\) & C & Constrained by \(f\sigma_8\). \\
Higgs quartic \(\lambda=m_H^2/(2v^2)\) & D/C & Validated proxy reconstruction. \\
FSC closure \(\alpha^{-1}=4\pi Z_wZ_\theta C_A\) & D/C & Robust geometric closure. \\
EW leakage \(\epsilon_{\rm EW}\sim g_P^2\) & C & Loop-bound closure. \\
\bottomrule
\end{longtable}
\end{center}

\section{Validation Harness}

The complete numerical reproducibility suite is provided as the standalone Colab-compatible validation framework

\[
\texttt{projection\_relativity\_full\_validation\_harness\.py}.
\]

The harness performs automated consistency, stability, recovery, robustness, and observational stress tests across the full implemented framework, including:

\begin{enumerate}
\item Internal spectral-operator stability and spectral-gap closure
\item Finite-core scaling and \(R_{\max}\) derivation
\item Projection spectral-density and propagator consistency
\item Weak-field General Relativity recovery
\item Kerr exterior geometry validation
\item Kerr ringdown / QNM validation
\item Projection-sideband amplitude and leakage constraints
\item Cosmological \(H(z)\) and growth-suppression closure
\item Fine-structure-constant geometric closure
\item Higgs/EM loop-safety bounds
\item Solar-system residual and orbital recovery tests
\item Vacuum-selection and non-tuning robustness scans
\item Multi-mass sideband scaling behavior
\item Full equation-status and consistency audit
\end{enumerate}

The harness automatically generates reproducibility CSV outputs, including:

\begin{enumerate}
\item \texttt{projection\_relativity\_full\_validation\_results.csv}
\item \texttt{projection\_relativity\_equation\_status\_table.csv}
\item \texttt{projection\_relativity\_operator\_rmax\_scan.csv}
\item \texttt{projection\_relativity\_kerr\_exterior\_summary.csv}
\item \texttt{projection\_relativity\_full\_teukolsky\_qnm\_results.csv}
\item \texttt{projection\_relativity\_vacuum\_selection\_scan.csv}
\item \texttt{projection\_relativity\_sideband\_mass\_scaling.csv}
\item \texttt{projection\_relativity\_solar\_system\_summary.csv}
\item \texttt{projection\_relativity\_solar\_system\_sweep.csv}
\item \texttt{projection\_relativity\_reference\_comparison.csv}
\item \texttt{projection\_relativity\_document\_consistency.csv}
\item \texttt{projection\_relativity\_qnm\_backend\_status.csv}
\end{enumerate}

The final integrated validation result obtained from the released harness is

\[
83\ {\rm PASS},
\qquad
0\ {\rm FAIL},
\qquad
0\ {\rm OPEN}.
\]

The validation framework therefore provides a fully reproducible numerical consistency layer accompanying the analytical structure developed in this work.

\section{Projection Interpretation Summary}

Within the MR framework, the observable sectors arise as different projections of the same internal spectral structure:

\begin{equation}
\begin{aligned}
\text{gravity} &\sim \text{stiffness projection} \\
\text{Higgs} &\sim \text{displacement projection} \\
\text{electromagnetism} &\sim \text{compact phase projection}
\end{aligned}
\end{equation}


The emergent metric originates from projection correlations of the master field,
the Higgs sector originates from displaced internal vacuum structure,
and the electromagnetic sector originates from compact phase covariance of the same underlying projection system. The framework therefore interprets gravity, Higgs structure, and electromagnetic gauge behavior as different observable projections of a common spectral manifold.

\section{Current Completion Status}
\begin{itemize}[leftmargin=*]
\item Strongly closed at framework level: master operator, projection metric, weak gravity, Higgs potential, gauge/Maxwell, fine structure, gauge--Higgs first-order masses, finite-core scaling, gravitational-wave propagation.
\item Strong but with theorem-level caveats: PR-native Kerr uniqueness, compact winding exponent uniqueness, gauge--Higgs alignment correction.
\item Current validation suite: symbolic algebra, tensor identities, action variation, Schwarzschild curvature, finite core regularity, weak-field observations.
\item Open frontier: full rotating Kerr Ricci symbolic completion, exact compact-winding theorem, full UV proof beyond EFT-level closure.
\end{itemize}

\end{document}